---
title: 
output: pdf_document
header-includes:
   - \usepackage{longtable}
   - \usepackage{fullpage}
   - \usepackage[margin=0.5in]{geometry}
---

```{r setup, include=FALSE}
library(dplyr)
library(purrr)

knitr::opts_chunk$set(echo = FALSE)
```

Cluster: __`r cluster`__ --- Village: __`r sprintf("%s (%s)", village.name, village.code)`__ --- Table Number: __`r table.num`__

Enumerator: _________________________________

Date: ____/____/_____, Time: _______________

## Instructions

* Please fill out one these forms per community member interviewed. Note that the names listed will differ between forms. Only _one_ form should be filled per community member.
* For each of the ten listed community members ask whether their treatment compliance is known 
* Note that the spelling of names might not perfectly correct. If there is confusion about which of several people a name refers to, please mark it as an __M__.

\begin{longtable}{l|l|l|l|l}
\hline 
 & & & & \\
 & \textbf{Name} & \textbf{Treated in MDA?} & \textbf{Day Treated} & \textbf{Wear Bracelet or Ink?} \\
 &               & Y = Yes & L = Late & B = Bracelet \\
 &               & N = No & E = Early & K = Ink \\
 &               & D = Don't Know if Dewormed & D = Don't Know & N = None \\
 &               & P = Don't Know Person &  & D = Don't Know \\
 &               & M = Multiple Persons &  &  \\
 & & & & \\
\hline
\hline
\endfirsthead
\hline 
 & & & & \\
 & \textbf{Name} & \textbf{Treated in MDA?} & \textbf{Day Treated} & \textbf{Wear Bracelet or Ink?} \\
 &               & Y = Yes & L = Late & B = Bracelet \\
 &               & Y = No & E = Early & K = Ink \\
 &               & D = Don't Know if Dewormed & D = Don't Know & N = None \\
 &               & P = Don't Know Person &  & D = Don't Know \\
 & & & & \\
\hline
\hline
\endhead
```{r, results='asis'}
for (individ.index in seq_along(obs.names)) {
  cat(" & & & & \\\\* \n")
  cat(sprintf("%d & %s [%d] &  &  &  \\\\* \n",
              individ.index, 
              obs.names[individ.index],
              ids[individ.index]))
  cat(" & & & & \\\\* \n \\hline \n")
}
```
\end{longtable}