---
title: "TakeUp Parametric Static Model Analysis Notebook"
author:
- Anne Karing^[University of California Berkeley]
- Karim Naguib^[Evidence Action]
output:
  html_notebook:
    fig_align: "center"
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    number_sections: yes
    theme: flatly
    toc: yes
    # toc_float:
    #   collapsed: true
    #   smooth_scroll: false
    toc_depth: 5
header-includes:
   - \usepackage{bbm}
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r param-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(magrittr)
library(foreach)
library(plyr)
library(lubridate)
library(forcats)
library(haven)
library(broom)
library(tidyverse)
library(ggrepel)
library(ggmap)
library(modelr)

library(rstan)
library(bayesplot)

library(econometr)

source("takeup_rct_assign_clusters.R")
source("analysis_util.R")

knitr::read_chunk("analysis_util.R", labels = "analysis-util")

options(dplyr.show_progress = TRUE, digits = 4) #, mc.cores = max(1, parallel::detectCores()))

theme_set(theme_minimal())
```

```{r param-parallel-setup}
num_cores <- tryCatch({
  yaml::yaml.load_file("../local_config.yaml") %$% cores
}, error = function(err) parallel::detectCores())

cl <- parallel::makeCluster(max(1, num_cores))
doParallel::registerDoParallel(cl)
```

```{r param-rstan-setup}
options(mc.cores = max(1, parallel::detectCores()))
rstan_options(auto_write = TRUE)
```

```{r param-model-version}
fit_version <- "test_static_2"
```

Loading sampled estimates:

```{r load-param-model-fit}
model_fit <- dir("stanfit", pattern = str_interp("model_${fit_version}_\\d+.csv"), full.names = TRUE) %>% 
  read_stan_csv()

check_hmc_diagnostics(model_fit)

load(file.path("stan_analysis_data", str_interp("model_${fit_version}.RData")))
```
# Analyzing

```{r param-model-prep-data, include=FALSE}
static_treatment_cell_info <- tibble(treatment_size = with(param_stan_data, missing_treatment_sizes + observed_treatment_sizes),
                                     all_treatment_id = param_stan_data$ate_treatments) %>% 
  left_join(param_stan_data$treatment_map, "all_treatment_id") %>% 
  select(-ends_with("_id")) %>% 
  mutate(treatment_rank = seq_len(n()),
         observed_treatment_size = param_stan_data$observed_treatment_sizes, 
         observed_takeup_prop = param_stan_data$observed_takeup_total / observed_treatment_size) %>% 
  unite(incentive_treatment, str_c(c("private", "social"), "_value"), sep = "-", remove = FALSE) %>% 
  create_incentive_treatment_col()

static_ate_pair_info <- param_stan_data$ate_pairs %>% 
  mutate(pair_rank = seq_len(n())) %>% 
  left_join(static_treatment_cell_info, c("rank_id_left" = "treatment_rank")) %>% 
  left_join(static_treatment_cell_info, c("rank_id_right" = "treatment_rank"), suffix = c("_left", "_right")) %>% 
  mutate(treatment_size = treatment_size_left)

est_deworming_takeup <- model_fit %>% 
  as.data.frame( pars = "est_takeup") %>%
  mutate(iter_id = seq_len(n())) %>% 
  gather(treatment_rank, iter_takeup, -iter_id) %>% 
  mutate(treatment_rank = str_extract(treatment_rank, "\\d+") %>% as.integer()) %>% 
  inner_join(static_treatment_cell_info, "treatment_rank") 

est_deworming_takeup_ate <- model_fit %>% 
  as.data.frame(pars = "est_takeup_ate") %>%
  mutate(iter_id = seq_len(n())) %>% 
  gather(outcome_id, iter_ate, -iter_id) %>% 
  mutate(pair_rank = str_extract(outcome_id, "\\d+") %>% as.integer()) %>% 
  inner_join(static_ate_pair_info, "pair_rank")
```

```{r param-takeup-levels, include=FALSE}
est_deworming_takeup_phone <- est_deworming_takeup %>% 
  prepare_est_deworming_takeup(subgroups = "phone_owner")

est_deworming_takeup_dist <- est_deworming_takeup %>% 
  prepare_est_deworming_takeup(subgroups = "dist.pot.group")

est_deworming_takeup_phone_dist <- est_deworming_takeup %>%
  prepare_est_deworming_takeup(subgroups = c("phone_owner", "dist.pot.group"))

est_deworming_takeup_all <- est_deworming_takeup %>% 
  filter(dist.pot.group == dist.pot.group) %>% 
  prepare_est_deworming_takeup() 
```

```{r new-param-dyn-ate, include=FALSE}
est_deworming_takeup_ate_phone <- est_deworming_takeup_ate %>% 
  prepare_est_deworming_ate(subgroups = "phone_owner_left")

est_deworming_takeup_ate_dist <- est_deworming_takeup_ate %>% 
  prepare_est_deworming_ate(subgroups = str_c("dist.pot.group", c("_left", "_right")))

est_deworming_takeup_ate_phone_dist <- est_deworming_takeup_ate %>%
  prepare_est_deworming_ate(subgroups = c("phone_owner_left", str_c("dist.pot.group", c("_left", "_right"))))

est_deworming_takeup_ate_all <- est_deworming_takeup_ate %>% 
  prepare_est_deworming_ate() 
```

```{r}
```

## All Combined

### Take-up Levels

```{r param-takeup-level-all, fig.width=10, fig.height=4}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_all,
  takeup_data = est_deworming_takeup,
  combiner = . %>%
    subgroup_combiner("iter_takeup"), 
  data_preparer = . %>% 
    filter(sms.treatment.2 == "control"),
  incentive_treatment_col = "incentive_treatment"
)
```

### ATE

```{r param-dyn-ate-all, fig.width=10, fig.height=4}
est_deworming_takeup_ate_all %>% 
  plot_ate(
    ate_summ_data = .,
    ate_data = est_deworming_takeup_ate,
    combiner = . %>%
      subgroup_combiner("iter_ate"), 
    data_preparer = . %>% 
      filter(incentive_treatment_right %in% c("Control", "Calendar")), 
    incentive_treatment_left_col = "incentive_treatment_left", 
    by_comparator = "incentive_treatment_right"
  )
```

```{r static-dynamic-all, fig.width=10, fig.height=5}
est_deworming_takeup_ate_all %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>%
      filter(dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>% 
      subgroup_combiner("iter_ate", "compare_type"), 
    data_preparer = . %>% 
      # filter(incentive_treatment_static_right != "Control" | incentive_treatment_static_left != incentive_treatment_dynamic_left) %>%
      filter(incentive_treatment_static_right != "Control" | incentive_treatment_static_left != incentive_treatment_dynamic_left) %>%
      mutate(compare_type = if_else(incentive_treatment_static_left == incentive_treatment_dynamic_left, 
                                    "dynamic effect", 
                                    "static effect") %>% 
           factor() %>% 
           fct_relabel(str_to_title))
  ) +
  labs(subtitle = "Separating static and dynamic effects") +
  facet_wrap(~ compare_type, ncol = 1) 
```

### Daily Take-up Levels

```{r param-dyn-daily-takeup-levels-all, fig.width=10}
est_deworming_day_all %>% 
  filter(incentive_treatment_static == incentive_treatment_dynamic) %>% 
  plot_dyn_takeup_daily()
```

## Split by Distance

### Take-up Levels

```{r param-dyn-takeup-levels-dist, fig.width=10, fig.height=8}
plot_dyn_takeup(
  takeup_summ_data = est_deworming_takeup_dyn_dist,
  takeup_data = est_deworming_takeup_dyn,
  combiner = . %>%
    subgroup_combiner("iter_takeup", "dist.pot.group_static"),
  data_preparer = . %>% 
    filter(incentive_treatment_static == incentive_treatment_dynamic,
           dist.pot.group_static == dist.pot.group_dynamic) %>% 
    mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title)))) +
  facet_wrap(~ dist.pot.group_static, ncol = 1)
```

### ATE

```{r param-dyn-ate-dist, fig.width=10, fig.height=8}
est_deworming_takeup_ate_dist %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>% 
      subgroup_combiner("iter_ate", "dist.pot.group_static_left"),
    data_preparer = . %>% 
      filter(dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right,
             incentive_treatment_static_left == incentive_treatment_dynamic_left,
             incentive_treatment_static_right == incentive_treatment_dynamic_right) %>% 
             # sms.treatment.2_static == sms.treatment.2_dynamic) %>% 
      mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(factor(.), str_to_title))) 
  ) +
  facet_wrap(~ dist.pot.group_static_left, ncol = 1)
```

```{r param-dyn-sepstatdyn-dist, fig.width=12, fig.height=6}
est_deworming_takeup_ate_dist %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>% 
      subgroup_combiner("iter_ate", c("dist.pot.group_static_left", "compare_type")),
    data_preparer = . %>% 
      filter(incentive_treatment_static_right != "Control" | incentive_treatment_static_left != incentive_treatment_dynamic_left) %>%
      filter(dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>%
      mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(factor(.), str_to_title))) %>% 
      mutate(compare_type = if_else(incentive_treatment_static_left == incentive_treatment_dynamic_left, 
                                    "dynamic effect", 
                                    "static effect") %>% 
               factor() %>% 
               fct_relabel(str_to_title))
  )  +
  labs(subtitle = "Separating static and dynamic effects") +
  facet_grid(dist.pot.group_static_left ~ compare_type) 
```

```{r list-info-ate, eval=FALSE}
est_deworming_takeup_ate_dist %>% 
    filter(dist.pot.group_static_left != dist.pot.group_dynamic_left | dist.pot.group_static_right != dist.pot.group_dynamic_right,
           dist.pot.group_static_right == dist.pot.group_dynamic_right, 
           dist.pot.group_dynamic_right == "far", 
           dist.pot.group_static_left == dist.pot.group_static_right) %>% 
   count(incentive_treatment_static_left,
         dist.pot.group_static_left, dist.pot.group_dynamic_left, dist.pot.group_static_right, dist.pot.group_dynamic_right) 
   # count(incentive_treatment_static_left, incentive_treatment_dynamic_left, incentive_treatment_static_right, incentive_treatment_dynamic_right,
```

```{r info-ate-dist, fig.width=10, fig.height=4}
plot_dyn_ate(info_inc_ate, ate_data = info_inc_ate_iter_data)  

# est_deworming_takeup_ate_dist %>% 
#   plot_dyn_ate(
#     ate_data = est_deworming_takeup_ate,
#     combiner = . %>% 
#       subgroup_combiner("iter_ate", "info_change_type"),
#     data_preparer = . %>% 
#       filter(dist.pot.group_static_left != dist.pot.group_dynamic_left | dist.pot.group_static_right != dist.pot.group_dynamic_right,
#              dist.pot.group_static_right == dist.pot.group_dynamic_right, 
#              dist.pot.group_static_left == dist.pot.group_static_right) %>% 
#       mutate(info_change_type = if_else(dist.pot.group_static_right == "far", "increase", "decrease") %>% 
#                factor() %>% 
#                fct_relabel(str_to_title))
#   ) +
#   facet_wrap(~ info_change_type, ncol = 1)
```

### Daily Take-up Levels

```{r param-dyn-daily-takeup-levels-dist, fig.width=10, fig.height=8}
est_deworming_day_dist %>% 
  filter(incentive_treatment_static == incentive_treatment_dynamic,
         dist.pot.group_static == dist.pot.group_dynamic) %>% 
  mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
  plot_dyn_takeup_daily() +
  facet_wrap(~ dist.pot.group_static, ncol = 1, scales = "free_y")
```



## Split by Phone Ownership

### Take-up Levels

```{r param-dyn-takeup-levels-phone, fig.width=10, fig.height=8}
  plot_dyn_takeup(
    takeup_summ_data = est_deworming_takeup_dyn_phone,
    takeup_data = est_deworming_takeup_dyn %>% 
      filter(dist.pot.group_static == dist.pot.group_dynamic) %>% 
      subgroup_combiner("iter_takeup", "phone_owner_static"),
    data_preparer = . %>% 
      filter(incentive_treatment_static == incentive_treatment_dynamic) %>% 
      # sms.treatment.2_static == sms.treatment.2_dynamic) %>% 
      mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners"))))) +
  facet_wrap(~ phone_owner_static, ncol = 1)
```

### ATE

```{r param-dyn-ate-phone, fig.width=10, fig.height=8}
est_deworming_takeup_ate_phone %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate %>% 
      filter(incentive_treatment_static_left == incentive_treatment_dynamic_left,
             incentive_treatment_static_right == incentive_treatment_dynamic_right,
             dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>% 
      subgroup_combiner("iter_ate", "phone_owner_static_left"),
    data_preparer = . %>% 
      filter(incentive_treatment_static_left == incentive_treatment_dynamic_left,
             incentive_treatment_static_right == incentive_treatment_dynamic_right) %>% 
      mutate_at(vars(starts_with("phone_owner_static")), 
                funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) 
  ) +
  facet_wrap(~ phone_owner_static_left, ncol = 1)
```

```{r param-dyn-sepstatdyn-phone, fig.width=12, fig.height=6} 
est_deworming_takeup_ate_phone %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>% 
      filter(dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>% 
      subgroup_combiner("iter_ate", c("phone_owner_static_left", "compare_type")),
    data_preparer = . %>% 
      filter(incentive_treatment_static_right != "Control" | incentive_treatment_static_left != incentive_treatment_dynamic_left) %>%
      mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) %>% 
      mutate(compare_type = if_else(incentive_treatment_static_left == incentive_treatment_dynamic_left, 
                                    "dynamic effect", "static effect") %>% 
               factor() %>% 
               fct_relabel(str_to_title)) 
  )  +
  labs(subtitle = "Separating static and dynamic effects") +
  facet_grid(phone_owner_static_left ~ compare_type) 
```

### Daily Take-up Levels

```{r param-dyn-daily-takeup-phone, fig.width=10, fig.height=8}
est_deworming_day_phone %>% 
  filter(incentive_treatment_static == incentive_treatment_dynamic) %>% 
  mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) %>% 
  plot_dyn_takeup_daily() +
  facet_wrap(~ phone_owner_static, ncol = 1)
```

## Split by Distance and Phone Ownership

### Take-up Levels

```{r param-dyn-takeup-levels-phone-dist, fig.width=10, fig.height=12}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_phone_dist,
  takeup_data = est_deworming_takeup,
  combiner = . %>% 
    subgroup_combiner("iter_takeup", c("phone_owner", "dist.pot.group")),
  data_preparer = . %>% 
    filter(sms.treatment.2 == "control") %>% 
    mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(., str_to_title))) %>% 
    mutate_at(vars(starts_with("phone_owner")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Non-Phone Owners", "Phone Owners")))),
  incentive_treatment_col = "incentive_treatment") +
  facet_wrap(~ dist.pot.group + phone_owner, ncol = 1)
```

### ATE 

```{r param-dyn-ate-phone-dist, fig.width=10, fig.height=12}
est_deworming_takeup_ate_phone_dist %>%
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>% 
      subgroup_combiner("iter_ate", c("dist.pot.group_static_left", "phone_owner_static_left")),
    data_preparer = . %>% 
      filter(incentive_treatment_static_left == incentive_treatment_dynamic_left,
             incentive_treatment_static_right == incentive_treatment_dynamic_right,
             dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>% 
      mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
      mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) 
  ) +
  facet_wrap(~ dist.pot.group_static_left + phone_owner_static_left, ncol = 1)
```

```{r param-dyn-sepstatdyn-phone-dist, fig.width=12, fig.height=8}
est_deworming_takeup_ate_phone_dist %>% 
  plot_dyn_ate(
    ate_data = est_deworming_takeup_ate,
    combiner = . %>% 
      subgroup_combiner("iter_ate", c("dist.pot.group_static_left", "phone_owner_static_left", "compare_type")),
    data_preparer = . %>% 
      filter(incentive_treatment_static_right != "Control" | incentive_treatment_static_left != incentive_treatment_dynamic_left,
             dist.pot.group_static_left == dist.pot.group_dynamic_left,
             dist.pot.group_static_right == dist.pot.group_dynamic_right) %>% 
      mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
      mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) %>% 
      mutate(compare_type = if_else(incentive_treatment_static_left == incentive_treatment_dynamic_left, 
                                    "dynamic effect", "static effect") %>% 
           factor() %>% 
           fct_relabel(str_to_title)) 
  )  +
  labs(subtitle = "Separating static and dynamic effects") +
  facet_grid(phone_owner_static_left + dist.pot.group_static_left ~ compare_type) 
```

```{r info-ate-phone-dist, fig.width=12, fig.height=6}
plot_dyn_ate(info_inc_ate_phone, 
             ate_data = info_inc_ate_iter_data_phone,
             data_preparer = . %>% 
               mutate_at(vars(starts_with("phone_owner_static")), 
                         funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners"))))) +
  facet_wrap(~ phone_owner_static_left, ncol = 1)

# est_deworming_takeup_ate_phone_dist %>% 
#   plot_dyn_ate(
#     ate_data = est_deworming_takeup_ate,
#     combiner = . %>% 
#       subgroup_combiner("iter_ate", c("phone_owner_static_left", "info_change_type")),
#     data_preparer = . %>% 
#       filter(dist.pot.group_static_left != dist.pot.group_dynamic_left | dist.pot.group_static_right != dist.pot.group_dynamic_right,
#              dist.pot.group_static_right == dist.pot.group_dynamic_right, 
#              dist.pot.group_static_left == dist.pot.group_static_right) %>% 
#       mutate(info_change_type = if_else(dist.pot.group_static_right == "far", "increase", "decrease") %>% 
#                factor() %>% 
#                fct_relabel(str_to_title))
#   ) +
#   facet_grid(phone_owner_static_left ~ info_change_type) 
```

### Daily Take-up Levels

```{r param-dyn-daily-takeup-phone-dist, fig.width=12, fig.height=8}
est_deworming_day_phone_dist %>% 
  filter(incentive_treatment_static == incentive_treatment_dynamic,
         dist.pot.group_static == dist.pot.group_dynamic) %>% 
  mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
  mutate_at(vars(starts_with("phone_owner_static")), funs(factor(., levels = c(FALSE, TRUE), labels = c("Phone Owners", "Non-Phone Owners")))) %>% 
  plot_dyn_takeup_daily() +
  facet_grid(dist.pot.group_static ~ phone_owner_static, scales = "free_y")
```

# Checking MCMC

This section takes a look at the validity of our MCMC simulation.

```{r, include=FALSE}
# From http://discourse.mc-stan.org/t/how-can-i-solve-bfmi-low-problem/3018/2
pairs_stan <- function(chain, stan_model, pars) {
  energy <- as.matrix(sapply(get_sampler_params(stan_model, inc_warmup = F), 
                             function(x) x[,"energy__"]))
  pars <- extract(stan_model, pars = pars, permuted = F)
  df <- data.frame(energy[,chain], pars[,chain,])
  names(df)[1] <- "energy"
  GGally::ggpairs(df, title = paste0("Chain", chain), 
                  lower = list(continuous = GGally::wrap("points", alpha = 0.2)))                    
}
```

```{r}
model_fit@model_pars
model_fit %>% print(pars = c("est_takeup_ate"))
model_fit %>% print(pars = c("hyper_beta"))
```

```{r}
model_posterior_array <- as.array(model_fit)
model_np <- nuts_params(model_fit)
model_lp <- log_posterior(model_fit)
```

```{r check-energy}
sample_param <- model_fit %>% get_sampler_params(inc_warmup = FALSE)

sample_param %>% 
  map(~ .x[, "energy__"]) %>% 
  map(~ (sum(diff(.x)^2)/length(.x))/var(.x)) 
```

```{r}
rhat(model_3_fit) %>% summary()
rhat(model_3_fit) %>% discard(~ is_less_than(.x, 1.2) | is.nan(.x)) 
```


```{r, eval=FALSE, fig.width=15}
mcmc_trace(model_3_posterior_array, regex_pars = c("hyper_baseline_dyn_effect\\[[1-3]\\]"), np = model_3_np)
```

```{r, fig.width=15}
mcmc_nuts_divergence(model_np, model_lp)
```

```{r, eval=FALSE}
color_scheme_set("darkgray")
mcmc_parcoord(model_3_posterior_array, np = model_3_np, 
              regex_pars = c("hyper_beta_day1"))
mcmc_parcoord(model_3_posterior_array, np = model_3_np, 
              regex_pars = c("hyper_baseline_dyn_effect"))
mcmc_parcoord(model_3_posterior_array, np = model_3_np, 
              regex_pars = c("strata_beta_day1_raw"))
mcmc_parcoord(model_3_posterior_array, np = model_3_np, 
              regex_pars = c("QR_hyper_treat_beta_dyn_effect"))
mcmc_parcoord(model_3_posterior_array, np = model_3_np, 
              regex_pars = c("cluster_beta_day1"))
```

```{r, fig.width=15}
color_scheme_set("darkgray")
mcmc_pairs(model_3_posterior_array, 
           regex_pars = c(
             "hyper_beta_day1\\[1\\]",
             "strata_beta_day1_raw\\[[1-3]\\,1",
             "strata_beta_day1_tau\\[[1-3]\\]" 
           ),
           transform = lst(
             "strata_beta_day1_tau[1]" = "log", 
             "strata_beta_day1_tau[2]" = "log",
             "strata_beta_day1_tau[3]" = "log",
           ), 
           np = model_3_np)
```

```{r, fig.width=15}
color_scheme_set("darkgray")
mcmc_pairs(model_3_posterior_array, 
           regex_pars = c(
             "strata_beta_day1_raw\\[1,1\\]",
             "strata_baseline_dyn_effect_raw\\[1,1\\]",
             # "QR_strata_beta_dyn_effect\\[1,1\\]",
             "strata_beta_dyn_effect\\[1,1\\]",
             # "QR_cluster_beta_day1\\[1,1\\]",
             "strata_beta_day1_tau\\[1\\]",
             "strata_baseline_dyn_effect_tau\\[1\\]",
             "strata_beta_dyn_effect_tau\\[1\\]",
             # "cluster_beta_day1_tau\\[1\\]",
             "lp__"
           ),
           transform = lst(
             "strata_baseline_dyn_effect_tau[1]" = "log",
             "strata_beta_day1_tau[1]" = "log",
             "strata_beta_dyn_effect_tau[1]" = "log",
             # "cluster_beta_day1_tau[1]" = "log",
           ), 
           np = model_3_np)
```

```{r, eval=FALSE, fig.width=20}
# pairs_stan(1, model_3_fit, c("hyper_beta_day1[1]", "hyper_beta_day1[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("hyper_baseline_dyn_effect[1]", "hyper_baseline_dyn_effect[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("hyper_treat_beta_dyn_effect[1]", "hyper_treat_beta_dyn_effect[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_beta_day1_tau[1]", "strata_beta_day1_tau[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_baseline_dyn_effect_tau[1]", "strata_baseline_dyn_effect_tau[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_beta_dyn_effect_tau[1]", "strata_beta_dyn_effect_tau[10]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_beta_day1_L_corr_mat_non_phone[1,2]", "strata_beta_day1_L_corr_mat_non_phone[3,1]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_beta_day1_raw[1,1]", "strata_beta_day1_raw[10,2]", "lp__"))
# pairs_stan(1, model_3_fit, c("strata_baseline_dyn_effect_raw[1,1]", "strata_baseline_dyn_effect_raw[10,2]", "lp__"))
# pairs_stan(1, model_3_fit, c("QR_strata_beta_dyn_effect[1,1]", "QR_strata_beta_dyn_effect[10,2]", "lp__"))
pairs_stan(1, model_3_fit, c("cluster_beta_day1_tau[1]", "cluster_beta_day1_tau[10]", "lp__"))
pairs_stan(1, model_3_fit, c("cluster_beta_day1_tau", "lp__"))
pairs_stan(1, model_3_fit, c("cluster_beta_day1_L_corr_mat[1,2]", "cluster_beta_day1_L_corr_mat[3,1]", "lp__"))
pairs_stan(1, model_3_fit, c("QR_cluster_beta_day1[1,1]", "QR_cluster_beta_day1[10,2]", "lp__"))
# pairs_stan(1, model_3_fit, c("[1]", "[10]", "lp__"))
```

```{r tree-energy-plots}
color_scheme_set("red")
mcmc_nuts_treedepth(model_3_np, model_3_lp)
mcmc_nuts_energy(model_3_np)
```


