---
title: |
    | Evidence from a Field Experiment in Kenya
    | The Role of Social Signaling in Community Mass Deworming^[Thanks]
subtitle: "Preliminary Findings -- Do Not Distribute"
date: "April 2017"
author:
- Anne Karing^[University of California Berkeley, `akaring@econ.berkeley.edu`.]
- Grace Morgan^[Evidence Action, `grace.morgan@evidenceaction.org`. Cost-effectiveness analysis.]
- Karim Naguib^[Evidence Action, `karim.naguib@evidenceaction.org`. Corresponding author.]
output: 
  pdf_document:
    number_sections: yes
header-includes:
   - \usepackage{pxfonts}
   - \usepackage{bbm}
   - \usepackage{setspace}
   - \usepackage{booktabs}
   - \usepackage[table]{xcolor}
   - \usepackage{pdflscape}
   - \usepackage{threeparttable}
abstract: "This report presents preliminary analysis findings for a randomized control trial (RCT) assessing the effectiveness of social incentives on adult deworming. Working with the Kenyan Government, we implemented a new community deworming program that offered free deworming treatment to adults and explicitly emphasized the public good aspect of deworming. We distributed two types of social incentives in the form of colorful bracelets and ink. The bracelets and ink made the decision to deworm or abstain from treatment observable and allowed adults to signal to others that they contributed to protecting their community from worms. We further introduced a calendar as private incentive that was comparable in its consumption value to the bracelet but could not easily be observed by others. Communities were randomized into being eligible for the ink, calendar or bracelet incentive or a control arm where no incentive was offered. In a second stage, we offered free text messages to a random subset of adults living in these communities, reminding them of the availability of free deworming treatment and providing information about deworming treatment take-up in their community. TODO conclude" 
bibliography: ~/Documents/library.bib
---

\doublespacing

```{r prelim-report-setup, include=FALSE}
library(gridExtra)
library(rgeos)
library(knitr)
library(sp)

read_chunk(purl("takeup_analysis2.Rmd")) 

opts_chunk$set(echo = FALSE, cache.path = "takeup_prelim-cache/", fig.path = "takeup_prelim-fig/", fig.align = "center", cache = TRUE)
```

```{r analysis-setup, include=FALSE, ref.label="setup", cache=FALSE}
```

```{r ggplot-theme, cache=FALSE}
theme_set(theme_minimal() +
            theme(legend.position = "bottom"))
```

```{r load-experiment-design-data}
rct.schools.data <- read_rds(file.path("data", "takeup_rct_schools.rds"))
rct.cluster.selection <- read_rds(file.path("data", "rct_cluster_selection_2.0.rds"))
cluster.strat.data <- read_rds(file.path("data", "takeup_processed_cluster_strat.rds"))

load(file.path("data", "takeup_village_pot_dist.RData"))
```

```{r load-analysis-data, ref.label="load-data"}

```

# Introduction

Over the last decade there has been important progress in the treatment of neglected tropical diseases (NTDs), as a result of unprecedented attention by governments, funders, and the private sector. The enduring prevalence of soil transmitted helminths (STHs), however, still constitutes a massive development burden for both children and adults in many developing countries, including Kenya. Recent efforts to reduce contamination rates in the country have focused on deworming school-aged children, but the remaining reservoir of worms among the adult population fosters reinfection. Epidemiologists have recently postulated that it may be scientifically feasible to reach a transmission breakpoint for STHs [@Anderson2012]. Preventing transmission and eliminating STHs using mass drug administration (MDA) covering the entire population, including children and adults, might be a viable strategy to eliminate worms moving forward. 

This study explores cost-effective ways to achieve high deworming take-up among adults by offering free deworming treatment at central locations and incentives. The evaluation of the incentivized community deworming program relates four separate strands of the literature: compliance with mass drug administration (MDA), incentives, volunatry good contributions, and pro-social signaling. 

Different to previous MDA, this study is focused on deworming treatment at a central location, not through door-to-door visits. @Kremer2011a observe that for preventive and non-acute care such as deworming, insecticide-treated bednet use and water chlorination there is a dramatic drop in demand at non-zero prices. Since a large number of people have such an abrupt cutoff at the same point, they conclude that they are not likely motivated by a simple cost-benefit analysis, but instead have a strong present bias; future benefits are heavily discounted compared to immediate benefits. One approach that has been widely tested and shown to be successful, is to provide a small reward when coming for treatment to offset any inconvenience costs individuals might face, as well as to address present bias. @Kremer2011a review a wide number of studies on the use for incentives to increase education and health service take-up. They find strong evidence in favor of incentives compared to education only interventions.

In this study we focus the program's message on social returns, emphasizing the benefit of taking treatment to reduce reinfection of community members, especially school-aged children. The community deworming program could therefore be viewed as a voluntary collective action game, where an individual's treatment compliance decision can be modeled as the decision to contribute to a pool shared by all community members. One approach to increase contribution in such a setting is to allow for signaling, thus introducing social approval/disapproval as a reward/punishment [@Benabou2006; @Benabou2012a]. Our aim is to test how social signaling can be leveraged to increase demand for deworming treatment among adults, by introducing two signals in the form of colorful ink (similar to that used for voting) and bracelets. Both allow individuals to show to others that they have taken deworming treatment. 

To test the effectiveness of social signals and to investigate the behavioral and social mechanisms driving their influence on deworming take-up, we conducted a cluster randomized trial in western Kenya, stratified over three counties. Our main experimental manipulation was the provision of private incentives (simple wall calendars) and social incentives/signals (voting ink or bracelets).  In addition, we manipulated the distance community members would have to travel to receive deworming treatment; and provided reminders or social information (on peer deworming take-up) using text messaging, randomly assigned to a subset of individuals in each community.

```{r, ref.label="basic-reg-covar"}
```

```{r, ref.label="sms-reg-covar"}
```

```{r basic-ate}
tidy.reg.res <- tidy(reg.output.sms.ctrl.covar) %>% mutate(estimate = estimate * 100)
tidy.reg.res.calendar <- tidy(reg.output.sms.ctrl.calendar.covar) %>% mutate(estimate = estimate * 100)

basic.control.takeup <- tidy.reg.res %>% 
  filter(term == "(intercept)") %$% 
  estimate

basic.calendar.takeup <- tidy.reg.res.calendar %>% 
  filter(term == "(intercept)") %$% 
  estimate

basic.bracelet.takeup <- tidy.reg.res %>% 
  filter(term %in% c("(intercept)", "bracelet")) %$% 
  sum(estimate)

basic.ink.takeup <- tidy.reg.res %>% 
  filter(term %in% c("(intercept)", "ink")) %$% 
  sum(estimate)

bracelet.vs.control.ate <- tidy.reg.res %>% 
  filter(term == "bracelet") %$% 
  estimate

bracelet.vs.calendar.ate <- tidy.reg.res.calendar %>% 
  filter(term == "bracelet") %$% 
  estimate

bracelet.vs.control.pval <- tidy.reg.res %>% 
  filter(term == "bracelet") %$% 
  p.value

bracelet.vs.calendar.pval <- tidy.reg.res.calendar %>% 
  filter(term == "bracelet") %$% 
  p.value
```

```{r sms-ate}
bracelet.sms.res <- linear_tester(reg.output.sms.treat.covar, 
                                  c("social.info + bracelet:social.info + bracelet",
                                    "(intercept) + social.info + bracelet:social.info + bracelet")) %>% 
  mutate(estimate = estimate * 100)

bracelet.sms.vs.control.ate <- bracelet.sms.res[1, "estimate"]
bracelet.sms.vs.control.pval <- bracelet.sms.res[1, "p.value"]

bracelet.sms.takeup <- bracelet.sms.res[2, "estimate"]

phone.owner.control.takeup <- tidy(reg.output.sms.treat.covar) %>% 
  filter(term == "(intercept)") %$% 
  estimate %>% 
  multiply_by(100)
```

Of the three incentive we found the bracelets to be the most effective, with a `r sprintf("%.2f", bracelet.vs.control.ate)` percentage point increase in deworming take-up, compared to the control arm (`r sprintf("%.2f%% vs %.2f%%, $P < %.3f$", basic.bracelet.takeup, basic.control.takeup, bracelet.vs.control.pval)`), a `r sprintf("%.2f", bracelet.vs.control.ate/basic.control.takeup * 100)`% change. When compared to the calendar incentive arm --- to control for the private valuation bracelets might have --- we found that bracelets increased deworming take-up by `r sprintf("%.2f", bracelet.vs.calendar.ate)` percentage point (`r sprintf("%.2f%% vs %.2f%%, $P < %.3f$", basic.bracelet.takeup, basic.calendar.takeup, bracelet.vs.calendar.pval)`), a `r sprintf("%.2f", bracelet.vs.calendar.ate/basic.calendar.takeup * 100)`% change. Other incentives did not have a statistically significant impact on take-up.

Text messages reporting peer take-up were also found to have a strong impact on deworming take-up, in particular when combined with the bracelet incentives. Take-up in response to bracelet and text messaging treatment increased take-up by `r sprintf("%.2f", bracelet.sms.vs.control.ate)` percentage points when compared to the control arm without text messaging treatment (`r sprintf("%.2f%% vs %.2f%%, $P < %.2e$", bracelet.sms.takeup, phone.owner.control.takeup, bracelet.sms.vs.control.pval)`), a `r sprintf("%.2f", bracelet.sms.vs.control.ate/phone.owner.control.takeup * 100)`% increase.

Based on our preliminary reduced form analysis, we conclude that the use of bracelets as social incentives is a promising instrument to motivate the take-up of health-related behaviors of low private value--but with some social value--such as adult deworming treatment. This is especially true when combined with an informational intervention such as text messages. While this report delves further in how distance affects take-up and how it interacts with the other experimental treatments, and what private value the study's population places on the incentives we are testing, we are not as of yet able to identify the different potential mechanisms influencing take-up. For example, while evidence points to social mechanisms, broadly speaking, as being the main influence, we are not able to distinguish between social learning (receiving information from others), social signaling (broadcasting information to other), or even if our treatments simply function as reminders or "nudges". We will consider these issues elsewhere. 

The remainder of the report is organized as follows: In section \ref{the-intervention} we describe the design of the design of the intervention and the motivation behind it; in section \ref{experiment-design} we describe the design of the experiment; in section \ref{descriptive-statistics} we provide descriptive statistics from the experiment; in section \ref{analysis} we conduct our analysis; in section \ref{cost-effectiveness} we compare the cost effectiveness of the incentives/signals tested; and finally, in section \ref{conclusion} we discuss our findings and present our conclusions.

# The Intervention

Working with the Government of Kenya we offered free deworming treatment to adults in 3 counties in western Kenya: Busia, Kakamega and Siaya County. Community Health Volunteers (CHVs) provided the treatment at central locations and sensitized households about the upcoming deworming treatment. CHVs informed all study communities one week prior to the start of the deworming treatment about the social benefits of deworming, when and where free deworming treatment will be available and if applicable what type of incentive will be given to adults when coming for treatment. Pamphlets were handed out to community members and posters were placed in prominent locations. 

Deworming treatment was subsequently offered at central locations, from 8am to 5pm, for a period of 12 days. For logistical reasons, we split deworming treatment into two waves: the first deworming wave was from October 3 to 14 in Busia and Siaya County, and the second wave was from October 24 to November 4 in Kakamega County. Depending on the a cluster's assigned treatment, individuals who came for deworming were either only dewormed or were dewormed and either 

(i) required to receive a mark on their hand using indelible ink as is normally done when voting, 
(ii) given a simple one page wall calendars, with a design unrelated to deworming, as a gift, or
(iii) given a silicon bracelet as a bracelet.

All adults who came to a treatment location were provided with deworming (and applicable incentives/signals) irrespective of where they live; we did not provide treatment only to the communities targeted by the informational campaign^[This was particularly important since nearly half of all clusters' targeted villages were assigned a treatment location in another village.] or require individuals to receive treatment in their home cluster. After treatment, all individuals were asked brief questions by research enumerators.

Central locations were picked to be easy locatable by targeted community members, either in their own villages or in neighboring villages. We initially selected treatment locations to be adjacent to primary schools because of their prominence and ubiquity (more on this below). However, the Ministry of Education did not permit us to operate in such close proximity to schools, so we decided to use alternative locations (such as churches) that are not too far from the originally selected schools^[The Ministry of Education prohibited any social activities within or near primary schools to prevent cheating in exams. During the treatment location survey, we had collected information on backup locations.].

During the informational campaign conducted by CHVs prior to the MDA, we also recruited a random sample of individuals from different households to receive informational text messages about the MDA (see the [Experiment Design](#experiment-design) section). Messages were sent to all recruited subjects a day before the MDA with information on where to find their treatment locations. After that, messages were sent every other day (on the second, fourth, sixth, eight and tenth deworming day). 

CHVs were trained by their supervising Community Health Extension Workers (CHEWs), who also handled the distribution and recovery of deworming drugs. Thus our study was focused on the social aspects of the intervention, e.g., the framing of deworming as a public good and the use of private or social incentives to encourage take-up. We were not involved with the medical aspects of deworming, for which we coordinated with national and local health officials. 

# Experiment Design

We randomly selected 158 clusters in the three study counties, of which 144 were used in the study^[We only intended to use 150 clusters, and only included eight extra clusters as fallback clusters. For various practical reasons, implementation was only possible in 144 clusters.]. We relied on the high geographic density of primary schools in the study counties to select both treatment locations and targeted villages^[Geographic coordinates for primary schools were retrieved from the Kenya Open Data Portal (<http://www.opendata.go.ke/>).]. Each cluster is defined as a treatment location and targeted village pair. We used the location of primary schools as proxies for communities, so that we can identify acceptable locations (i) to set up our treatment locations and (ii) to find villages to target with our informational campaign and data collection.

To pick our clusters from the pool of all primary schools in our study area (a total of 1,451 schools), we used an acceptance-rejection method whereby we randomly picked schools, checked their acceptability based on their overlap with already selected clusters, and if accepted added them to our selected sample. This process was repeated until we had selected the requisite number of clusters. If no acceptable schools remained before completion, the whole process was restarted. Each cluster, centered on its treatment location, had a 2.5 kilometer radius _catchment circle_ and 3-4 kilometer radius _buffer circle_ (buffer sizes were randomly assigned). A cluster was considered acceptable if its _buffer circle_ did not leave any of the already selected clusters' nonoverlapped _catchment circles_ smaller than an a pre-specified size (with about one primary school nonoverlapped).

```{r all-clusters-map, message=FALSE, fig.width=6, fig.height=6, fig.cap="Map of Initial Cluster Selection. Black crosses (+) indicate the selected treatment locations, while the grey regions indicate the nonoverlapped catchment circles from which we selected village(s) to target."}
ggplot.clusters(rct.cluster.selection, include.cluster.ids = FALSE, source = "stamen", maptype = "toner") 
```

After all clusters were selected, we randomly assigned (stratified within counties) each cluster to be either a "close" or "far" cluster: whether its targeted village would be less or more than 1.25 kilometers away from the the treatment location, respectively. We then selected for each cluster, from its nonoverlapping _catchment circle_ and according to its assigned distance treatment, a primary school as an anchor for us to locate its targeted village^[For further details on the cluster selection algorithm refer to the study's pre-analysis plan [@Karing2016].]. Figures \ref{fig:dist-to-pot} and \ref{fig:marginal-dist-to-other-pot} show the distribution of cluster distance to treatment locations and to other clusters. 

```{r dist-to-pot, echo=FALSE, fig.width=6, fig.height=3, fig.cap="Distance to Treatment Locations"}
verify.vill.pot.dist %>% 
  select(dist.to.own.pot, closest.other) %>% 
  gather(dist.type, dist) %>% {
  ggplot(.) +
    geom_histogram(aes(dist, fill = dist.type), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = alpha("black", 0.5), position = "dodge") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 5)) +
    scale_fill_discrete("Distance", labels = c("To Closest Other Treatment Location", "To Assigned Treatment Location")) 
}
```

```{r dist-to-other-pot, fig.width=6, fig.height=2, fig.cap="Distance to Closest Other Point-of-Treatment", eval=FALSE}
verify.vill.pot.dist %>% { 
  ggplot(.) +
    geom_histogram(aes(closest.other), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = "black") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 2)) 
} 
```

```{r marginal-dist-to-other-pot, fig.height=2.5, fig.width=6, fig.cap="Marginal Distance to Closest Other Treatment Location. Dashed vertical lines indicate the 10th, 25th, 50th, 75th, and 90th percentiles of the distribution."}
verify.vill.pot.dist %>% 
  mutate(marginal.dist = closest.other - dist.to.own.pot,
         dist.to.own.pot.cat = cut(dist.to.own.pot, 
                                   breaks = c(0,  2500/2, 10000),
                                   labels = c("Close", "Far"))) %>% {
  ggplot(.) +
    geom_histogram(aes(marginal.dist), alpha = 0.5, color = alpha("black", 0.5), binwidth = 500, boundary = 0, position = "dodge") +
    scale_y_continuous("Number of Clusters", breaks = seq(0, 50, 2)) +
    scale_x_continuous("", breaks = seq(-1000, 10000, 1000)) +
     geom_vline(xintercept = quantile(.$marginal.dist, probs = c(0.1, 0.25, .5, 0.75, 0.9)), linetype = "dashed", alpha = 0.5)
}
```

Clusters were then randomly assigned, stratified over counties and distance treatment, an incentive/signal treatment: 

(i) Control: no incentives or public signals
(ii) Indelible ink: a mandatory signal of treatment
(iii) Calendar: a private low-value gift 
(iv) Bracelet: a low-value gift and public signal 

To finalize the cluster selection process, we surveyed the treatment location and target village anchor schools. For the treatment locations we confirmed that treatment would be feasible there and identified an alternative treatment locations, not far from the selected schools, as backups. For the anchor schools, we identified all the villages near them. From each cluster's candidate villages we randomly selected a village to target (in some cases because the initial village was too small, we added a second village).

For each village selected for targeting we then conducted a census of all adult community members (18 years of age or older). Enumerators visited all the households in selected villages, captured their geographic coordinates, and filled a roster of all household members, enought to identify them if sampled in later stages and to stratify over relevant characteristics (e.g., phone ownership, relevant for text message treatment).

Using the census lists we drew a number of samples for data collection. All individuals who were in these samples were collectively put the _monitored_ group. At the treatment location, individuals who were treated were asked some quick identifying questions (name, age, etc.), and if they were found to match someone in the _monitored_ group we made a record of their treatment. This is the group for whom we estimate the probability of take-up in our analysis. Except for those in the baseline survey sample, all individuals were not informed about their participation in a study (incomplete disclosure), and therefore we needed to get their reconsent after the study was completed.

### Baseline survey sample {-}

Before the intervention started, we aimed to conduct baseline surveys with 15 individuals (from unique households) per cluster^[The actual number of individuals that were located varied for all the samples.]. The baseline survey questionnaire covered topics such as:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others
c) Beliefs about one's own and others' deworming decisions in response to an MDA, and how that decision is affected by others' choices
d) Beliefs about one's own and others' reputation if infected and treated
e) Past experience with deworming treatment

### Text message sample {-}

As described above, in the [Intervention](#the-intervention) section, we recruited individuals to receive informational text messages. We aimed to recruit 30 individiuals per cluster in the control arm and 25 individuals per cluster in the treated arms. In the control arm, we broke the sample into two groups of 15, one received reminder messages only, and the other got reminders and social information -- they were told about the take-up of their community members up to the day of the message^[Peer take-up was described both as "few", "almost half", "almost everyone", etc., and as a "$n$ in 10" proportion.]. In the treated arms, all individuals received social information messages. All text messages recipients were reminded about where the treatment location is.

Naturally, this sample was drawn from the population of phone owners, from which we also drew a comparator "control" sample, not receiving any text messages, and included in the _monitored_ group. We also drew a sample of text message "control" individuals from the non phone owners population. In other words, the sampling of monitored individuals not receiving any text messages was stratified over phone ownership.

### Endline survey sample {-}

After the intervention was concluded, we aimed to conduct endline surveys with the 25 individuals per cluster, selected according to the following schedule:

* From the sample of those not receiving text messages:
    - 15 individuals per cluster in the control arm
    - 20 individuals per cluster in the treated arms
* From the sample of those receiving reminder messages only:
    - 5 individuals per cluster 
* From the sample of those receiving social information messages:
    - 5 individuals per cluster 
   
Since not all individuals responding to the endline survey also responded to the baseline survey, some questions overlapped between the two questionnaires. The endline survey questionnaire covered topics such as:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others
c) Knowledge of the MDA intervention: location, start date, and duration of treatment; where respondent got dewormed; how did respondent learn about the MDA; and if they were contacted about a CHV or text messaging
d) Questions testing knowledge of peer deworming: 
    i. Respondents were incentivized to estimate how many of their community members got dewormed.
    ii. Respondents were explicitly asked about their relationship with and their knowledge of deworming status of ten other individuals or pairs of individuals in their community^[We randomly asked respondents about individuals or pairs of individuals, in an effort to overcome potential aversion to disclosing negative information about peers.].
    
All individuals who responded to the endline survey were also asked to reconsent to having their observed take-up status used in our study. The study was explained to them, as well as the reason for not informing about the participation in it prior to the endline survey.

### Reconsent only sample {-}

All remaining individuals in the text message sample (recipients and non-recipients of messages) and who are not in the endline survey sample were visited to to ask for reconsent in the same manner as the endline survey sample. The baseline survey sample was reconsented if they overlapped with any of the other sample. Thus, we were table to observe deworming take-up for a mix of individuals who did and did not respond to a baseline survey.

### Willingness-to-pay survey sample {-}

In order to assess individuals' private valuation of the calendar and bracelet incentives, we conducted willingness-to-pay surveys with a sample of subjects in the control arm who have neither responded to any endline survey nor have they received any text messaging treatment. We randomly selected 25 individuals from each of 24 randomly selected control communities. Respondents were asked to choose one of the two incentives as a gift, revealing their preference. Subsequently, they were offered a random cash amount for them to switch the other incentive, allowing us to estimate the difference in the incentives' price value. 

# Descriptive Statistics 

In this section we will present some descriptive statistics and plots, using data collected from the various study surveys. 

```{r cluster-stats}
cluster.stats <- census.data %>%
  filter(!is.na(cluster.id)) %>%
  left_join(select(cluster.strat.data, cluster.id, dist.pot.group), "cluster.id") %>% 
  arrange(county) 

calc.cluster.stats <- . %>% 
  count(county, assigned.treatment) %>% 
  ungroup %>% 
  spread(assigned.treatment, n) %>% { 
    total <- select(., -county) %>% mutate_all(as.integer) %>% rowSums 
    mutate(., all = total) 
  }

clusters.stats <- cluster.stats %>% 
  distinct(cluster.id, .keep_all = TRUE) %>% 
  calc.cluster.stats %>%
  set_names(str_to_title(names(.))) 

individ.stats <- cluster.stats %>% 
  calc.cluster.stats %>% 
  set_names(str_to_title(names(.))) 
```

\begin{table}
\centering
\caption{Number of clusters and individuals in targeted communities, by county and treatment arm.}
\begin{tabular}{l*{10}{c}}
\toprule
       & \multicolumn{5}{c}{Clusters} & \multicolumn{5}{c}{Individuals} \\ \\
County & Control & Ink & Calendar & Bracelet & All & Control & Ink & Calendar & Bracelet & All \\
\cmidrule(r){2-6} \cmidrule(r){7-11}

```{r cluster-stats-tab, results="asis"}
clusters.stats %>%
  left_join(individ.stats, "County", suffix = c(".clusters", ".individuals")) %>% 
  a_ply(1, function(row) sprintf("%s %s \\\\\n", 
                                 row$County,
                                 paste(sprintf(" & %s", prettyNum(as.integer(row[, -1]), big.mark = ",")), collapse = "")) %>% 
          cat)
  
```
\bottomrule
\end{tabular}
\end{table}

By the end of the intervention, we had recorded the deworming treatment of approximately 97,000 individuals. Figure \ref{fig:absolute-takeup} shows how much absolute take-up there was, split by assigned incentive treatment, assigned distance to treatment location, and county. While the pattern of take-up is similar to what we will find in our formal analysis, we are not making any causal interpretations based on these findings. The aim of this study is to learn about impact on the _proportion_ of take-up in targeted communities, and therefore an analysis based on absolute figures would be misleading as we do not have information of what communities all treated individuals are from.

```{r absolute-takeup, fig.height=6, fig.cap="Absolute Deworming Take-up"}
plot.aggreg.takeup <- function(.data) {
  ggplot(.data, aes(assigned.treatment)) +
    geom_bar(alpha = 0.5, color = alpha("black", 0.5)) +
    labs(x = "Treatment", y = "Number of Individuals Dewormed (x 100)", caption = "Note: range on Y axis varies between counties.") +
    facet_grid(county.randomization ~ dist.pot.group, scales = "free_y", margins = TRUE) +
    scale_y_continuous(labels = . %>% divide_by(100)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

takeup.data %>% 
  mutate_at(vars(dist.pot.group, assigned.treatment), funs(factor(.) %>% fct_relabel(str_to_title))) %>% 
  plot.aggreg.takeup 
```

As descibed in the [Experiment Design](#experiment-design) section, clusters were randomly assigned to be either _close_ or _far_ from the treatment location. Due to small changes in the actual location of treatment and the dispersion of households within targeted areas, actual distances the had the spread seen in Figure \ref{fig:actual-distance}. While there does appear to be some slight overlap or non-compliance with assigned treatment, this should not affect the intention-to-treat analysis carried in this report.

```{r actual-distance, fig.width=8, fig.cap="Distribution of actual distance from targeted villages and their assigned treatment location."}
analysis.data %>%  
  anti_join(outlier.clusters, c("sms.treatment", "cluster.id")) %>% 
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% 
  ggplot(aes(dist.to.pot)) +
  geom_density(aes(color = dist.pot.group, linetype = "Household")) +
  geom_density(aes(color = dist.pot.group, linetype = "Cluster Center"),
               data = mutate(village.centers, assigned.treatment = fct_relabel(assigned.treatment, str_to_title))) +
  geom_vline(xintercept = c(1250), linetype = "dashed") +
  labs(y = "Density", 
       caption = "Cluster centers were calculated as the centroid location of all households in cluster.") +
  scale_x_continuous("Distance to Treatment Location (meters)", breaks = seq(0, 10000, 2500/4)) +
  scale_color_discrete("Cluster Distance Assignment", labels = c("Close", "Far")) +
  scale_linetype_discrete("Distance From") +
  facet_wrap(~ assigned.treatment)
```

```{r mean-assigned-dist, warning=FALSE}
analysis.data %>%  
  anti_join(outlier.clusters, c("sms.treatment", "cluster.id")) %>% 
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% {
    bind_rows(group_by(., assigned.treatment, dist.pot.group) %>%
                summarize(mean.dist = mean(dist.to.pot)) %>%
                ungroup,
              group_by(., dist.pot.group) %>% 
                summarize(mean.dist = mean(dist.to.pot), assigned.treatment = "(All)") %>% 
                ungroup)
  } %>% 
  spread(dist.pot.group, mean.dist) %>% 
  mutate(mean.dist.diff = far - close) %>% 
  kable(col.names = c("Arm", "Close", "Far", "Mean Difference"), 
        caption = "Mean Distance to Treatment Location (meters)",
        format = "latex", align = "lccc", booktabs = TRUE, longtable = FALSE, format.args = list(big.mark = ",")) 
```

Figure \ref{fig:know-believe-categorical-responses} presents individuals' responses to some of the baseline and endline survey questions. Comparing reported knowledge and beliefs of surveyed individuals, the most significant change appears to be the understanding of who is at risk of worm infection. More people are reporting after the intervention the belief that everyone is at risk of worm infection, compared to before. Surprisingly, there seems to be a decrease in the understanding that individuals can infection one another.

```{r know-believe-categorical-responses, warning=FALSE, fig.width=8, fig.height=10, fig.cap="Knowledge and beliefs baseline and endline survey responses."}
tribble(~ col.name,      ~ label,
        "who_worms",     "Who is at risk of worms?",
        "effect_worms",  "What are the effects of worms?",
        "spread_worms",  "Can an infected person spread worms to other?",
        "how_spread",    "How are worms spread?",
        "stop_worms",    "How to stop worms?",
        "when_treat",    "When should people get dewormed?",
        "worms_affect",  "If infected, can you affect others' health?",
        "neighbours_worms_affect", "Can neighbors or relatives worm infection affect your health?") %>% 
  multi.know.bel.cat.plot() +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

```{r general-desc-stats, fig.width=8, fig.height=5, warning=FALSE, fig.cap="Study population summary statistics"}
gen.stats.plot <- tribble(~ col.name,       ~ label,
        "gender",         "Gender",
        "ethnicity2",      "Ethnicity",
        "school",         "Schooling",
        "floor",          "Home floor construction",
        "have_phone",     "Own mobile phone?") %>%
  multi.know.bel.cat.plot(.census.data = census.data %>% mutate(gender = factor(gender, levels = 1:2, labels = c("Male", "Female"))),
                          preprocess.fun = . %>% mutate(response = fct_relevel(response, rev(levels(baseline.data$school)))),
                          na.rm = TRUE)

age.density.plot <- list(Census = mutate(census.data, age = age.census), 
                         Baseline = baseline.data, 
                         Endline = endline.data) %>% 
  map_df(~ select(., age), .id = "survey.type") %>% 
  mutate(survey.type = factor(survey.type, levels = c("Census", "Baseline", "Endline"))) %>% 
  ggplot(aes(survey.type, age, color = survey.type)) +
  geom_boxplot() +
  coord_flip() +
  scale_y_continuous("Age Box Plot", breaks = seq(15, 100, 5)) +
  labs(x = "") +
  theme(legend.position = "none")

grid.arrange(gen.stats.plot, age.density.plot, layout_matrix = as.matrix(c(1, 1, 1, 1, 2)))
```

Figure \ref{fig:dewormed-history} presents individuals' reported deworming history, prior to the intervention. Unsurprisingly, the majority of respondents said that children in their families have been previously dewormed, and the most common location for treatment for their family members had been during the annual school-based MDA. We also see that almost two of adults had been previously dewormed. However, more than half of those reporting prior treatment, were treated over two years ago. Furthermore, most adults reported getting dewormed at a hospital/clinic or purchased medication.

```{r dewormed-history, fig.width=8, fig.height=9, fig.cap="Deworming history."}
ever.dewormed.plot <- baseline.data %>% 
  select(treated, family_treated) %>% 
  gather(key = who.treated) %>% 
  mutate(who.treated = if_else(who.treated == "treated", "Self", "Family")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>%
  ungroup %>%
  mutate(value = fct_recode(factor(value), "Don't Know" = "DK") %>% 
             fct_relabel(str_to_title) %>% 
             fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Ever been dewormed before?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

who.was.dewormed.plot <- baseline.data %>% 
  select(family_treated, who_treated) %>% 
  filter(family_treated == "yes") %>% 
  mutate(who_treated = fct_relabel(factor(who_treated), str_to_title)) %>% 
  ggplot(aes(who_treated)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "Who in family got dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

when.dewormed.plot <- baseline.data %>% 
  transmute(treated, 
            treated_when = fct_relabel(factor(treated_when), str_to_title)) %>% 
  filter(treated == "yes") %>%
  ggplot(aes(treated_when)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "When did you last get dewormed?", x = "", y = "Proportion")

where.treated.plot <- baseline.data %>% 
  select(treated, family_treated, treated_where, where_family_treated) %>% 
  gather(key = who.treated, value = value, -c(treated, family_treated)) %>% 
  mutate(who.treated = if_else(who.treated == "treated_where", "Self", "Family")) %>% 
  filter((who.treated == "Self" & treated == "yes") | (who.treated == "Family" & family_treated == "yes")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>% 
  ungroup %>% 
  mutate(value = fct_recode(value, "Don't Know" = "DK") %>% 
           fct_relabel(str_to_title) %>% 
           fct_relabel(function(.label) str_replace_all(.label, "Mda", "MDA")) %>% 
           fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Where did you last get dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

grid.arrange(ever.dewormed.plot, who.was.dewormed.plot, when.dewormed.plot, where.treated.plot, 
             layout_matrix = as.matrix(c(1, 1, 2, 3, 3, 4, 4)))
```

Since the study's main research questions focus on the social impact of signals, incentives and information, we included a number of questions in our surveys to get a clearer picture of how individuals perceive and predict others' deworming choices. Figure \ref{fig:response-other-deworm} shows individuals reporting that their own deworming decisions would not be influenced by others' decisions, as well as having a strong _intention_ to getting dewormed. In addition, as shown in Figure \ref{fig:baseline-deworming-beliefs}, people predicted similar deworming among peers. As we will see below, most people overestimated their own and others' deworming take-up. Finally, when individuals were asked about how others would respond to the use of indelible ink as a signal of deworming treatment, they predicted a positive effect, contrary to what we actually observed. 

```{r survey-of-10-beliefs, ref.label="survey-of-10-beliefs", warning=FALSE}
```

```{r survey-of-10-beliefs-boxplot, ref.label="survey-of-10-beliefs-boxplot", warning=FALSE}
```

We also inquired about respondents' social perception/judgement of some of others' behaviors (some more observable than others). We wanted to compare attitudes towards deworming and other behaviors such as wearing nice clothes to church, using latrines, and immunizing children. Individuals were presented with difference scenarios and were asked whether they would inspire praise or stigma. Figure \ref{fig:praise-stigma-plot} shows that deworming during the MDA is reported to be as highly praiseworthy as the use of latrines and immunization children, more praise worthy than wearing nice clothes to church. In terms of stigma, failing to get dewormed is slightly lower than open defecation and not immunizating children, but much higher than not wearing nice clothes to church.

To verify that the targeted communities were properly informed about the MDA we asked endline survey respondents a few questions to test their knowledge, presented in Figure \ref{fig:know-about-mda}. Responses indicate good knowledge of the MDA and start and end dates. The majority reported learning about the MDA from CHVs, and few said they were informed by other social contacts such as barazas, churches, family and friends. Posters did not appear to be very successful. Overall, the MDA's informational campaign, spearheaded by CHVs, was successful at reaching most community members.

```{r praise-stigma, ref.label="praise-stigma"}
```

```{r response-other-deworm, warning=FALSE, fig.width=8, fig.height=2.5, fig.cap="Reported response to others' deworming choices."}
tribble(~ col.name,      ~ label,
        "few_deworm",     "Deworm if less than half of others deworm?",
        "many_deworm",    "Deworm if more than half of others deworm?",
        "more_less",      "Would you be more likely to deworm if few/many others get dewormed?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

```{r baseline-deworming-beliefs, warning=FALSE, fig.width=8, fig.height=5, fig.cap="Baseline beliefs/predictions about others' deworming choices."}
other.predict.deworm.plot <- tribble(~ col.name,              ~ label,
                                     "dworm_proportion",      "How many people will come to get dewormed?",
                                     "ink_more_less",         "Will the ink signal increase/decrease deworming take-up?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL,
                          preprocess.fun = . %>% 
                            mutate(response = fct_relevel(response,
                                                          "Few", "Nearly Half", "Half", "More Than Half", "Many", "All", "Less", "Same", "More", "Prefer Not Say", "Don't Know"))) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  labs(title = "Peer deworming predictions")

survey.takeup.beliefs.10.boxplot <- survey.takeup.beliefs.10.boxplot + theme(legend.position = "none")
survey.takeup.beliefs.10 <- survey.takeup.beliefs.10 + theme(legend.position = "right")

grid.arrange(other.predict.deworm.plot, survey.takeup.beliefs.10, survey.takeup.beliefs.10.boxplot, 
             layout_matrix = rbind(c(1, 1, 1, 1), c(2, 2, 3, 3)))

```

```{r praise-stigma-plot, fig.width=8, fig.height=3, fig.cap="Reported social perception of some observable activities."}
plot(praise.stigma.plot) 
```

```{r mda-dates-dist, ref.label="mda-dates-dist"}
```

```{r know-about-mda, warning=FALSE, fig.width=8, fig.height=6, fig.cap="Knowledge of RCT intervention."}
know.mda.cat.plot <- tribble(~ col.name,      ~ label,
        "know_deworm",    "Know about community-based MDA?",
        "treat_begin",    "Know when MDA starts?",
        "treat_end",      "Know when MDA ends?",
        "days_available", "Know length of MDA?",
        "find_out",       "From whom or how did you learn about the MDA?",
        "chv_visit",      "Did a CHV visit you to tell you about MDA?") %>% 
  multi.know.bel.cat.plot(.baseline.data = NULL, .census.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 

mda.dates.dist.plot <- mda.dates.dist.plot + theme(legend.position = "right")

grid.arrange(know.mda.cat.plot, mda.dates.dist.plot, layout_matrix = as.matrix(c(1, 1, 1, 2, 2)))
```

## Revealed Preferences for Incentives

In order to distinguish between the private and social motivation of incentives/signals, we asked endline survey respondents some questions on their preferences for calendars and bracelets, and separately conducted a [willingness-to-pay survey](#willingness-to-pay-survey-sample) in the control arm. The identification challenge for us is separating between 

a) _private valuation_, individuals like it for its intrinsic value, and 
b) _social valuation_, individuals are affected by braclets either because they they want to broadcast their deworming or are receiving information on observing others deworming.

Figure \ref{fig:gift-plots} reports which incentive (bracelet or calendar) individuals preferred as a gift during the endline survey. Calendars are typically preferred by all except for those already dewormed or live in the same household as someone who already received a calendar (in the calendar treatment arm). Similarly, in the willingness-to-pay survey, we found that the majority of individuals preferred calendars to bracelets (Figure \ref{fig:wtp-plots}). Therefore, we are not concerned that bracelets could have influenced take-up only as a consumption good. 

```{r reported-gift-pref-deworm, ref.label="reported-gift-pref-deworm"}
```


```{r other-incentive-plot, ref.label="other-incentive-plot"}
```

```{r first-choice-wtp, ref.label="first-choice-wtp"}
```

```{r switch-price-wtp, ref.label="switch-price-wtp"}
```

```{r gift-plots, fig.height=7, fig.width=9, fig.cap="Reported calendar/bracelet preferences, split by experiment arm and respondents' deworming take-up."}
grid.arrange(reported.gift.pref.dewormed.plot, other.have.incentive.plot, 
             layout_matrix = as.matrix(c(1, 1, 2, 2, 2)))
```

```{r wtp-plots, fig.width=8, fig.cap="Willingness-to-pay survey responses."}
switch.price.plot <- switch.price.plot + theme(legend.position = "right")

grid.arrange(first.choice.wtp.plot, switch.price.plot, 
             layout_matrix = as.matrix(c(1, 1, 2, 2, 2, 2, 2))) 
```

# Analysis

In this section we conduct a reduced form regression analysis in order identify the causal impact of cluster assigned incentive/signal treatment; cluster assigned distance to treatment location; and individually assigned SMS reminder and information treatment. We use the regression approach proposed by @Imbens2015 to analyze stratified experiments:

\begin{equation*}
Y_{ij} = m_K(Z_j, D_j, M_{ij}, B_j, X_{ij};\theta_K) \cdot \frac{B_{j}(K)}{N(K)/N} + \sum_{k=1}^{K-1} m_k(Z_j, D_j, M_{ij}, B_j, X_{ij};\theta_k) \cdot \left( B_{j}(k) - B_{j}(K)\cdot\frac{N(k)}{N(K)} \right) + \varepsilon_{ij},
\end{equation*}
where the stratum specific model is
\begin{align*}
m_k(Z_j, D_j, M_{ij}, B_j; \theta) &= \alpha_k + X_{ij}\cdot \beta_k + \delta_k \cdot D_j \\
&+ \sum_{z \in \mathcal{Z}\setminus \{control\}} Z_{j}(z) \cdot \left\{\tau_k(z) + \lambda_k(z) \cdot D_j + \sum_{s \in \mathcal{M}\setminus \{none\}} M_{ij}(s) \cdot \left[ \gamma_k(z, s) + \rho_k(z, s) \cdot D_j \right] \right\} \\ 
&+ \sum_{s\in\mathcal{M}\setminus \{none\}}  M_{ij}(s) \left\{\psi_k(s) + \pi_k(s) \cdot D_j \right\}  
\end{align*}

* $i$ indexes individuals, $j$ clusters
* $Z_j \in \mathcal{Z} = \{ control, ink, calendar, bracelet \}$
* $M_{ij} \in \mathcal{M} = \{ none, reminders, socialinfo \}$
* $Z_{j}(z) = \mathbf{1}\{Z_j = z\}$ is an indicator for whether cluster $j$ was assigned treatment $z$.
* $B_{j}(k) = \mathbf{1}\{B_j = k\}$ is an indicator for whether cluster $j$ is in stratum $k$.
* $X_{ij}$ is a vector of covariates
* $N(k)$ is the size of stratum $k$.
* $N$ is the total number of observations

A typical parameter $\theta_k(z, s)$ captures the effect of $Z_j = z$ and $M_{ij} = s$ in stratum $k$. The super-population average treatment effects are estimated by the stratum $K$ parameters. Since this is linear probability model, average treatment effects are interpreted as the change in an individual's probability of deworming (or the proportion of the super-population doing so).

```{r basic-reg, ref.label="basic-reg"}
```

```{r dist-reg, ref.label="dist-reg"}
```

```{r dist-reg-covar, ref.label="dist-reg-covar"}
```

```{r sms-reg, ref.label="sms-reg"}
```

```{r dist-sms-reg, ref.label="dist-sms-reg"}
```

```{r sms-dist-reg-covar, ref.label="sms-dist-reg-covar"}
```

```{r reg-tab-data, include=FALSE}
reg.table.data <- list("Monitored, No SMS" = reg.output.sms.ctrl, 
                       "Endline, No SMS" = reg.output.sms.ctrl.covar) %>% 
  map_df(function(reg.res) {
    joint.tests.res <- list("Any Treatment" = c("ink", "calendar", "bracelet"),
                            "Signaling Treatment" = c("ink", "bracelet")) %>% 
      map_df(~ linear_tester(reg.res, .x, joint = TRUE), .id = "joint.test.type") %>% 
      select(-starts_with("linear.test")) %>% 
      mutate(joint.test.type = forcats::as_factor(joint.test.type))
    
    tidy(reg.res) %>% 
      bind_rows(control = .,
                calendar = linear_tester(reg.res, c("(intercept) + calendar", "bracelet - calendar")) %>% 
                  mutate(term = c("calendar", "bracelet")),
                .id = "ref.type") %>% 
      mutate(term = fct_recode(factor(term), control = "(intercept)"),
             ref.pt = term == ref.type) %>% 
      list %>% 
      tibble(pt.est = .,
             num.col = n_distinct(.[[1]]$ref.type),
             joint.tests.res = list(joint.tests.res),
             num.obs = length(reg.res$fitted.values),
             num.clusters = length(unique(reg.res$cluster)),
             average.cluster.num.obs = mean(table(reg.res$cluster)),
             r.squared = r_squared(reg.res, adjusted = FALSE),
             adj.r.squared = r_squared(reg.res))
    
  }, .id = "spec") 
 
dist.reg.table.data <- list("Monitored, No SMS" = reg.output.sms.ctrl.dist,
                            "Endline, No SMS" = reg.output.sms.ctrl.dist.covar) %>% 
  map_df(function(reg.res) {
    joint.tests.res <- list("Any Treatment" = c("ink", "calendar", "bracelet", "ink:far", "calendar:far", "bracelet:far"),
                            "Signaling Treatment" = c("ink", "bracelet", "ink:far", "bracelet:far")) %>% 
      map_df(~ linear_tester(reg.res, .x, joint = TRUE), .id = "joint.test.type") %>% 
      select(-starts_with("linear.test")) %>% 
      mutate(joint.test.type = forcats::as_factor(joint.test.type))
    
    tidy(reg.res) %>% 
      filter(!str_detect(term, ":")) %>%
      bind_rows(linear_tester(reg.res, c("ink + ink:far", "calendar + calendar:far", "bracelet + bracelet:far")) %>% 
                  mutate(term = c("ink:far", "calendar:far", "bracelet:far"))) %>% 
      bind_rows(control = .,
                calendar = linear_tester(reg.res, c("(intercept) + calendar", "bracelet - calendar")) %>% 
                  mutate(term = c("calendar", "bracelet")),
                far = linear_tester(reg.res, c("(intercept) + far",
                                               "ink + ink:far", "calendar + calendar:far", 
                                               "bracelet + bracelet:far")) %>% 
                  mutate(term = c("far", "ink:far", "calendar:far", "bracelet:far")),
                "calendar:far" = linear_tester(reg.res, c("(intercept) + far + calendar + calendar:far", 
                                                          "bracelet + bracelet:far - calendar - calendar:far")) %>% 
                  mutate(term = c("calendar:far", "bracelet:far")),
                .id = "ref.type") %>% 
      mutate(term = fct_recode(factor(term), control = "(intercept)"),
             ref.pt = term == ref.type) %>% 
      list %>% 
      tibble(pt.est = .,
             num.col = n_distinct(.[[1]]$ref.type),
             joint.tests.res = list(joint.tests.res),
             num.obs = length(reg.res$fitted.values),
             num.clusters = length(unique(reg.res$cluster)),
             average.cluster.num.obs = mean(table(reg.res$cluster)),
             r.squared = r_squared(reg.res, adjusted = FALSE),
             adj.r.squared = r_squared(reg.res))
    
  }, .id = "spec") 

sms.reg.table.data <- list("Monitored, SMS" = reg.output.sms.treat,
                           "Endline, SMS" = reg.output.sms.treat.covar) %>% 
  map_df(function(reg.res) {
    joint.tests.res <- list("Any Incentive Treatment" = c("ink", "calendar", "bracelet", 
                                                          "ink:social.info", "calendar:social.info", "bracelet:social.info"),
                            "Any SMS Treatment" = c("reminder.only", "social.info",
                                                    "ink:social.info", "calendar:social.info", "bracelet:social.info"),
                            "Signaling Treatment" = c("ink", "bracelet", "ink:social.info", "bracelet:social.info")) %>% 
      map_df(~ linear_tester(reg.res, .x, joint = TRUE), .id = "joint.test.type") %>% 
      select(-starts_with("linear.test")) %>% 
      mutate(joint.test.type = forcats::as_factor(joint.test.type))
    
    tidy(reg.res) %>% 
      filter(!str_detect(term, ":")) %>% 
      bind_rows(linear_tester(reg.res, c("ink", "calendar", "bracelet") %>% paste(., paste0(., ":social.info"), sep = " + ")) %>% 
                  mutate(term = paste0(c("ink", "calendar", "bracelet"), ":social.info"))) %>% 
      bind_rows(control = .,
                calendar = linear_tester(reg.res, c("(intercept) + calendar", "bracelet - calendar", "social.info + calendar:social.info")) %>% 
                  mutate(term = c("calendar", "bracelet", "calendar:social.info")),
                reminder.only = linear_tester(reg.res, c("(intercept) + reminder.only", "social.info - reminder.only")) %>% 
                  mutate(term = c("reminder.only", "social.info")),
                ink = linear_tester(reg.res, c("(intercept) + ink", "social.info + ink:social.info")) %>% 
                  mutate(term = c("ink", "ink:social.info")),
                bracelet = linear_tester(reg.res, c("(intercept) + bracelet", "social.info + bracelet:social.info")) %>% 
                  mutate(term = c("bracelet", "bracelet:social.info")),
                # social.info = linear_tester(reg.res, c("(intercept) + social.info", 
                #                                        "ink:social.info", 
                #                                        "calendar:social.info", 
                #                                        "bracelet:social.info")) %>% 
                #   mutate(term = c("social.info", 
                #                   "ink:social.info", 
                #                   "calendar:social.info", 
                #                   "bracelet:social.info")),
                # "calendar:social.info" = linear_tester(reg.res, c("(intercept) + social.info + calendar:social.info", 
                #                                                   "bracelet:social.info - calendar:social.info", 
                #                                                   "ink:social.info - calendar:social.info")) %>% 
                #   mutate(term = c("calendar:social.info", 
                #                   "bracelet:social.info", 
                #                   "ink:social.info")),
                # "ink:social.info" = linear_tester(reg.res, c("(intercept) + social.info + ink:social.info", 
                #                                              "bracelet:social.info - ink:social.info", 
                #                                              "calendar:social.info - ink:social.info")) %>% 
                #   mutate(term = c("ink:social.info", 
                #                   "bracelet:social.info", 
                #                   "calendar:social.info")),
                .id = "ref.type") %>% 
      mutate(term = fct_recode(factor(term), control = "(intercept)"),
             ref.pt = term == ref.type) %>% 
      list %>% 
      tibble(pt.est = .,
             num.col = n_distinct(.[[1]]$ref.type),
             joint.tests.res = list(joint.tests.res),
             num.obs = length(reg.res$fitted.values),
             num.clusters = length(unique(reg.res$cluster)),
             average.cluster.num.obs = mean(table(reg.res$cluster)),
             r.squared = r_squared(reg.res, adjusted = FALSE),
             adj.r.squared = r_squared(reg.res))
    
  }, .id = "spec") 

dist.sms.reg.table.data <- list("Monitored, SMS" = reg.output.sms.treat.dist,
                           "Endline, SMS" = reg.output.sms.treat.dist.covar) %>% 
  map_df(function(reg.res) {
    joint.tests.res <- list("Any Incentive Treatment" = c("ink", "calendar", "bracelet", 
                                                          "ink:far", "calendar:far", "bracelet:far",
                                                          "ink:social.info", "calendar:social.info", "bracelet:social.info",
                                                          "ink:social.info:far", "calendar:social.info:far", "bracelet:social.info:far"),
                            "Any SMS Treatment" = c("reminder.only", "social.info",
                                                    "reminder.only:far", "social.info:far",
                                                    "ink:social.info", "calendar:social.info", "bracelet:social.info",
                                                    "ink:social.info:far", "calendar:social.info:far", "bracelet:social.info:far"),
                            "Signaling Treatment" = c("ink", "bracelet", 
                                                      "ink:far", "bracelet:far", 
                                                      "ink:social.info", "bracelet:social.info",
                                                      "ink:social.info:far", "bracelet:social.info:far")) %>% 
      map_df(~ linear_tester(reg.res, .x, joint = TRUE), .id = "joint.test.type") %>% 
      select(-starts_with("linear.test")) %>% 
      mutate(joint.test.type = forcats::as_factor(joint.test.type))
    
    tidy(reg.res) %>% 
      filter(!str_detect(term, ":")) %>%
      bind_rows(linear_tester(reg.res, c("ink + ink:far", "calendar + calendar:far", "bracelet + bracelet:far")) %>% 
                  mutate(term = c("ink:far", "calendar:far", "bracelet:far"))) %>% 
      bind_rows(linear_tester(reg.res, c("ink", "calendar", "bracelet") %>% paste(., paste0(., ":social.info"), sep = " + ")) %>% 
                  mutate(term = paste0(c("ink", "calendar", "bracelet"), ":social.info"))) %>% 
      bind_rows(linear_tester(reg.res, c("ink", "calendar", "bracelet") %>% 
                                paste(., paste0(., ":social.info"), paste0(., ":far"), sep = " + ") %>% 
                                paste("social.info", sep = " + ") %>% 
                                paste("far", sep = " + ") %>% c("reminder.only:far + far", "social.info:far + far")) %>% 
                  mutate(term = c("ink", "calendar", "bracelet") %>% sprintf("%s:social.info:far", .) %>%  
                           c("reminder.only:far", "social.info:far"))) %>% 
      bind_rows(control = .,
                calendar = linear_tester(reg.res, c("(intercept) + calendar", 
                                                    "bracelet - calendar", 
                                                    "social.info + calendar:social.info")) %>% 
                  mutate(term = c("calendar", 
                                  "bracelet", 
                                  "calendar:social.info")),
                far = linear_tester(reg.res, c("(intercept) + far", 
                                               "reminder.only + reminder.only:far",
                                               "social.info + social.info:far",
                                               "ink + ink:far", "calendar + calendar:far", "bracelet + bracelet:far",
                                               "ink + ink:far + social.info + ink:social.info + ink:social.info:far", 
                                               "calendar + calendar:far + social.info + calendar:social.info + calendar:social.info:far",
                                               "bracelet + bracelet:far + social.info + bracelet:social.info + bracelet:social.info:far")) %>% 
                  mutate(term = c("far", "reminder.only:far", "social.info:far", 
                                  "ink:far", "calendar:far", "bracelet:far",
                                  "ink:social.info:far", "calendar:social.info:far", "bracelet:social.info:far")),
                "calendar:far" = linear_tester(reg.res, c("(intercept) + far + calendar + calendar:far", 
                                                          "bracelet + bracelet:far - calendar - calendar:far",
                                                          "social.info + calendar:social.info + calendar:social.info:far")) %>% 
                  mutate(term = c("calendar:far", 
                                  "bracelet:far",
                                  "calendar:social.info:far")),
                reminder.only = linear_tester(reg.res, c("(intercept) + reminder.only", 
                                                         "social.info - reminder.only")) %>% 
                  mutate(term = c("reminder.only", 
                                  "social.info")),
                "reminder.only:far" = linear_tester(reg.res, c("(intercept) + reminder.only + far + reminder.only:far", 
                                                               "social.info + social.info:far - reminder.only + reminder.only:far")) %>% 
                  mutate(term = c("reminder.only:far", "social.info:far")),
                ink = linear_tester(reg.res, c("(intercept) + ink", 
                                               "social.info + ink:social.info")) %>% 
                  mutate(term = c("ink", "ink:social.info")),
                bracelet = linear_tester(reg.res, c("(intercept) + bracelet", 
                                                    "social.info + bracelet:social.info")) %>% 
                  mutate(term = c("bracelet", "bracelet:social.info")),
                # social.info = linear_tester(reg.res, c("(intercept) + social.info", 
                #                                        "ink:social.info", "calendar:social.info", "bracelet:social.info")) %>% 
                #   mutate(term = c("social.info", "ink:social.info", "calendar:social.info", "bracelet:social.info")),
                
                # "calendar:social.info" = linear_tester(reg.res, c("(intercept) + calendar + social.info + calendar:social.info", 
                #                                                   "ink:social.info + ink - calendar:social.info + calendar",
                #                                                   "bracelet:social.info + bracelet - calendar:social.info + calendar")) %>% 
                #   mutate(term = c("calendar:social.info", "ink:social.info", "bracelet:social.info")),
                
                # "ink:social.info" = linear_tester(reg.res, c("(intercept) + ink + social.info + ink:social.info", 
                #                                               "bracelet:social.info + bracelet - ink:social.info + ink")) %>% 
                #   mutate(term = c("ink:social.info", "bracelet:social.info")),
                
                "ink:far" = linear_tester(reg.res, c("(intercept) + ink + far + ink:far", 
                                                     "social.info + ink:social.info + social.info:far + ink:social.info:far")) %>% 
                  mutate(term = c("ink:far", "ink:social.info:far")),
                
                "bracelet:far" = linear_tester(reg.res, c("(intercept) + bracelet + far + bracelet:far", 
                                                          "social.info + bracelet:social.info + social.info:far + bracelet:social.info:far")) %>% 
                  mutate(term = c("bracelet:far", "bracelet:social.info:far")),
                
                # "social.info:far" = linear_tester(reg.res, c("(intercept) + social.info + far + social.info:far", 
                #                                        "ink:social.info + ink:far + ink:social.info:far", 
                #                                        "calendar:social.info + calendar:far + calendar:social.info:far", 
                #                                        "bracelet:social.info + bracelet:far + bracelet:social.info:far")) %>% 
                #   mutate(term = c("social.info:far", "ink:social.info:far", "calendar:social.info:far", "bracelet:social.info:far")),
                
                # "calendar:social.info:far" = linear_tester(reg.res, 
                #                                            c("(intercept) + calendar + social.info + calendar:social.info + far + social.info:far + calendar:social.info:far", 
                #                                              "bracelet + bracelet:social.info + bracelet:social.info:far - calendar - calendar:social.info - calendar:social.info:far")) %>% 
                #   mutate(term = c("calendar:social.info:far", "bracelet:social.info:far")),
                # "ink:social.info:far" = linear_tester(reg.res, 
                #                                       c("(intercept) + ink + social.info + ink:social.info + far + social.info:far + ink:social.info:far", 
                #                                         "bracelet + bracelet:social.info + bracelet:social.info:far - ink - ink:social.info - ink:social.info:far")) %>% 
                  # mutate(term = c("ink:social.info:far", "bracelet:social.info:far")),
                .id = "ref.type") %>% 
      mutate(term = fct_recode(factor(term), control = "(intercept)"),
             ref.pt = term == ref.type) %>% 
      list %>% 
      tibble(pt.est = .,
             num.col = n_distinct(.[[1]]$ref.type),
             joint.tests.res = list(joint.tests.res),
             num.obs = length(reg.res$fitted.values),
             num.clusters = length(unique(reg.res$cluster)),
             average.cluster.num.obs = mean(table(reg.res$cluster)),
             r.squared = r_squared(reg.res, adjusted = FALSE),
             adj.r.squared = r_squared(reg.res))
    
  }, .id = "spec") 
```


We will report results for four specifications identifying:

1. The average treatment effects of incentives/signals on deworming take-up, excluding individuals assigned to any SMS treatment
2. The average treatment effects of incentives/signals and distance to treatment location on deworming take-up, excluding individuals assigned to any SMS treatment
3. The average treatment effects of incentives/signals and SMS treatment on deworming-takeup, excluding individuals who do not own a mobile phone.
4. The average treatment effects of incentives/signals, distance to treatment location and SMS treatment on deworming-takeup, excluding individuals who do not own a mobile phone.

For each specification we present a table with point estimates and their standard errors, $P$-values for tests of joint significance, other regression related information, as well as a plot showing take-up rates and 90\% confidence intervals for tests of significance against the reference treatment, for the regression controlling for covariates. The number of clusters included in each specification vary because we dropped outlier clusters.

The first results we look at are reported in Table \ref{tab:reg-basic} and Figure \ref{fig:reg-basic-covar-plot}. The impact of incentives/signals appears to be progressively stronger going from ink, calendars, to bracelets. Bracelets' impact is statistically significant compared to the control and calendar arms: bracelets increase the probability of take-up by 8 to 12 percentage points, with a baseline level of between 37 to 34 percent take-up. Evidence on the preference for calendars over bracelets and the statistical significance between the impact of calendar and bracelets, lead us to conclude that bracelets did not prove effective solely as a private incentive.

```{r reg-basic-table, results="asis", cache=FALSE, warning=FALSE}
print.reg.table(reg.table.data, caption = "Incentive/signal treatment effects, without SMS treatment.", label = "tab:reg-basic")
```

```{r reg-basic-covar-plot, fig.width=8, fig.cap="Plot of regression results comparing incentive/signal treatments."}
prep.sms.ctrl.plot.data(reg.output.sms.ctrl.covar) %>% 
  plot.sms.ctrl.takeup +
  labs(subtitle = "With control")
```

To investigate how the distance between targeted communities and the treatment location affects deworming take-up, we conduct our regression analysis interacting incentive/signal treatment with distance (categorized according to their randomly assigned distance of _close_ and _far_). Results are presented in Table \ref{tab:reg-dist} and Figure \ref{fig:dist-reg-covar-plot}. From columns 1 and 5, see that distance has strong negative effect on take-up, dropping between 17 to 20 percentage points in response to an approximate mean difference in distance of one kilometer (see Table \ref{tab:mean-assigned-dist}). We also not a big change in the impact of incentives/signals: their impact is strongly diminished for those close to the treatment location, and is no longer statistically significant compared to the control arm. The pattern of incentives/signals' impact, compared to the control arm, is similar across specification, although only the bracelets have a statistically significant impact, in _far_ communities: between 11 and 17 percentage points change, compared to the control arm, and between 9 and 12 percentage points change compared to the calendar arm. 


```{r reg-dist-table, results="asis", cache=FALSE, warning=FALSE}
print.reg.table(dist.reg.table.data, 
                caption = "Incentive/signal treatment effects, split by assigned distance to treatment location, without SMS treatment.",
                label = "tab:reg-dist")
```

```{r dist-reg-covar-plot, fig.width=8, fig.height=7, fig.cap="Plot of regression results comparing incentive/signal treatments with distance from treatment location interactions."}
prep.sms.ctrl.plot.data(reg.output.sms.ctrl.dist.covar, .interact.with = "far") %>% 
  mutate(grp = factor(grp, levels = c("ref.grp", "compare.grp"), labels = c("Close", "Far"))) %>% 
  plot.sms.ctrl.takeup(.facet.formula = grp ~ ref.treatment) +
  labs(subtitle = "With controls") 
```

In the last two specifications, we consider the impact of SMS reminders and informational messages, combined with incentive/signal treatment and distance to treatment location, on deworming take-up. Hence, we limit our analysis to the population of phone owners. As shown in Figure \ref{fig:general-desc-stats}, this encompasses between 2/3 to 3/4 of the population.

First, the impact of SMS treatment on deworming is estimated in Figure \ref{fig:sms-reg-covar-plot} and Tables \ref{tab:reg-sms} and \ref{tab:sms-interact}. There appears to be a big difference in the estimated take-up of deworming in the control arm when control for individual characteristics (refer to columns 1 and 9 in Table \ref{tab:reg-sms}). Including controls results in an increase in the impact of calendars and bracelets, as well as becoming statistically significant. Also, both impacts are very similar in magnitude (column 11). 

Considering the difference between a reminders only treatment (only tested in the incentives/signals control arm) and a social information treatment (tested in all arms), we see an almost six percentage point difference in take-up (columns 5 and 13), although only statistically significant when not controlling for covariates. This is also a surprising outcome, considering the the social information messages also functioned as reminders. 

Overall, social information treatment seems to have had a dramatic effect on deworming take-up, in particular when combined with incentives/signals. In columns 2-4 and 10-12, we observe an increase in the social information interaction effects, but only consistently statistically significant when comparing the bracelet and social information take-up with the ink and social information take-up (see Table \ref{tab:sms-interact}).

```{r reg-sms, results="asis", cache=FALSE, warning=FALSE}
print.reg.table(sms.reg.table.data, 
                font.size = "scriptsize",
                caption = "Incentive/signal treatment and SMS treatment effects.", label = "tab:reg-sms",
                estimate.buffer = TRUE, landscape = FALSE)
```

```{r sms-reg-covar-plot, fig.width=8, fig.height=6, fig.cap="Plot of regreession results comparing incentive/signal treatment with SMS treatment interactions."}
prep.sms.treat.plot.data(reg.output.sms.treat.covar) %>% 
  plot.sms.treat.takeup +
  labs(subtitle = "With Controls") 
```

```{r compare-sms-interact-reg}
sms.interact.diff.lh <- c(paste(c("ink:social.info",
                                  "calendar:social.info",
                                  "bracelet:social.info"), "= social.info"),
                          paste(c("calendar:social.info",
                                  "bracelet:social.info"), "= ink:social.info"),
                          "bracelet:social.info = calendar:social.info") %>% 
  c(str_replace_all(., "(\\S*social.info)", "\\1 + \\1:far"))

sms.interact.table.data <- list("Monitored, SMS" = reg.output.sms.treat,
                                "Endline, SMS" = reg.output.sms.treat.covar) %>% 
  map(linear_tester, sms.interact.diff.lh %>% magrittr::extract(!str_detect(., "far")))

sms.dist.interact.table.data <- list("Monitored, SMS" = reg.output.sms.treat.dist,
                                     "Endline, SMS" = reg.output.sms.treat.dist.covar) %>% 
  map(linear_tester, sms.interact.diff.lh)
```

```{r sms-interact-tab, results="asis", cache=FALSE, warning=FALSE}
print.sms.interact.table(sms.interact.table.data, 
                         caption = "Comparing the social information SMS treatment across incentive/signal treatment arms.",
                         label = "tab:sms-interact")
```

Finally, regression analysis results for the impact of incentive/signal treatment, SMS reminders and social information treatment, and assigned distance to treatment location, are presented in Figure \ref{fig:sms-dist-plot} and Tables \ref{tab:reg-sms-dist-monitored}, \ref{tab:reg-sms-dist-endline}, and \ref{tab:sms-dist-interact}. The impact of incentives/signals and SMS treatment is very similar to that discussed above. In particular, impact is strengthened when looking at the social information interactions with incentives/signals in _far_ communities; we see the highest impact on deworming where it almost triples comparing going from the pure control arm to the bracelets with social information treatment (based on the endline sample analysis). 

Evidence from this analysis does point to a multiplier effect of social information treatment when combined with the bracelet signal. As shown in Table \ref{tab:sms-dist-interact}, the difference between social information interaction is big in magnitude and statistically significant when comparing the bracelet interaction with the calendar and ink interactions. This multiplier effect, however, seems to disappear when considering _close_ communities, which points to another interesting pattern: there does appear to be a ceiling in proportion of deworming take-up across treatments and assigned distances. The take-up ceiling appears to be around 74 percent (absolute) take-up rate.

```{r reg-sms-dist, results="asis", cache=FALSE, warning=FALSE}
dist.sms.reg.table.data %>% 
  mutate(spec.simple = str_extract(spec, "[^,]+") %>% str_to_lower) %>% 
  a_ply(1, . %>% 
          print.reg.table(caption = "Incentive/signal treatment and SMS treatment effects, split by assigned distance to treatment location.",
                          label = paste0("tab:reg-sms-dist-", .$spec.simple), 
                          font.size = "scriptsize",
                          estimate.buffer = FALSE, landscape = FALSE))
```

```{r sms-dist-plot, fig.width=8, fig.height=8, fig.cap="Plot of regression results comparing incentive/signal treatment with SMS and distance from treatment location interactions."}
prep.sms.treat.dist.plot.data(reg.output.sms.treat.dist.covar) %>% 
  plot.sms.treat.takeup +
  facet_grid(dist ~ ., labeller = as_labeller(. %>% paste0("Distance: ", .))) +
  labs(subtitle = "Split by distance to treatment location, with controls")
```


```{r sms-dist-interact-tab, results="asis", cache=FALSE, warning=FALSE}
print.sms.interact.table(sms.dist.interact.table.data,
                         landscape = TRUE,
                         caption = "Comparing the social information SMS treatment across incentive/signal treatment arms, split by distance to treatment location.",
                         label = "tab:sms-dist-interact")
```

# Cost-effectiveness

We conducted a simplified analysis to assess which incentives/signals is the most cost-effective at increasing adult deworming treatment adoption. This analysis only assesses the incremental impact of ink, calendars, and bracelets, and does not look at the impact of SMS as an intervention. We estimated the baseline costs for implementing an adult community-based deworming program, first without any incentive/signal costs, based off of costs incurred during the study. We disaggregated costs that were directly related to the implementation of the deworming program, since many costs incurred during the study were related to research and design. Research-oriented costs, such as research enumerators and baseline survey costs, were excluded from the analysis. These implementation-related costs included 

1) Program management costs 
2) Drug and material transportation costs
3) Monitoring costs
4) Community sensitization costs
5) Training costs
6) Policy coordination costs
7) CHEW and CHV costs. 

The activities occurring during the weeks of deworming such as CHV/CHEW transport, airtime, supervision, and setup costs accounted for about 33% of implementation costs. Program management, messaging/sensitization activities, and CHV training made up 33%, 12%, and 6% of implementation costs, respectively. These cost proportions were estimated from budgeted amounts. We plan to do a more in-depth analysis of the implementation-related costs and the cost per person dewormed in the future.

We then calculated unit costs per person for each intervention, as well as unit drug costs. Although the drugs were donated and did not present a direct cost to the program, their imputed value is included as an important incremental cost to implementing the deworming program. The outcome measure used to evaluate 'effect' was the percentage increase in adoption of deworming treatment. Percent adoption was measured by the number of targeted community members who came to receive deworming treatment out of the total targeted population. The cost-effectiveness for each intervention was calculated in comparison to the control group (the cost and effect of delivering deworming treatment using no social incentive).

Arm         Unit Cost per Person (USD)   Take-up (%)   Cost Per % Increase in Take-up
--------   ---------------------------- ------------- --------------------------------
Ink            \$0.41                       35%             \$1,475
Calendar       \$0.33                       38%             \$341
Bracelet       \$0.35                       46%             \$141

Table: Cost-effectiveness analysis.

The cost-effectiveness analysis shows that using bracelets as an incentive/signal is the most cost-effective intervention in comparison to using calendars and ink when assessing the cost per percentage point increase in the take-up of deworming. Using bracelets as a social incentive/signal to increase treatment take-i[ by 1 percentage point for the community-based deworming program cost \$141. Using calendars and ink cost \$341 and \$1,475 per percentage increase in treatment take-up, respectively. The higher unit cost of providing ink as a social incentive (\$0.41) in comparison to the lower unit costs of calendars (\$0.33) and bracelets (\$0.35) can partially explain the low cost-effectiveness results of ink. Although calendars were the least expensive intervention on a per-unit basis, we observed the largest increase in adoption among the population who received bracelets, thus explaining its high cost-effectiveness. 

We do not expect these cost-effectiveness results to be linear in application (i.e. we expect that there is a ceiling effect in adoption since certain populations may be harder to reach as adoption continues to increase). Therefore, the cost-effectiveness results presented demonstrate the actual cost-effectiveness between the observed control and treatment populations, but cannot necessarily be generalized to the cost of increasing adoption by 1% point from a higher baseline adoption rate (e.g. increasing adoption from 70% to 71%).  

```{r abs-takeup-by-arm, eval=FALSE}
left_join(takeup.data %>% count(assigned.treatment) %>% rename(abs.takeup = n),
          census.data %>% count(assigned.treatment) %>% rename(census.total = n), "assigned.treatment") %>% 
  mutate(coef = if_else(assigned.treatment == "control", "", levels(assigned.treatment)[assigned.treatment]),
         basic.linear.test = paste("(intercept)", if_else(assigned.treatment == "control", "", sprintf("+ %s", coef))),
         sms.linear.test = paste("(intercept) + social.info", if_else(assigned.treatment == "control", "", sprintf("+ %s + %s:social.info", coef, coef)))) %>% 
  left_join(linear_tester(reg.output.sms.ctrl.covar, .$basic.linear.test), c("basic.linear.test" = "linear.test")) %>% 
  left_join(linear_tester(reg.output.sms.treat.covar, .$sms.linear.test), c("sms.linear.test" = "linear.test"), suffix = c(".non.sms", ".sms")) %>% 
  transmute(assigned.treatment = fct_relabel(assigned.treatment, str_to_title), 
            abs.takeup, census.total, estimate.non.sms, estimate.sms) %>% 
  kable(col.names = c("Arm", "Total Take-up", "Census Population", "Non-SMS-Treated Take-up", "SMS-Treated Take-up"), 
        format.args = list(big.mark = ","), )
```

# Conclusion

# References