---
title: |
    | The Role of Social Signaling in Community Deworming 
    | Evidence from a Field Experiment in Kenya^[This study was funded by the Children's Investment Fund Foundation and implemented by Evidence Action. We thank Guillaume Kroll, the study's project manager; Arthur Baker, our research assistant; Doris Njomo and Rosemary Musuva for their qualitative research input during the study's pilot; Carol Nekesa and her implementation and data collection team; Ned Augenblick, Edward Miguel and Stefano DellaVigna for their research advice; and Karen Levy and Grace Hollister for their advice and support. We received Internal Review Board clearance from the Kenya Medical Research Institute and the University of California Berkeley. The study pre-analysis plan was registered with the American Economic Association registry (<https://www.socialscienceregistry.org/trials/1643/history/17782>).]
subtitle: "Internal Working Paper -- Do Not Cite or Distribute"
date: "October 2017"
author:
- Anne Karing^[University of California Berkeley, `akaring@econ.berkeley.edu`.]
- Karim Naguib^[Evidence Action, `karim.naguib@evidenceaction.org`.]
output: 
  pdf_document:
    number_sections: yes
header-includes:
   - \usepackage{pxfonts}
   - \usepackage{bbm}
   - \usepackage{setspace}
   - \usepackage{booktabs}
   - \usepackage[table]{xcolor}
   - \usepackage{pdflscape}
   - \usepackage{threeparttable}
   - \usepackage{todonotes}
abstract: "This paper provides field-experimental evidence on the role of social signaling in community deworming. Working with the Kenyan Government, we implement a new community deworming program that offers free deworming treatment to 200,000 adults over a period of twelve days. The program explicitly emphasizes the public good aspect of deworming. We introduce two types of social signals in the form of colorful bracelets and ink applied to the thumb. The bracelets and ink make the decision to deworm or abstain from treatment observable and allow adults to signal to others that they contributed to protecting their community from worms. We further introduce a private incentive, in the form of a calendar, that is comparable in its consumption value to the bracelet. Deworming treatment points and their catchment communities are randomized into being eligible for the ink, bracelet or calendar incentive or a control group where no incentive is offered. The cluster randomization identifies the combined effect of social signaling, learning and reminders or salience effects. To separately identify the extent to which deworming decisions are driven by a desire to signal, we offer free text messages to a random subset of adults, reminding them of the availability of deworming treatment and providing information about deworming take-up in their community. To exogenously vary the information, we randomly assign communities to far or close walking distances to the treatment points, thus randomizing the average level of take-up in their community. We estimate a static and dynamic hierarchical Bayesian model to identify the average partial effect of social signaling on deworming take-up. Bracelets as \textit{signals} increased deworming take-up by 4 to 6 percentage points, an 11% to 20% increase compared to the control group. We find a close to zero average treatment effect for the ink incentive, with substantial heterogeneity in the impact across close (-3pp) and far communities (+2pp). The results suggest that mandatory signaling as in the case of inking people’s thumb, can dissuade marginal individuals if the perceived social desirability of being someone who deworms is negative. We find no evidence that visibility in actions, through ink or bracelets, affects take-up decisions through social learning or reminders. The text message treatment led to large increases (13-17pp) in deworming take-up across all groups, supporting existing evidence on the power of personal nudges."
bibliography: ~/Documents/library.bib
---

\doublespacing
\newtheorem{assumption}{Assumption}

```{r workingpaper-setup, include=FALSE}
library(plyr)
library(magrittr)
library(lubridate)
library(forcats)
library(broom)
library(ggrepel)
library(ggmap)
library(gridExtra)
library(rgeos)
library(sp)
library(knitr)
library(modelr)
library(car)
library(rstan)
library(tidyverse)

library(econometr)

source("takeup_rct_assign_clusters.R")
source("analysis_util.R")

knitr::read_chunk("analysis_util.R", labels = "analysis-util")

read_chunk(purl("takeup_analysis2.Rmd")) 
read_chunk(purl("takeup_bayesian_analysis.Rmd")) 

options(dplyr.show_progress = FALSE, digits = 4)

opts_chunk$set(echo = FALSE, warning = FALSE, 
               cache = TRUE, cache.path = "takeup_workingpaper-cache/", 
               fig.path = "takeup_workingpaper-fig/", fig.align = "center")
```

```{r proj4}
wgs.84 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
kenya.proj4 <- "+proj=utm +zone=36 +south +ellps=clrk80 +units=m +no_defs"
```

```{r wp-parallel-setup, ref.label="parallel-setup", eval=FALSE}
```

```{r ggplot-theme, cache=FALSE}
theme_set(theme_minimal() +
            theme(legend.position = "bottom"))
```

```{r load-experiment-design-data}
rct.schools.data <- read_rds(file.path("data", "takeup_rct_schools.rds"))
rct.cluster.selection <- read_rds(file.path("data", "rct_cluster_selection_2.0.rds"))
cluster.strat.data <- read_rds(file.path("data", "takeup_processed_cluster_strat.rds"))

load(file.path("data", "takeup_village_pot_dist.RData"))
```

```{r load-analysis-data}
load(file.path("data", "analysis.RData"))
```

# Introduction

How do social signals affect adults’ willingness to contribute to public goods? The role of social signaling and image concerns has been widely studied in the theoretical literature in economics, including motives for pro-social behavior [@Benabou2006; -@Benabou2012a] and norms [@Bernheim1994; Benabou2012]. Recent field experiments have found that social image concerns affect important behaviors, such as  consumption, the decision to vote, and student effort [@Dellavigna2017; @Bursztyn2017a; @Bursztyn2015]. However, there is a lack of empirical evidence on social signaling in individuals’ decisions to contribute to public goods and whether social image concerns can be influenced in empirically relevant settings [@Bursztyn2017]. We choose an important empirical application, community deworming, to manipulate social signaling concerns and test their relevance to individuals' decisions to take-up deworming treatment. 

Intestinal worms are a development burden to children and adults in many developing countries. According to the World Health Organization approximately 1.5 billion people are infected with soil-transmitted helminths (STH) worldwide.^[World Health Organization, Fact Sheet Soil-transmitted helminth infections, September 2017
http://www.who.int/mediacentre/factsheets/fs366/en/]. While mild infections are asymptomatic, more severe infections lead to abdominal pain, iron-deficiency, anemia, malnutrition, and stunting. 

There is a strong case to be made for community mass deworming as strategy to reduce the disease burden: deworming drugs are safe, have no side effects for uninfected individuals and cost a small fraction of what screening for worm infections costs (4 to 10 times less). Further, deworming treatment leads to health improvements in the short term and productivity increases in the long term. @Kremer2011a showed that deworming is one of the most cost-effective ways to increase school attendance and has positive externalities on the untreated. Since most of deworming benefits come through reduced disease transmission, deworming is a public good. Epidemiologists postulate that it might be feasible to eliminate worms using mass drug administration covering the entire population, including children and adults. While significant progress has been made in deworming children through school-based deworming programs, the remaining infectious reservoir among adult populations fosters reinfection. An important empirical questions is therefore, whether high take-up of deworming treatment among adults can be achieved cost effectively and within a short time. Social incentives, whose main attribute is to make actions observable, may be less expensive than material incentives and through their visibility can influence social image concerns. 

In this paper, we (i) provide experimental evidence on the effects of making actions observable through social incentives, (ii) identify the average partial effect of social signaling on individuals' probability of getting dewormed and (iii) quantify the utility from social signaling. Working with the Kenyan Government, we implement a large-scale randomized control trial in Western Kenya, stratified over three counties. We introduce a new community deworming program, where community health volunteers offer free worming treatment to adults at central locations (instead of through door-to-door treatment). Adults are informed about the private and community-wide health benefits of deworming prior to the start of the program. Our main experimental manipulation is to alter the observability of deworming treatment take-up. We introduce two social incentives in the form of colorful bracelets and ink applied to people’s thumb. To control for the consumption value of bracelets, we introduce a private incentive in the form of a one-page calendar. In a separate willingness to pay experiment we show that adults who had no prior exposure to either incentive, strictly prefer the calendar over the bracelets. 150 treatment locations and their catchment communities are randomized into the ink, bracelet or calendar incentive or a control group where no incentive is offered. The cluster randomization identifies the combined effect of social signaling, learning and reminders. To separately identify the extent to which deworming decisions are driven by a desire to signal, we offer free text messages to a random subset of 25 adults in each of the study communities. The text messages remind individuals of the availability of deworming (starting the day before the deworming program starts) and provide information about the share of people that have come for deworming treatment in their community (provided on day 2, 4, 6, 8 and 10 of the 12 days where treatment is available). To exogenously vary the information, we randomly assign communities to close (less than 1.25 kilometer) or far (between 1.25-2.5 kilometers) walking distances to the treatment points, thus randomizing the average level of take-up in their community.

We estimate a static and dynamic hierarchical Bayesian model to create the necessary counterfactuals to identify the partial effect of social signaling on deworming take-up. In the static model, we show that bracelets as signals meaningfully increased individuals' probability to deworm, and that these effects persist when also providing SMS reminders and information about others' take-up decision. The text message treatment led to large increases (13-17pp) in deworming take-up across all groups, supporting existing evidence on the power of personal nudges. The dynamic model allows us to go one step further and explicitly model potential learning, reminder or salience effects that were introduced as individuals could observe other people's deworming decision. Controling for these effects, we find bracelets (after controling for any potential consumption value) increased deworming take-up by 4 percentage points, an 11% increase compared to the control group. We find a zero average treatment effect for the ink incentive, with substantial heterogeneity in the impact across close (-3pp) and far communities (+2pp). The results suggest that “forced” signaling as in the case of inking people’s thumb, can dissuade marginal individuals if the perceived social desirability of being someone who deworms is negative. Same as in the static model with the SMS treatment, we find no evidence that visibility in actions, through ink or bracelets, affects take-up decision’s through social learning or reminders. 

Our work contributes to the literature of social signaling and social image concerns in three ways. First, we provide direct evidence of the effectiveness of making actions observable through a low-cost signal. Recent empirical studies have highlighted the negative effects of visibility like in the case of conspicuous consumption or student efforts. This study shows how social welfare can be improved through social signaling. Second, we show that the type of signal offered can drastically influence its effectiveness. A “looser” signal that does not force individuals to signal can be more effective in increasing take-up despite weakening the type inference. Third, we are overcoming the identification challenge of social signaling in the presence of dynamics where individuals cannot only signal but also observe other individuals’ take-up decisions and might hence be nudged or reminded of deworming, or update their beliefs about the benefits of deworming. We do so in two ways: first, we introduce an SMS treatment that reminds individuals of the availability of deworming and provides information about take-up levels; second, we build a dynamic (hierarchical Bayesian) model to exploit the full information about changes in take-up levels across the 12 days of treatment. Lastly, our work contributes to the literature on incentives and comparisons of material versus non-financial incentives. There is limited field-experimental evidence on non-financial incentives and the mechanisms through with they affect behavior. 

The remainder of this paper is organized as follows. In Section \ref{the-intervention}, we describe the setting of the intervention. In Section \ref{experiment-design}, we describe the experimental design to identify social signaling concerns. Section \ref{descriptive-statistics}, provides descriptive statistics from the experiment. In Section \ref{structural-model}, we present the structural model to describe individual decision-making in the presence of observability of actions.  In Section \ref{empirical-models}, we present the empirical Bayesian model, which is based of the structural model outlined in \ref{structural-model} and the experimental variations described in \ref{experiment-design}. In Section \ref{results} we show the results. Section \ref{conclusion} concludes.

# The Intervention

Working with the Government of Kenya we offered free deworming treatment to adults at central locations in 3 counties in Western Kenya: Busia, Kakamega and Siaya County. Central locations were selected to be easily locatable by targeted community members by being in close proximity of a primary school and either located in their own villages or in neighboring villages.^[We initially selected treatment locations to be adjacent to primary schools because of their prominence and ubiquity. However, the Ministry of Education did not permit us to operate in such close proximity to schools to prevent cheating in exams. We therefore used alternative locations (such as churches) that were not too far from the originally selected schools.] Community Health Volunteers (CHVs) led the implementation of the community deworming program and provided the treatment at central locations and informed households about the upcoming deworming treatment.^[CHVs were trained in drug administration by their supervising Community Health Extension Workers (CHEWs), who also handled the distribution and recovery of deworming drugs. The research team worked closely with national and local health officials but was not involved in the medical aspects of deworming.] One week prior to the start of the deworming treatment CHVs conducted a door-to-door sensitization, informing households about the community-wide benefits of deworming and risk of infection through others, when and where free treatment will be available and if applicable what type of incentive will be given to adults coming for treatment. CHVs further worked with community stakeholders to spread the information through established channels (e.g. community meetings/barazas) and placed posters in prominent locations. 

<!-- TODO Add CHV script in Appendix -->
<!-- TODO Add Poster Example in Appendix -->

Deworming treatment was subsequently offered at central locations, from 8am to 5pm, for a period of 12 days. For logistical reasons, we split the intervention into two waves: from October 3 to 14 we offered deworming treatment to communities in Busia and Siaya County, and from October 24 to November 4 we offered treatment in Kakamega County. Depending on the treatment location a community was assigned to, adults who came for deworming were dewormed or were dewormed and also the first deworming wave was from October 3 to 14 in Busia and Siaya County, and the second wave was from October 24 to November 4 in Kakamega County. Depending on the a cluster's assigned treatment, individuals who came for deworming were either only dewormed or were dewormed and either 

(i) received a mark on their thumb using indelible ink as is normally done during voting, 
(ii) given a simple one page wall calendar, with a design unrelated to deworming, as a gift, or
(iii) given a silicon green bracelet as a gift.

All adults who came to a given treatment location were provided with deworming treatment (and if applicable were given an incentive) irrespective of where they lived.^[We did not provide treatment only to adults that came from communities that were targeted by the informational campaign or require individuals to receive treatment in their home cluster.] After treatment, individuals were asked to provide their name, gender, age and community location.^[This data is commonly collected during health campaigns for administrative purposes. For the purpose of this evaluation, recording deworming treatment take-up directly at the point of treatment instead of relying on self-reported measures greatly helped us improve the accuracy of our data.]   

Prior to the start of deworming treatment, we also recruited a random sample of individuals to receive informational text messages about the community deworming program (see the [Experiment Design](#experiment-design) section). The text messages reminded adults of the availability of deworming treatment and their treatment location, and provided information about deworming treatment take-up in their communities. Messages were sent the day before the deworming program started and after that every other day (on the second, fourth, sixth, eight and tenth deworming day). 


# Experiment Design

We randomly selected 158 clusters in the three study counties, of which 144 were used in the study.^[We only intended to use 150 clusters, and only included eight extra clusters as fallback clusters. For various practical reasons, implementation was only possible in 144 clusters.] We relied on the high geographic density of primary schools in the study counties to select both treatment locations and targeted communities.^[Geographic coordinates for primary schools were retrieved from the Kenya Open Data Portal (<http://www.opendata.go.ke/>).] Each cluster is defined as a treatment location and targeted community pair. We used the location of primary schools as proxies to (i) identify acceptable locations to set up our treatment locations and (ii) to find villages to target with our informational campaign and data collection.

To select our clusters from the pool of a total of 1,451 primary schools in our study area, we used an acceptance-rejection method whereby we randomly picked schools, checked their acceptability based on their overlap with already selected clusters, and if accepted added them to our selected sample. This process was repeated until we had selected the requisite number of clusters. If no acceptable schools remained before completion, the whole process was restarted. Each cluster, centered on its treatment location, had a 2.5 kilometer radius _catchment circle_ and 3-4 kilometer radius _buffer circle_. A cluster was considered acceptable if its _buffer circle_ did not leave any of the already selected clusters' non-overlapping _catchment circles_ smaller than an a pre-specified size.

<!-- TODO ^[Buffer sizes were randomly assigned -  EXPLAIN MORE?]  -->
<!-- TODO ^[EXPLAIN OR DELETE: with about one primary school nonoverlapped. ALSO ADD pre-specified size = X] -->

```{r all-clusters-map, message=FALSE, fig.width=6, fig.height=6, fig.cap="Map of Initial Cluster Selection. Black crosses (+) indicate the selected treatment locations, while the grey regions indicate the nonoverlapped catchment circles from which we selected village(s) to target."}
ggplot.clusters(rct.cluster.selection, include.cluster.ids = FALSE, source = "stamen", maptype = "toner") 
```

After all clusters were selected, we randomly assigned^[Randomization was stratified within counties to increase statistical power.] each cluster to be either a "close" or "far" cluster: whether its targeted community would be less or more than 1.25 kilometers away from the treatment location, respectively. We then selected for each cluster, from its non-overlapping _catchment circle_ and according to its assigned distance treatment, a primary school as an anchor for us to locate its targeted community.^[For further details on the cluster selection algorithm refer to the study's pre-analysis plan [@Karing2016].] Figure \ref{fig:dist-to-pot} shows the distribution of targeted communities' distances (in meters) to their own treatment locations and to the closest other treatment locations.

<!-- TODO I struggle to interpret: first graph shows almost zero overlap, second graph shows that for 25% of communities closest other treatment loc was 2.5km or less away. DELETED 2nd graph (for now). -->
<!-- TODO Add further detail about what learn from graph e.g. (?) cluster selection algorithm was successful in that for almost all clusters own treatment location was closer than closest other treatment location -->

```{r dist-to-pot, echo=FALSE, fig.width=6, fig.height=3, fig.cap="Distance to Treatment Locations"}
verify.vill.pot.dist %>% 
  select(dist.to.own.pot, closest.other) %>% 
  gather(dist.type, dist) %>% {
  ggplot(.) +
    geom_histogram(aes(dist, fill = dist.type), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = alpha("black", 0.5), position = "dodge") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 5)) +
    scale_fill_discrete("Distance", labels = c("To Closest Other Treatment Location", "To Assigned Treatment Location")) 
}
```

```{r dist-to-other-pot, fig.width=6, fig.height=2, fig.cap="Distance to Closest Other Point-of-Treatment", eval=FALSE}
verify.vill.pot.dist %>% { 
  ggplot(.) +
    geom_histogram(aes(closest.other), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = "black") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 2)) 
} 
```

```{r marginal-dist-to-other-pot, fig.height=2.5, fig.width=6, fig.cap="Marginal Distance to Closest Other Treatment Location. Dashed vertical lines indicate the 10th, 25th, 50th, 75th, and 90th percentiles of the distribution.", eval=FALSE}
verify.vill.pot.dist %>% 
  mutate(marginal.dist = closest.other - dist.to.own.pot,
         dist.to.own.pot.cat = cut(dist.to.own.pot, 
                                   breaks = c(0,  2500/2, 10000),
                                   labels = c("Close", "Far"))) %>% {
                                     ggplot(.) +
                        geom_histogram(aes(marginal.dist), alpha = 0.5, color = alpha("black", 0.5), binwidth = 500, boundary = 0, position = "dodge") +
                        scale_y_continuous("Number of Clusters", breaks = seq(0, 50, 2)) +
                        scale_x_continuous("", breaks = seq(-1000, 10000, 1000)) +
                        geom_vline(xintercept = quantile(.$marginal.dist, probs = c(0.1, 0.25, .5, 0.75, 0.9)), linetype = "dashed", alpha = 0.5)
                                   }
```

Clusters were then randomly assigned, stratified over counties and distance treatment, to the different incentive treatments: 

(i) Control: no incentive
(ii) Indelible ink: a public signal of treatment
(iii) Calendar: a private low-value gift 
(iv) Bracelet: a low-value gift and public signal of treatment 

To finalize the cluster selection process, we surveyed the treatment location and target community anchor schools. For the treatment locations we confirmed that treatment would be feasible there and identified alternative treatment locations, close to the selected schools, as potential backups. For the anchor schools, we identified all the communities near them and randomly selected one community to target.^[In some cases because the initial village was too small, we added a second village] We then conducted a census of all adults (18 years or older of age) residing in the selected communities: surveyors visited each household, captured their geographic coordinates, and collected basic information of each household member that would allow us to follow-up with individuals if they were sampled in later stages and to stratify over relevant characteristics (e.g., phone ownership).

Using the census lists we randomly sampled individuals to be surveyed at base- and/or endline and to be part of the text messaging intervention. The sampling of individuals who did not receive any text messages was stratified over phone ownership. For all sampled individuals, we monitored the decision to take-up deworming treatment and obtained their consent to having observed their take-up status and using their data.^[Except for individuals who were surveyed at baseline, the majority were not informed about their participation in the study and therefore needed to be re-consented.] 

<!-- TODO Strange bit since we state above that all individuals who came for treatment, were asked about their name, age, gender and community. So saying "All individuals who were in these samples were collectively put the _monitored_ group. At the treatment location, individuals who were treated were asked some quick identifying questions (name, age, etc.), and if they were found to match someone in the _monitored_ group we made a record of their treatment." does not quite make sense and makes it sound like as if we did not monitor other people's treatment status which we did though.-->

<!-- TODO Add experiment design and survey timeline diagram -->

### Baseline survey {-}

<!-- TODO should later replace intended number of people surveyed with actual avrg. number of adults surveyed-->

Before implementing the information campaign, we aimed to conduct baseline surveys with 15 individuals from unique households in each cluster.^[The actual number of individuals that were located varied for all the samples.] 
<!-- TODO ADD WHY WE DID THIS?-->
The baseline survey included questions on:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of.
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others.
c) Beliefs about one's own and others' deworming decisions in response to an MDA, and how that decision is affected by others' choices.
d) Beliefs about one's own and others' reputation if infected and treated.
e) Past experience with deworming treatment.

### Text message intervention {-}

We aimed to recruit 30 individuals per cluster in the control arm and 25 individuals per cluster in the treated arms to receive informational text messages. In the control arm, we divided the sample into two groups of 15: one group that received reminder messages only,^[The reminder messages stated "Free deworming now at [Central Location]."] and a second group that received reminders and social information about other individuals' deworming take-up.^[Peer take-up was described both as "few", "almost half", "almost everyone", etc. of your village came, and as a "$n$ in 10" proportion.] In the incentive arms, all individuals received the reminder and the social information.

The text message treatment sample was drawn from the population of phone owners, from which we also drew a comparison "control" sample, that did not receive any text messages. 

### Endline survey {-}

After deworming treatment was completed, we aimed to conduct endline surveys with the 25 individuals per cluster, who were selected from the following groups:

* From the sample of those not receiving text messages:
    - 15 individuals per cluster in the control arm
    - 20 individuals per cluster in the treated arms
* From the sample of those receiving reminder messages only:
    - 5 individuals per cluster 
* From the sample of those receiving reminder and social information messages:
    - 5 individuals per cluster 
   
Since the majority of endline survey respondents were not part of the baseline survey, some questions overlapped between the two questionnaires. The endline survey included questions on:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of.
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others.
c) Knowledge of the MDA intervention: location, start date, and duration of treatment; where respondent got dewormed; how did respondent learn about the MDA; and if they were contacted by a CHV or received text messages.
d) Questions testing knowledge of others' deworming choices: 
    i. Respondents were incentivized to estimate how many of their community members got dewormed.
    ii. Respondents were explicitly asked about their relationship with and their knowledge of deworming status of ten other individuals or pairs of individuals in their community.^[We randomly asked respondents about individuals or pairs of individuals, with the objective to reduce potential aversion to disclosing negative information about peers.]
    
<!-- TODO Note according to IRB WTP was part of endline survey, just a different survey part. I think we should treat it that way. -->

As part of the endline survey, we implemented a discrete choice experiment to elicit individuals' private valuation for the calendar and bracelet incentives. We conducted a willingness-to-pay survey with a sample of subjects in the control arm who were neither part of the endline survey nor were they part of the text messaging treatment. We randomly selected 24 control communities and sampled 25 individuals from each. Respondents were given the choice to receive either the calendar or the bracelet for free, revealing their preferred choice. We then offered a random cash amount for respondents to switch to the incentive that they had not chosen, which allows us to estimate the utility difference in monetary terms. 

# Descriptive Statistics 

In this section we will present descriptive statistics pertinent to implementation of the community deworming program and its outcomes. 

### Study sample {-}
Table \ref{tab:cluster-stats} shows the total number of clusters by treatment arm and county as well as the number of adults that were surveyed during the census. Across 144 cluster, we surveyed 39,301 individuals who formed the sampling frame for different surveys and text messaging intervention. 
<!-- useless sentence and should definitely move table to appendix later. useful only if we describe different sample, where this is super sample and then there is monitored, monitored consent and endline sample -->

```{r cluster-stats}
cluster.stats <- census.data %>%
  filter(!is.na(cluster.id)) %>%
  left_join(select(cluster.strat.data, cluster.id, dist.pot.group), "cluster.id") %>% 
  arrange(county) 

calc.cluster.stats <- . %>% 
  count(county, assigned.treatment) %>% 
  ungroup %>% 
  spread(assigned.treatment, n) %>% { 
    total <- select(., -county) %>% mutate_all(as.integer) %>% rowSums 
    mutate(., all = total) 
  }

clusters.stats <- cluster.stats %>% 
  distinct(cluster.id, .keep_all = TRUE) %>% 
  calc.cluster.stats %>%
  set_names(str_to_title(names(.))) 

individ.stats <- cluster.stats %>% 
  calc.cluster.stats %>% 
  set_names(str_to_title(names(.))) 
```

\begin{table}
\centering
\caption{Number of clusters and individuals in targeted communities, by county and treatment arm.}\label{tab:cluster-stats}
\begin{tabular}{l*{10}{c}}
\toprule
       & \multicolumn{5}{c}{Clusters} & \multicolumn{5}{c}{Individuals} \\ \\
County & Control & Ink & Calendar & Bracelet & All & Control & Ink & Calendar & Bracelet & All \\
\cmidrule(r){2-6} \cmidrule(r){7-11}

```{r cluster-stats-tab, results="asis"}
clusters.stats %>%
  left_join(individ.stats, "County", suffix = c(".clusters", ".individuals")) %>% 
  plyr::a_ply(1, function(row) sprintf("%s %s \\\\\n", 
                                 row$County,
                                 paste(sprintf(" & %s", prettyNum(as.integer(row[, -1]), big.mark = ",")), collapse = "")) %>% 
          cat)
  
```
\bottomrule
\end{tabular}
\end{table}

Figure \ref{fig:general-desc-stats} shows socio-economic characteristics of individuals in the census, base- and endline survey. The mean age is 35 and 40 years respectively. Over half of respondents have not completed primary education and a large share (80$\%$) live in houses with floors made of earth. Both is indicative of low-income status, yet 65$\%$ to 80$\%$ of respondents report to have a mobile phone across the different surveys. 

```{r general-desc-stats, fig.width=8, fig.height=6, warning=FALSE, fig.cap="Study population summary statistics"}
gen.stats.plot <- tribble(~ col.name,       ~ label,
        "gender",         "Gender",
        "ethnicity2",      "Ethnicity",
        "school",         "Schooling",
        "floor",          "Home floor construction",
        "have_phone",     "Own mobile phone?") %>%
  multi.know.bel.cat.plot(.census.data = census.data %>% mutate(gender = factor(gender, levels = 1:2, labels = c("Male", "Female"))),
                          preprocess.fun = . %>% mutate(response = fct_relevel(response, rev(levels(baseline.data$school)))),
                          na.rm = TRUE)

age.density.plot <- list(Census = mutate(census.data, age = age.census), 
                         Baseline = baseline.data, 
                         Endline = endline.data) %>% 
  map_df(~ select(., age), .id = "survey.type") %>% 
  mutate(survey.type = factor(survey.type, levels = c("Census", "Baseline", "Endline"))) %>% 
  ggplot(aes(survey.type, age, color = survey.type)) +
  geom_boxplot() +
  coord_flip() +
  scale_y_continuous("Age Box Plot", breaks = seq(15, 100, 5)) +
  labs(x = "") +
  theme(legend.position = "none")

grid.arrange(gen.stats.plot, age.density.plot, layout_matrix = as.matrix(c(1, 1, 1, 1, 2)))
```

<!--Gender decomposition -->

### Knowledge, beliefs and perceptions of deworming {-}

Figure \ref{fig:know-believe-categorical-responses} presents individuals' responses to base- and endline questions about worms and deworming treatment. The majority of respondents knew about deworming treatment (78$\%$). However, less than one third of adults had knowledge of the negative externalities of worm infection. Comparing reported knowledge and beliefs of baseline and endline surveyed individuals, the most significant change is in people's understanding of who is at risk of worm infections. More people are reporting after the intervention the belief that everyone is at risk of worm infection. 
<!-- TOOK OUT since people are both less likely to answer yes and no to this question, as if they were less open to answering the question after deworming took place "Surprisingly, there seems to be a decrease in the understanding that individuals can infection one another. -->

```{r know-believe-categorical-responses, warning=FALSE, fig.width=8, fig.height=10, fig.cap="Knowledge and beliefs baseline and endline survey responses."}
tribble(~ col.name,      ~ label,
        "who_worms",     "Who is at risk of worms?",
        "effect_worms",  "What are the effects of worms?",
        "spread_worms",  "Can an infected person spread worms to other?",
        "how_spread",    "How are worms spread?",
        "stop_worms",    "How to stop worms?",
        "when_treat",    "When should people get dewormed?",
        "worms_affect",  "If infected, can you affect others' health?",
        "neighbours_worms_affect", "Can neighbors or relatives worm infection affect your health?") %>% 
  multi.know.bel.cat.plot() +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

Since our study's main research questions focus on social influence in deworming decisions, we tried to elicit individuals' perceptions and beliefs of others' deworming choices. Figure \ref{fig:response-other-deworm} shows individuals reporting that their own deworming decisions would not be influenced by others' decisions, as well as having a strong _intention_ to getting dewormed.

```{r response-other-deworm, warning=FALSE, fig.width=8, fig.height=2.5, fig.cap="Reported response to others' deworming choices."}
tribble(~ col.name,      ~ label,
        "few_deworm",     "Deworm if less than half of others deworm?",
        "many_deworm",    "Deworm if more than half of others deworm?",
        "more_less",      "Would you be more likely to deworm if few/many others get dewormed?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

In addition, as shown in Figure \ref{fig:baseline-deworming-beliefs}, people predicted similar deworming among peers. As we will see below, most people overestimated their own and others' deworming take-up. Finally, when individuals were asked about how others would respond to the use of indelible ink as a signal of deworming treatment, they predicted a positive effect, contrary to what we actually observed.

```{r survey-of-10-beliefs, ref.label="survey-of-10-beliefs", warning=FALSE}
```

```{r survey-of-10-beliefs-boxplot, ref.label="survey-of-10-beliefs-boxplot", warning=FALSE}
```

```{r baseline-deworming-beliefs, warning=FALSE, fig.width=8, fig.height=5, fig.cap="Baseline beliefs/predictions about others' deworming choices."}
other.predict.deworm.plot <- tribble(~ col.name,              ~ label,
                                     "dworm_proportion",      "How many people will come to get dewormed?",
                                     "ink_more_less",         "Will the ink signal increase/decrease deworming take-up?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL,
                          preprocess.fun = . %>% 
                            mutate(response = fct_relevel(response,
                                                          "Few", "Nearly Half", "Half", "More Than Half", "Many", "All", "Less", "Same", "More", "Prefer Not Say", "Don't Know"))) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  labs(title = "Peer deworming predictions")

survey.takeup.beliefs.10.boxplot <- survey.takeup.beliefs.10.boxplot + theme(legend.position = "none")
survey.takeup.beliefs.10 <- survey.takeup.beliefs.10 + theme(legend.position = "right")

grid.arrange(other.predict.deworm.plot, survey.takeup.beliefs.10, survey.takeup.beliefs.10.boxplot, 
             layout_matrix = rbind(c(1, 1, 1, 1), c(2, 2, 3, 3)))

```

To measure existing social norms surrounding deworming, we elicited individuals' attitudes towards deworming and other well-known behaviors such as wearing nice clothes to church, using latrines, and immunizing children. We presented individuals with different scenarios and asked whether these would inspire praise or stigma.

We also inquired about respondents' social perception/judgement of some of others' behaviors (some more observable than others). We wanted to compare attitudes towards deworming and other behaviors such as wearing nice clothes to church, using latrines, and immunizing children. Individuals were presented with difference scenarios and were asked whether they would inspire praise or stigma. Figure \ref{fig:praise-stigma-plot} shows that deworming is considered to be as highly praiseworthy as the use of latrines and immunization of children, and more praiseworthy than wearing nice clothes to church. In terms of stigma, failing to get dewormed is reported to be slightly less stigmatized than open defecation and not immunizing ones children, but is more negatively viewed than not wearing nice clothes to church.


```{r praise-stigma, ref.label="praise-stigma"}
```

```{r praise-stigma-plot, fig.width=8, fig.height=3, fig.cap="Reported social perception of some observable activities."}
plot(praise.stigma.plot) 
```

```{r mda-dates-dist, ref.label="mda-dates-dist"}
```

### Prior experience with deworming {-}

Figure \ref{fig:dewormed-history} presents individuals' reported experience with deworming, prior to the intervention. The majority of respondents said that children in their families had been previously dewormed, and the most common location for treatment for family members had been during the annual school-based deworming program. We also see that almost two third of adults had been previously dewormed. However, more than half of those reporting prior treatment, were treated over two years ago. Furthermore, most adults reported getting dewormed at a hospital/clinic or to have purchased medication.

```{r dewormed-history, fig.width=8, fig.height=9, fig.cap="Deworming history."}
ever.dewormed.plot <- baseline.data %>% 
  select(treated, family_treated) %>% 
  gather(key = who.treated) %>% 
  mutate(who.treated = if_else(who.treated == "treated", "Self", "Family")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>%
  ungroup %>%
  mutate(value = fct_recode(factor(value), "Don't Know" = "DK") %>% 
             fct_relabel(str_to_title) %>% 
             fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Ever been dewormed before?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

who.was.dewormed.plot <- baseline.data %>% 
  select(family_treated, who_treated) %>% 
  filter(family_treated == "yes") %>% 
  mutate(who_treated = fct_relabel(factor(who_treated), str_to_title)) %>% 
  ggplot(aes(who_treated)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "Who in family got dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

when.dewormed.plot <- baseline.data %>% 
  transmute(treated, 
            treated_when = fct_relabel(factor(treated_when), str_to_title)) %>% 
  filter(treated == "yes") %>%
  ggplot(aes(treated_when)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "When did you last get dewormed?", x = "", y = "Proportion")

where.treated.plot <- baseline.data %>% 
  select(treated, family_treated, treated_where, where_family_treated) %>% 
  gather(key = who.treated, value = value, -c(treated, family_treated)) %>% 
  mutate(who.treated = if_else(who.treated == "treated_where", "Self", "Family")) %>% 
  filter((who.treated == "Self" & treated == "yes") | (who.treated == "Family" & family_treated == "yes")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>% 
  ungroup %>% 
  mutate(value = fct_recode(value, "Don't Know" = "DK") %>% 
           fct_relabel(str_to_title) %>% 
           fct_relabel(function(.label) str_replace_all(.label, "Mda", "MDA")) %>% 
           fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Where did you last get dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

grid.arrange(ever.dewormed.plot, who.was.dewormed.plot, when.dewormed.plot, where.treated.plot, 
             layout_matrix = as.matrix(c(1, 1, 2, 3, 3, 4, 4)))
```

### Information campaign and knowledge about the community deworming program {-}

To verify that individuals were informed about the new community deworming program we asked endline survey respondents questions to test their knowledge, presented in Figure \ref{fig:know-about-mda}. Responses indicate a good knowledge of the program and its start and end dates. The majority reported learning about the deworming program from CHVs, and few said they were informed by other social contacts such as barazas, churches, family and friends. Posters did not appear to be very successful. Overall, the community deworming program's informational campaign, led by CHVs, was successful at reaching most community members.

```{r know-about-mda, warning=FALSE, fig.width=8, fig.height=6.5, fig.cap="Knowledge of RCT intervention."}
know.mda.cat.plot <- tribble(~ col.name,      ~ label,
        "know_deworm",    "Know about community-based MDA?",
        "treat_begin",    "Know when MDA starts?",
        "treat_end",      "Know when MDA ends?",
        "days_available", "Know length of MDA?",
        "find_out",       "From whom or how did you learn about the MDA?",
        "chv_visit",      "Did a CHV visit you to tell you about MDA?") %>% 
  multi.know.bel.cat.plot(.baseline.data = NULL, .census.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 

mda.dates.dist.plot <- mda.dates.dist.plot + theme(legend.position = "right")

grid.arrange(know.mda.cat.plot, mda.dates.dist.plot, layout_matrix = as.matrix(c(1, 1, 1, 2, 2)))
```


### Preferences for incentives {-}

<!-- Revealed Preferences for Incentives AND STATED --> 

In order to distinguish between the private and social motivation of incentives, we asked endline respondents for their preferences for the calendar and bracelet incentives, and separately conducted a [willingness-to-pay survey](#willingness-to-pay-survey-sample) in the control arm. The identification challenge for us is to separate

a) _private valuation_, individuals like the bracelets for their consumption value, and 
<!--I think in B&T intrinsic value is used to refer to the value assigned to deworming, a calendar or bracelet item would have extrinsic value because calendar can be used for dates etc. and bracelet can be worn on wrist -- both are goods to use-->
b) _social valuation_, individuals are influenced by bracelets in their deworming decision because they want to broadcast that their deworming or because they are reminded or learn about deworming by observing others' decisions.

Figure \ref{fig:gift-plots} reports which incentive (bracelet or calendar) individuals preferred as a gift during the endline survey. Calendars are typically preferred by all except for those already dewormed. Similarly, in the willingness-to-pay survey, we find that the majority (72 $\%$) of individuals preferred calendars to bracelets. This provides evidence that individuals assign a higher private value to calendars and that by comparing deworming treatment take-up across calendar and bracelet arms we are able to isolate the social component. 
<!-- weak, needs to be rewritten but hopefully okay for CIFF, really would need model at beginning -->

```{r reported-gift-pref-deworm, ref.label="reported-gift-pref-deworm"}
```

```{r other-incentive-plot, ref.label="other-incentive-plot"}
```

```{r gift-plots, fig.height=4, fig.width=8, fig.cap="Reported calendar/bracelet preferences, split by experiment arm and respondents' deworming take-up."}
plot(reported.gift.pref.dewormed.plot)
# grid.arrange(reported.gift.pref.dewormed.plot, other.have.incentive.plot, 
#              layout_matrix = as.matrix(c(1, 1, 2, 2, 2)))
```

```{r reported-gift-pref-deworm, ref.label="reported-gift-pref-deworm"}
```


### Distance to treatment location {-} 

As described in the [Experiment Design](#experiment-design) section, communities were randomly assigned to be either located _close_ or _far_ from the treatment locations. The distance assignment is key for us to estimate individuals' response to changes in treatment (travel) cost and quantify the utility from social signaling. Due to small changes in the actual location of treatment and the dispersion of households within targeted areas, actual distances to points of treatments were distributed as shown in Figure 11. While there does appear to be some slight overlap between _close_ and _far_ clusters (i.e. non-compliance with assigned treatment), this does not affect the intention-to-treat analysis carried out in this report.

```{r act-dist, fig.width=8, fig.cap="Distribution of actual distance from targeted villages and their assigned treatment location."}
analysis.data %>%  
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% 
  ggplot(aes(dist.to.pot)) +
  geom_density(aes(color = dist.pot.group, linetype = "Household")) +
  geom_density(aes(color = dist.pot.group, linetype = "Cluster Center"),
               data = mutate(village.centers, assigned.treatment = fct_relabel(assigned.treatment, str_to_title))) +
  geom_vline(xintercept = c(1250), linetype = "dashed") +
  labs(y = "Density", 
       caption = "Cluster centers were calculated as the centroid location of all households in cluster.") +
  scale_x_continuous("Distance to Treatment Location (meters)", breaks = seq(0, 10000, 2500/4)) +
  scale_color_discrete("Cluster Distance Assignment", labels = c("Close", "Far")) +
  scale_linetype_discrete("Distance From") +
  facet_wrap(~ assigned.treatment)
```


We can see in Table \ref{tab:mean-assigned-dist} that individuals from _far_ communities had to travel more than twice the distance to treatment locations compared to individuals from _close_ communities. 
<!-- TODO Elaborate on point that "treatment cost" assignment was successful. Sadly, though least difference for bracelets... -->

```{r mean-assigned-dist, warning=FALSE}
analysis.data %>%  
  # anti_join(outlier.clusters, c("sms.treatment", "cluster.id")) %>% 
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% {
    bind_rows(group_by(., assigned.treatment, dist.pot.group) %>%
                summarize(mean.dist = mean(dist.to.pot)) %>%
                ungroup,
              group_by(., dist.pot.group) %>% 
                summarize(mean.dist = mean(dist.to.pot), assigned.treatment = "(All)") %>% 
                ungroup)
  } %>% 
  spread(dist.pot.group, mean.dist) %>% 
  mutate(mean.dist.diff = far - close) %>% 
  kable(col.names = c("Arm", "Close", "Far", "Mean Difference"), 
        caption = "Mean Distance to Treatment Location (meters)",
        format = "latex", align = "lccc", booktabs = TRUE, longtable = FALSE, format.args = list(big.mark = ",")) 
```


### Absolute deworming treatment take-up {-}

By the end of the intervention, we had recorded the deworming treatment of approximately 97,000 individuals. Figure \ref{fig:absolute-takeup} shows how much absolute take-up there was, split by assigned incentive treatment, assigned distance to treatment location, and county. While the pattern of take-up is similar to what we will find in our formal analysis, we are not making any causal interpretations based on these findings. The aim of this study is to learn about impact on the _proportion_ of take-up in targeted communities, and therefore an analysis based on absolute figures would be misleading as we do not have information of what communities all treated individuals are from.


```{r absolute-takeup, fig.height=6, fig.cap="Absolute Deworming Take-up"}
plot.aggreg.takeup <- function(.data) {
  ggplot(.data, aes(assigned.treatment)) +
    geom_bar(alpha = 0.5, color = alpha("black", 0.5)) +
    labs(x = "Treatment", y = "Number of Individuals Dewormed (x 100)", caption = "Note: range on Y axis varies between counties.") +
    facet_grid(county.randomization ~ dist.pot.group, scales = "free_y", margins = TRUE) +
    scale_y_continuous(labels = . %>% divide_by(100)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

takeup.data %>% 
  mutate_at(vars(dist.pot.group, assigned.treatment), funs(factor(.) %>% fct_relabel(str_to_title))) %>% 
  plot.aggreg.takeup 
```

# Structural Model

We model the individuals' utility on deciding to take-up deworming as a function of assigned signal/incentive, SMS, and distance treatment, as
\begin{equation}
\begin{split}
U_{im}(z,s,d) &= u_i^c(z) + u_{im}^n(\bar{y}_{-i,m}; s) + u^h(\bar{y}_{-i,m};z,d) + u^s(\bar{y}_{-i,m};v_i, z, d) + u^r(\bar{y}_{-i,m};\rho_i, z, d) - c_i(d) \label{eqn:structural-utility}
\end{split} 
\end{equation}
where

<!-- , conditional on prosocial type type $v_i$. Health returns can differ in response to inferred peer take-up due to positive externalities, a response that potentially differs between prosocial and non-prosocial individuals. -->

* $z \in \mathcal{Z} = \{\mathrm{control, ink, calendar, bracelet}\}$, is the signal/incentive treatment assigned to $i$'s community.
* $s \in \mathcal{S} = \{\mathrm{control, reminders-only, social-info}\}$, is the SMS treatment assigned to $i$.
* $d \in \mathcal{D} = \{\text{close}, \text{far}\}$, is the distance to treatment location assigned to $i$'s community.
* $m \in \{1,\ldots, 12\}$, is the deworming day.
* $v_i \in \{0, 1\}$, is an indicator for $i$ being of a _prosocial_ type. This is known to $i$ but is unobservable to others.
* $\bar{y}_{-i,m} = \bar{y}_{-i,m}(z, s, d) \in [0, 1]$, is a measure of observed/inferred peer deworming take-up. This is $i$'s subjective belief about deworming in their community, potentially influenced by experimental treatment.
* $u^c_i(z)$ is the private consumption value of $z$ which is known to $i$.
* $u^n_{im}(\bar{y}_{-i}; s)$ captures the effect of deworming salience^[We use this term broadly to refer to any "nudge" or reminder effects, as well as conformity and herding effects.] from observation and information provided by SMS on day $m$. This is also known to $i$.
* $c_i(d)$ is the cost of deworming at distance $d$. This is also known to $i$.
<!-- TODO we should explore heterogeneity here with mixtures models -->
* $u^h(\bar{y}_{-i,m};z,d)$ is the private health benefit of deworming, assumed to be uniform for all $i$ but is unknown.
* $u^s(\bar{y}_{-i,m};v_i,z,d)$ is the social health benefit of deworming, assumed to be the same for all communities but is unknown. This term combines intrinsic motivation and externality, coordination, or conditional cooperation effects, and hence potentially responds directly to the level of community take-up, $\bar{y}_{-i,m}$.
* $\rho_i$ is a measure of how image motivated $i$ is.
* $\omega$ is a measure of the social desirability of deworming.
* $u^r(\bar{y}_{-i,m};\rho_i,z,d) \equiv \rho_i\omega\cdot\left(\Pr_{-i}[v_i = 1|y_{im} = 1, \bar{y}_{-i,m}, z,d] - \Pr_{-i}[v_i = 1|y_{im} = 0, \bar{y}_{-i,m}, z,d]\right)$ is $i$'s belief about how others will infer $v_i$ based on $i$'s deworming, given signal/incentive treatment $z$. This is a random variable due to $i$'s uncertainty about others' inference.

We model the binary decision to take-up deworming, conditional on not having already done so, as
\begin{equation} 
  y_{im}(z,s,d) = \mathbbm{1}(E_i[U_{im}(z,s,d)] > 0) \lor y_{i,m-1}, \label{eqn:dynamic-decision-rule}
\end{equation}
hence,
\begin{equation}
E_i[U_{im}(z,s,d)] = u_i^c(z) + \overbrace{u_{im}^n(\bar{y}_{-i,m}; s) + E_i[u^h(\bar{y}_{-i,m};z,d) + u^s(\bar{y}_{-i,m};v_i,z,d) + u^r(\bar{y}_{-i,m};\rho_i, z,d)]}^{L_{im}(z,s,d)} - c_i(d), \label{eqn:structural-expected-utility} 
\end{equation}
and $E_i[\cdot]$ is $i$'s subjective expectation reflecting uncertainty about $\bar{y}_{-i,m}$ and functions $u^h, u^s$, and $u^r$ (the later with uncertainty about $\omega$ and $\Pr_{-i}[v|y,z,d]$). 

For convenience, we have defined \[L_{im}(z, s, d) \equiv u_{im}^n(\bar{y}_{-i,m}; s) + E_i[u^h(\bar{y}_{-i,m};z,d) + u^s(\bar{y}_{-i,m};v_i,z,d) + u^r(\bar{y}_{-i,m};\rho_i,z,d)],\] a function of $i$'s evolving utility over the intervention's twelve deworming days, driven by observed changes in others' take-up, $\bar{y}_{-i,m}$.  
We can view $i$'s type to be $(\bar{y}_{-i,m}, u^c_i, u_{im}^n, c_i, v_i, \rho_i)$. So far, we have kept our model agnostic about the distribution of types in the population and individuals' priors and learning models (how their beliefs are updated).

\begin{assumption}[Private Consumption Value of Signals/Incentives]
For all $i$, 
\begin{enumerate}
\item $u^c_i(\mathrm{control}) = 0$ and $u^c_i(\mathrm{ink}) \leq 0$: ink has no consumption value.
\item $u^c_i(\mathrm{bracelet}) \geq 0$ and $u^c_i(\mathrm{calendar}) \geq 0$: these are voluntary signals/incentive so they cannot cause dis-utility.
\end{enumerate}
\end{assumption}

\begin{assumption}[Private Cost of Deworming]
For all $i$, $c_i(d) \geq c_i(d') \geq 0, \forall d > d'$.
\end{assumption}

<!-- Below assumption assumes fixed conformity effect. Is this reasonable given that individuals might have different priors on others' take-up based on their community's signal/incentive treatment? Perhaps we can weaken this by using strong priors on this equality and make use of reported beliefs on community take-up (in the baseline survey). This allows the data to overwhelm this assumption if needed. -->

\begin{assumption}[Constant Day One Salience]\label{assume:day-one-salience}
For all $i$, $u^n_{i1}(\bar{y}; s) = u^n_{i1}(\bar{y}'; s), \forall \bar{y}, \bar{y}', s$: on the first day salience/nudge effects are constant across signal/incentive arms. 
\end{assumption}

\begin{assumption}[Constant Prior Beliefs About Health Benefits]
For all $i$,
\begin{enumerate}
\item $E_i[u^h(\bar{y}_{-i,m};z,d)] = E_i[u^h(\bar{y}_{-i,m};z',d')], \forall i \text{ and }\forall z,z',d,d'$: on the first day of deworming prior beliefs about private health benefits are constant and not influenced by beliefs about others' take-up.
\item $E_i[u^s(\bar{y}_{-i,m};v_i,z,d)] = E_i[u^s(\bar{y}_{-i,m};v_i,z',d')|], \forall i\text{ and }\forall z,z',d,d'$: on the first day of deworming prior beliefs about social health benefits and externalities are constant and not influenced by beliefs about others' take-up. 
\end{enumerate}
\end{assumption}

<!-- \begin{assumption}[Baseline Observation for Calendar Incentive]\label{assume:calendar-baseline-observation}
For all $i$, $m$, $s, s', d$ and $d'$, calendars are assumed not to increase observability: 
\begin{enumerate}
\item $\bar{y}_{-i,m}(\text{calendar}, s, d) = \bar{y}_{-i,m}(\text{control}, s, d)$. 
\item $u^r(\bar{y}_{-i,m}(\text{calendar}, s, d); \rho_i, \text{calendar}, d) = u^r(\bar{y}_{-i,m}(\text{control}, s', d'); \rho_i, \text{control}, d')$.
\item $u^h(\bar{y}_{-i,m}(\text{calendar}, s, d); \text{calendar}, d) = u^h(\bar{y}_{-i,m}(\text{control};s, d); \text{control}, d)$. 
\item $u^s(\bar{y}_{-i,m}(\text{calendar}, s, d);v_i, \text{calendar}, d) = u^s(\bar{y}_{-i,m}(\text{control};s, d);v_i, \text{control}, d)$.
\end{enumerate}
\end{assumption}-->

<!-- Previous assumption 5 is not correct (given endline data and reported visibility of calendar) and assumption is also not needed -->
<!-- TODO elaborate on that calendar may have social signaling value too but we remove that since always control for calendar's "consumption value"  -->

\begin{assumption}[Social Information and Reminder Effects]\label{assume:social-info-reminders-only}
For all $i$,
\begin{enumerate}
\item $u^n_{im}(\bar{y}_{-i,m}(z,\text{social-info}, d); \text{social-info}) = u^n_{im}(\bar{y}_{-i,m}(z,\text{reminders-only}, d); \text{reminders-only}), \forall z, d$. 
\item $u^r(\bar{y}_{-i,m}(z,\text{social-info}, d); \rho_i, z, d) = u^r(\bar{y}_{-i,m}(z,\text{reminders-only}, d); \rho_i, z, d), \forall z \in \{\text{control}, \text{calendar}\}, d$.
\end{enumerate}
\end{assumption}

<!-- THINK about 2nd assumption in last set. Possible that should remove -->


# Empirical Models

### Model subscripts {-}

* $i$: individuals
* $j$: clusters
* $k$: strata (counties)

### Randomized treatment variables {-}

* Incentives/signals are split into
    - Private incentives: $Z^p_j \in \mathcal{Z}^p = \{\mathrm{control, calendar, bracelet}\}$
    - Social incentives: $Z^r_j \in \mathcal{Z}^r = \{\mathrm{control, ink, bracelet}\}$
* Assigned distance to treatment location: $D_j \in \{0, 1\}$ is an indicator of being assigned _far_ treatment (vs. _close_).
* SMS treatment: $S_i \in \mathcal{S}$.

For convenience, we define 

* $\widetilde{\mathcal{Z}}^p \equiv \mathcal{Z}^p \setminus \{\text{control}\}$ 
* $\widetilde{\mathcal{Z}}^r \equiv \mathcal{Z}^r \setminus \{\text{control}\}$ 
* $\widetilde{\mathcal{S}} \equiv \mathcal{S} \setminus \{\text{control}\}$
* $Z_w(z) \equiv \mathbbm{1}(z = w)$ 
* $S_w(s) \equiv \mathbbm{1}(s = w)$
* $D_w(d) \equiv \mathbbm{1}(d = w)$

<!-- TODO Karim simplify above to only express treatments in terms of Z_w()... -->

## Willingness-to-Pay Model

Let

* $V^c_i$ and $V^b_i$ be an individual's monetary valuation of calendars and bracelets, respectively.
* $G_i \in \{0, 1\}$ indicates initial gift choice of calendar (vs bracelet). Also, let $\widetilde{G}_i \equiv 2\cdot G_i - 1 \in \{-1, 1\}$.
* $M_i \in \{0, 10, 20,\ldots, 100\}$ be the randomly assigned offer (in Ksh) to switch gifts choice (calendar instead of bracelet and v.v.)
* $W_i(m) \in \{0, 1\}$ indicates accepting $m$ Ksh to switch gift choice.

\begin{align*}
  V_i \equiv V^c_i - V^b_i &\sim \mathtt{StudentT}(\nu_v, \mu_{k[i]}, \sigma) \\
  \mu_k &\sim \mathtt{StudentT}(\nu_\mu, \mu, \tau_\mu) \\
  \mu &\sim \mathtt{StudentT}(\nu_\mu, 0, \tau_\mu) \\
  \sigma &\sim \mathtt{HalfStudentT}(\nu_\sigma, 0, \tau_\sigma)
\end{align*}

with fixed hyper parameters: $\nu_v, \nu_\mu, \nu_\sigma, \tau_\mu, \tau_\sigma$.

<!-- TODO Specify fixed hyperparameter values -->

We estimate these model parameters using the likelihood probability:

\begin{equation*}
\mathcal{L}_i = \left\{\widetilde{G}_i\cdot [F_V(\widetilde{G}_i \cdot M_i|\mu, \mu_{k[i]}, \sigma) - F_V(0|\mu, \mu_{k[i]}, \sigma)]\right\}^{W_i}\cdot\left\{ F_V(\widetilde{G}_i\cdot M_i|\mu, \mu_{k[i]}, \sigma)\right\}^{(1 - W_i)} 
\end{equation*}

## Static Deworming Take-up Model 

In this section, we modified the structural model outlined in Section \ref{structural-model} to accommodate a static binary outcome model. We thus modify \eqref{eqn:dynamic-decision-rule} to be 
\[ y_i(z,s,d) = \mathbbm{1}(E_i[U_i(z,s,d)] > 0), \]
where 
\begin{equation}
E_i[U_i(z,s,d)] \equiv \max_m E_i[U_{im}(z,s,d)] = \tilde{u}^c(z) + \overbrace{\max_m\left\{\tilde{L}_m(z,s,d) + \tilde{\eta}_m\right\}}^{\tilde{L}(z,s,d)} - \tilde{c}(d) + \varepsilon_i. 
\end{equation}

We then model the probability to deworm
\begin{equation}
\begin{split}
\Pr[Y_i(z,s,d) = 1 | z,s,d] &= \Pr[\tilde{u}^c(z) + \tilde{L}(z,s,d) - \tilde{c}(d) + \varepsilon_i > 0] \\
                            &= F\left(\tilde{u}^c(z) + \tilde{L}(z,s,d) - \tilde{c}(d)\right), \label{eqn:static-latent-var-model} 
\end{split}
\end{equation}
where $F$ is the c.d.f. function for $\varepsilon$. We model $\varepsilon$ as having a standard logistic distribution. 

In place of structural terms we introduce the following linear parameters
\begin{align}
\left[\tilde{u}^c(z) - \tilde{c}(d)\right] - \left[\tilde{u}^c(\mathrm{control}) - \tilde{c}(\text{close})\right] = \sum_{w\in\widetilde{\mathcal{Z}}^p} Z_w(z) \times \beta^p_w + D_{\text{far}}(d) \times \beta^d \label{eqn:private-benefits-costs-param}
\end{align}
and
\begin{equation}
\begin{split}
\Delta \tilde{L}(z, s, d) &= \tilde{L}(z, s, d) - \tilde{L}(\mathrm{control}, \mathrm{control}, \text{close}) \\
                          &= \sum_{w\in\widetilde{Z}^r} \left\{Z_w(z)\times\beta^r_{w1} + Z_w(z)\times D_{\text{far}}(d) \times \beta^r_{w2} \right\} \\
            {} &+ \sum_{w\in\widetilde{S}} \left\{S_w(s)\times\beta^s_{w1} + S_w(s)\times D_{\text{far}}(d) \times \beta^s_{w2} \right\} \\
            {} &+ \sum_{u\in\widetilde{Z}^r}\sum_{w\in\widetilde{S}} Z_u(z) \times \left\{S_w(s)\times\beta^{rs}_{uw1} + S_w(s)\times D_{\text{far}}(d) \times \beta^{rs}_{uw2}\right\} \label{eqn:static-learned-params} 
\end{split}
\end{equation}

The main outcome of our analysis is to estimate the posterior distributions of the finite sample treatment effects defined by
\begin{equation} 
\Delta\tau[(z,s,d),(z', s', d')] \equiv \frac{1}{N}\sum_i \Delta\tau_i[(z,s,d),(z', s', d')] = \frac{1}{N}\sum_i Y_i(z,s,d) - Y_i(z',s',d') \label{eqn:static-ate-dist}
\end{equation}
and
\begin{equation}
\Delta\tau[(z,s),(z', s')] \equiv \frac{1}{N}\sum_i \Delta\tau_i[(z,s,D_{j[i]}),(z', s', D_{j[i]})] \label{eqn:static-ate}
\end{equation}
using our estimated model to impute unobservable counterfactual outcomes for all $i$. In particular, we are interested in estimating:

1. $\tau[(\text{ink}, \text{control}), (\text{control}, \text{control})]$, the impact of the combined private and social benefits of the _ink_ signal, since the partial effects captured are 
\[F\left(\tilde{u}^c(\text{ink}) + \tilde{L}(\text{ink},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right). \] 

2. $\tau[(\text{calendar}, \text{control}), (\text{control}, \text{control})]$, the impact of the private benefit of the _calendar_ incentive, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{calendar},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) =\\ 
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right). 
\end{align*}
Since we maintain assumption \ref{assume:calendar-baseline-observation}, $\tilde{L}(\text{calendar},\text{control},D_{j[i]}) = \tilde{L}(\text{control},\text{control},D_{j[i]})$. 

3. $\tau[(\text{bracelet}, \text{control}), (\text{calendar}, \text{control})]$, the impact of the social benefit of the _bracelet_ signal/incentive, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{bracelet},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{calendar},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) = \\
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{bracelet},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right). 
\end{align*}
By social benefit, we refer to all the components of $\tilde{L}$: $\tilde{u}^n, \tilde{u}^h, \tilde{u}^s$, and $\tilde{u}^r$.

4. $\tau[(\text{control}, \text{social-info}), (\text{control}, \text{control})]$, the impact of the social benefit of _social-info_ SMS treatment, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right)
\end{align*}

5. $\tau[(\text{ink}, \text{social-info}), (\text{ink}, \text{control})]$, the impact of the social benefit of _social-info_ SMS treatment with _ink_ available as a social signal, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{ink}) + \tilde{L}(\text{ink},\text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{ink}) + \tilde{L}(\text{ink},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right)
\end{align*}

6. $\tau[(\text{calendar}, \text{social-info}), (\text{calendar}, \text{control})]$, the impact of the social benefit (excluding reputational returns, $u^r$) of _social-info_ SMS treatment with _calendars_ provided as incentives, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{calendar},\text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{calendar},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right).
\end{align*}
Assumption \ref{assume:calendar-baseline-observation} allows us to cancel out the impact of social signaling.

7. $\tau[(\text{bracelet}, \text{social-info}), (\text{calendar}, \text{control})]$, the impact of the social benefit (excluding reputational returns, $u^r$) of _social-info_ SMS treatment with _calendars_ provided as incentives, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{bracelet}) + \tilde{L}(\text{bracelet},\text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{calendar},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) =\\
F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{bracelet},\text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{calendar}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right).
\end{align*}
Assumption \ref{assume:calendar-baseline-observation} allows us to cancel out the impact of social signaling.

8. $\tau[(\text{control}, \text{social-info}), (\text{control}, \text{reminders-only})]$, the impact of social learning from _social-info_ SMS treatment, since the partial effects captured are 
\begin{align*}
F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control}, \text{social-info},D_{j[i]}) - \tilde{c}(D_{j[i]})\right) - F\left(\tilde{u}^c(\text{control}) + \tilde{L}(\text{control},\text{control},D_{j[i]}) - \tilde{c}(D_{j[i]})\right),
\end{align*}
and we maintain assumption \ref{assume:social-info-reminders-only}.  Social learning refers to they increased information from SMS treatment on $u^h$ and $u^s$.


## Dynamic Deworming Take-up Model

To evaluate the structural model outlined in Section \ref{structural-model}, we need to construct a parametric empirical model. First we parameterize the latent expected utility function in \eqref{eqn:structural-expected-utility} to have the following form with additive error terms: $\tilde{\eta}$ to capture preferences for deworming on particular days and $\varepsilon$ to capture individual heterogeneity in other utility terms.
\begin{equation}
E_i[U_{im}(z,s,d)] = \tilde{u}^c(z) + \tilde{L}_m(z,s,d) - \tilde{c}(d) + \tilde{\eta}_m + \varepsilon_{im}. 
\end{equation}
We then model the probability to deworm, conditional on not having already been dewormed, as
\begin{equation}
\begin{split}
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 0, z,s,d] &= \Pr[\tilde{u}^c(z) + \tilde{L}_m(z,s,d) - \tilde{c}(d) + \tilde{\eta}_{m} + \varepsilon_{im} > 0] \\
                                              &= F\left(\tilde{u}^c(z) + \tilde{L}_m(z,s,d) - \tilde{c}(d) + \tilde{\eta}_{m}\right), \label{eqn:latent-var-model} 
\end{split}
\end{equation}
where $F$ is the c.d.f. function for $\varepsilon$. We model $\varepsilon$ as having a reverse extreme value (standard Gumbel) distribution and define $\tilde{\eta}_m \equiv \log \lambda_m$, to easily build a duration analysis model based on our structural model. In other words, we are adopting a complementary log-log link for our binomial model of take-up. The c.d.f. of $\varepsilon$ is therefore $F(z) = 1 - \exp\left\{-\exp[z]\right\}$ and
<!-- &= 1 - \exp\left\{-\exp[\tilde{u}^c(z) + \tilde{L}_m(z,s,d) - \tilde{c}(z, d) + \log \lambda_m]\right\} \\ -->
\begin{equation}
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 0, z,s,d] = 1 - \exp\left\{-\exp[\tilde{u}^c(z) + \tilde{L}_m(z,s,d) - \tilde{c}(z, d)]\cdot\lambda_m\right\},
\end{equation}
which results in a piecewise-constant proportional hazard model [@Wooldridge2010] with $\lambda_m$ as the baseline hazard for deworming day $m$, and with both static (time invariant) and dynamic (time-varying) effects: $(\tilde{u}^c(z) + \tilde{c}(z,s,d))$ and $\tilde{L}_m(z,s,d)$, respectively.

In place of structural terms we introduce the linear parameters in \eqref{eqn:private-benefits-costs-param} and
\begin{equation}
\begin{split}
\Delta \tilde{L}_m(z, s, d) &= \tilde{L}_m(z, s, d) - \tilde{L}_m(\mathrm{control}, \mathrm{control}, 0) \\
                                                                 &= \Delta \tilde{L}_1(z, s, d) + \gamma_m(z, s) \\
\Delta \tilde{L}_1(z, s, d) &= \sum_{w\in\widetilde{Z}^r} \left\{Z_w(z)\times\beta^r_{w1} + Z_w(z)\times d \times \beta^r_{w2} \right\} \\
            {} &+ \sum_{w\in\widetilde{S}} \left\{S_w(s)\times\beta^s_{w1} + S_w(s)\times d \times \beta^s_{w2} \right\} \\
            {} &+ \sum_{u\in\widetilde{Z}^r}\sum_{w\in\widetilde{S}} Z_u(z) \times \left\{S_w(s)\times\beta^{rs}_{uw1} + S_w(s)\times d \times \beta^{rs}_{uw2}\right\} \label{eqn:learned-params} 
\end{split}
\end{equation}
We assume that for deworming days $m > 1$, $\tilde{L}_m(z, ,s, d)$ evolves by a additive change $\gamma_m(z, s)$, which we parameterize to be a quadratic function of (a) the number of days social signals had been observed and (b) the number of SMS messages received
<!-- TODO We're assuming that distance doesn't make a difference on dynamics, which is perhaps a bit too strong. The problem is that we're going to have to add a lot more parameters -->
\begin{equation} 
\gamma_m(z, s) = \sum_{q = 1}^2\left\{\sum_{w\in\widetilde{Z}^r} (m - 1)^q\times Z_w(z)\times\gamma^r_{qw} + \sum_{w\in\widetilde{S}} \lfloor (m - 1)/2 \rfloor^q\times S_w(s)\times\gamma^s_{qw}\right\} \label{eqn:gamma-m}.
\end{equation}
This parameterization requires us to make the following assumption
\begin{assumption}[Learning/Salience Driven Deworming Day Dynamics]
Preference for which days to deworm on is only influenced by baseline preferences, $\tilde{\eta}_m$, and learning/salience dynamics, $\tilde{L}_m$. In other words, individuals are not assumed to alter their choice of deworming day in response to the private consumption value of signals/incentives.
\end{assumption}

Finally, we will use the above terms identifying our structural model's parameters in the model 
<!-- \Pr[Y_{im}(z,s,d) = 0 | Y_{i,m-1} = 0, z,s,d] &= \exp\left[\kappa_m(z,s,d)\lambda_m\right] \equiv \alpha_m(z, s, d) \\ -->
\begin{align*}
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 0, z,s,d] &= 1 - \exp\left[-\kappa_m(z,s,d)\lambda_m\right] \equiv 1 - \alpha_m(z, s, d) \\
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 1, z,s,d] &= 1.
\end{align*}
Where $\kappa_m(z,s,d) \equiv \kappa^{stat}(z,s,d)\cdot\kappa^{dyn}_m(z,s)$, and $\kappa^{stat}(z,s,d)$ is an exponential function with the right-hand terms of \eqref{eqn:private-benefits-costs-param} and \eqref{eqn:learned-params} as the exponent, and $\kappa^{dyn}_m(z,s) = \exp[\gamma_m(z,s)]$ (with $\gamma_m(z,s)$ defined in \eqref{eqn:gamma-m}). 

### Hierarchical Model

We further enrich our model to be hierarchical (by county) and add covariates so our model becomes
\begin{align*}
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 0, X_i, z,s,d] &= 1 - \exp\left[-\kappa_{k[i],m}(z,s,d;X_i)\lambda_{j[i],m}\right] \equiv 1 - \alpha_{k[i],m}(z, s, d; X_i) \\
\Pr[Y_{im}(z,s,d) = 0 | Y_{i,m-1} = 0, X_i, z,s,d] &= \exp\left[\kappa_{k[i],m}(z,s,d;X_i)\lambda_{j[i],m}\right] \equiv \alpha_{k[i],m}(z, s, d; X_i) \\
\Pr[Y_{im}(z,s,d) = 1 | Y_{i,m-1} = 1, X_i, z,s,d] &= 1 \\
\Pr[Y_{im}(z,s,d) = 0 | Y_{i,m-1} = 1, X_i, z,s,d] &= 0, 
\end{align*}
and
\[ \lambda_{jm} = v^{clust}_j\cdot v^{strat}_{k[j]}\cdot \lambda_m, \]
introducing both stratum and cluster effects.

We conducted our analysis using the following priors on the model's parameters and hyper parameters:
\begin{align*}
-\exp(\lambda_m) &\sim \mathtt{Uniform}[0, 1] \\
v^{clust}_j &\sim \mathtt{Gamma}(\delta^{clust}, \delta^{clust}) \\
v^{strat}_k &\sim \mathtt{Gamma}(\delta^{strat}, \delta^{strat}) \\
\beta &\sim \mathtt{StudentT}\left(\nu^{coef}, 0, \begin{pmatrix} \sigma^{coef} & 0             & \cdots & 0  \\
                                                     0             & \sigma^{coef} & \cdots & 0 \\ 
                                                     \vdots        &               & \ddots &   \\
                                                     0             &               &        & \sigma^{coef} \end{pmatrix}\right) \\\\
\beta_k &\sim \mathtt{StudentT}\left(\nu^{coef}, \beta, \begin{pmatrix} \tau_1 & 0             & \cdots & 0  \\
                                                     0             & \tau_2 & \cdots & 0 \\ 
                                                     \vdots        &               & \ddots &   \\
                                                     0             &               &        &  \end{pmatrix}\right) \\\\
\gamma &\sim \mathtt{StudentT}\left(\nu^{coef}, 0, \begin{pmatrix} \sigma^{coef} & 0             & \cdots & 0  \\
                                                     0             & \sigma^{coef} & \cdots & 0 \\ 
                                                     \vdots        &               & \ddots &   \\
                                                     0             &               &        & \sigma^{coef} \end{pmatrix}\right) \\\\
\gamma_k &\sim \mathtt{StudentT}\left(\nu^{coef}, \gamma, \begin{pmatrix} \tau^{dyn}_{1} & 0             & \cdots & 0  \\
                                                     0             & \tau^{dyn}_2 & \cdots & 0 \\ 
                                                     \vdots        &               & \ddots &   \\
                                                     0            &               &        &  \end{pmatrix}\right) \\
\delta^{clust} &\sim \mathtt{HalfStudentT}(\nu^{scale}, 0, \tau^{scale}) \\
\delta^{strat} &\sim \mathtt{HalfStudentT}(\nu^{scale}, 0, \tau^{scale}) \\
\tau^{clust} &\sim \mathtt{HalfStudentT}(\nu^{scale}, 0, \sigma^{scale}) \\ 
\tau^{strat} &\sim \mathtt{HalfStudentT}(\nu^{scale}, 0, \sigma^{scale}) \\
\tau &\sim \mathtt{HalfStudentT}(\nu^{scale}, 0, \sigma^{scale}) 
\end{align*}

With constant hyper parameters: $\nu^{coef}, \nu^{scale}, \sigma^{coef}, \sigma^{scale}$.
<!-- TODO Specify values for fixed hyper parameters -->

To estimate this model we use the likelihood probability:

\[ \mathcal{L}_i = \prod_{m = 1}^{M_i - 1} \alpha_{k[i],m}(z, s, d; X_i) \cdot \left(1 - \alpha_{k[i],M_i}(z, s, d;X_i)\right)^{Y_i} \]

# Results

## Willingness-to-Pay

The WTP experiment was implemented with a random subsample of adults in the no incentive i.e. control group after the end of the community deworming program. The adults had therefore no prior exposure to the bracelet or calendar incentive.

```{r, ref.label="wtp-stan-data"}
```

```{r, ref.label="load-wtp-fit", include=FALSE}
```

```{r, ref.label="prepare-wtp-sim-data"}
```

Table \ref{tab:wtp} shows the summary of the posterior distribution of the willingness-to-pay model. As shown, the posterior probability of preferring calendar to bracelets is high with an average of 42-53 Ksh difference in valuation. 

```{r wtp-table, results="asis"}
wtp_model_0_fit %>% 
  summary(par = c("hyper_mu_wtp_diff", "sigma_wtp_diff", "mu_wtp_diff", "hyper_prob_prefer_calendar", "prob_prefer_calendar"), 
          probs = c(0.025, 0.05, 0.5, 0.95, 0.975)) %$% 
  summary %>% 
  xtable::xtable(caption = "Posterior Estimates for Willing-to-Pay Parameters\\label{tab:wtp}",
                 align = "lrrrrrrrrrr") %>% 
  print(sanitize.colnames.function = . %>% 
          str_replace_all(c("se\\_mean" = "$SE_{Mean}$",
                            "mean" = "Mean",
                            "sd" = "SD",
                            "%" = "\\\\%",
                            "n_eff" = "$N_{eff}$",
                            "Rhat" = "$\\\\hat{R}$")),
        sanitize.rownames.function = . %>% 
          str_replace_all(c("hyper_mu_wtp_diff" = "$\\\\mu$",
                            "sigma_wtp_diff" = "$\\\\sigma$",
                            "mu_wtp_diff\\[(\\d)\\]" = "$\\\\mu_\\1$",
                            "hyper_prob_prefer_calendar" = "$\\\\Pr[V^c_i > V^b_i]$",
                            "prob_prefer_calendar\\[(\\d)\\]" = "$\\\\Pr[V^c_i > V^b_i|k = \\1]$")),
        booktabs = TRUE,
        comment = FALSE)
```

## Static Deworming Take-up Model 

\begin{assumption}[Private Consumption Value of Bracelets]\label{assume:calendar-bracelet-private-value}
We assume the private value of bracelets is equal to calendars : $\beta^p_{calendar} = \beta^p_{bracelet}$ for all strata. This is a conservative assumption given the greater preference for calendars shown in our willingness-to-pay analysis above. 
\end{assumption}

In the results of the static and dynamic model, we present both the combined social and private consumption effect of the bracelet incentive as the treatment arm “Bracelet” and the social value only imputed treatment arm as “Bracelet Social”.

```{r load-static-model-fit, ref.label="load-static-model-fit", include=FALSE}
```

```{r basic-model-1-prep-data, ref.label="basic-model-1-prep-data", include=FALSE, dependson="load-static-model-fit"}
```

```{r static-model-ate-plot, ref.label="static-model-ate-plot", fig.width=10, fig.height=7, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment)", dependson="basic-model-1-prep-data"}
```

```{r static-model-dist-ate-plot, ref.label="static-model-dist-ate-plot", fig.width=10, fig.height=12, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment), split by distance.", dependson="basic-model-1-prep-data"}
```

```{r static-model-phone-ate-plot, ref.label="static-model-phone-ate-plot", fig.width=10, fig.height=10, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment), split by phone-ownership type.", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-model-phone-dist-ate-plot, ref.label="static-model-phone-dist-ate-plot", fig.width=10, fig.height=10, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment), for phone-owners only, split by distance from treatment location.", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-model-non-phone-dist-ate-plot, ref.label="static-model-non-phone-dist-ate-plot", fig.width=10, fig.height=5, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment), for non-phone-owners only, split by distance from treatment location.", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-est-takeup-plotter, ref.label="static-est-takeup-plotter"}
```

```{r static-model-takeup-plot, ref.label="static-model-takeup-plot", fig.width=10, fig.height=4, fig.cap="Posterior distribution of the probability of deworming take-up.", dependson=c("basic-model-1-prep-data", "static-est-takeup-plotter")}
```

```{r static-model-dist-takeup-plot, ref.label="static-model-dist-takeup-plot", fig.width=10, fig.height=8, fig.cap="Posterior distribution of the probability of deworming take-up, split by distance.", dependson=c("basic-model-1-prep-data", "static-est-takeup-plotter")}
```

```{r static-model-phone-dist-takeup-plot, ref.label="static-model-phone-dist-takeup-plot", fig.width=10, fig.height=11, fig.cap="Posterior distribution of the probability of deworming take-up, split by phone ownership and distance from treatment location.", dependson=c("basic-model-1-prep-data", "static-est-takeup-plotter"), eval=FALSE}
```

```{r static-model-ate-percent-plot, ref.label="static-model-ate-percent-plot", fig.width=10, fig.height=7, fig.cap="Posterior distribution of percentage change in take-up compared with the control arm take-up (with no SMS treatment)", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-model-phone-ate-percent-plot, ref.label="static-model-phone-ate-percent-plot", fig.width=10, fig.height=10, fig.cap="Posterior distribution of percentage change in take-up compared with the control arm take-up (with no SMS treatment), split by phone-ownership type.", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-model-phone-dist-ate-percent-plot, ref.label="static-model-phone-dist-ate-percent-plot", fig.width=10, fig.height=10, fig.cap="Posterior distribution of percentage change in take-up compared with the control arm take-up (with no SMS treatment), for phone-owners only, split by distance from treatment location.", dependson="basic-model-1-prep-data", eval=FALSE}
```

```{r static-model-non-phone-dist-ate-percent-plot, ref.label="static-model-non-phone-dist-ate-percent-plot", fig.width=10, fig.height=5, fig.cap="Posterior distribution of percentage change in take-up compared with the control arm take-up (with no SMS treatment), for non-phone-owners only, split by distance from treatment location.", dependson="basic-model-1-prep-data", eval=FALSE}
```

In Figure \ref{fig:static-model-ate-plot} we report the posterior distribution of deworming take-up levels as defined in \eqref{eqn:static-ate}. Looking at treatment effects for individuals that did not receive the SMS treatment (Figure \ref{fig:static-model-ate-plot}, indicated in red), we find the biggest treatment effects for the bracelet incentives. Controlling for their consumption value, bracelets as signals (“Bracelet Social”) increased deworming take-up by 4 percentage points from 21 percent in the control to 25 percent, which is equivalent to a 19% increase in take-up.

The combined consumption and signaling treatment effect of bracelets (“Bracelet”) is three times that of calendars, despite the higher private valuation individuals expressed for calendars in the WTP experiment. 

We find a close to zero average treatment effect for the ink incentive, with substantial heterogeneity in the impact across close (-4pp) and far communities (+1pp) as shown in Figure \ref{fig:static-model-dist-ate-plot}. The results suggest that mandatory signaling as in the case of inking people’s thumb, can dissuade marginal individuals if the private valuation of the signal is negative. 

Looking at treatment effects for individuals that also received the SMS reminder and social information treatment (Figure \ref{fig:static-model-ate-plot}, indicated in blue), we find a large increases in take-up across all incentive arms and the control group. We achieve deworming take-up levels of 48 percent in the control group up to 60 percent in the bracelet arm (Figure \ref{fig:static-model-takeup-plot}). By combining the SMS treatment with the calendar incentive, we intended to control for the consumption value of the bracelets and mimic the reminder/nudge effects as well as potential learning that could take place in the presence of observability in the bracelet treatment. The combined treatment effect of calendar plus SMS is 16 percentage points, which is almost triple the effect of the bracelet incentive (“Bracelets”). The SMS reminder and/or social learning treatment effects are much stronger than any potential reminder or social learning effects that are introduced in the ink or bracelet treatment. 

We find similar results for the ink versus control group comparison. Providing individuals in the control group with SMS reminders (Figure \ref{fig:static-model-ate-plot}, indicated in green), increases the probability of deworming take-up by 15 percentage points. The very similar treatment effects of SMS reminder only (15pp) and SMS reminder plus social information (13pp) for the control group suggest that the SMS treatment mainly works as a reminder. The results from the dynamic model further support this. The posterior distribution of the daily finite sample average probability of deworming take-up (Figure \ref{fig:fast-sim-daily-sms-plot}) shows that the SMS treatment leads to the largest increases in take-up on day one and two, as a result of the text message reminder that was sent the day before treatment started. The treatment effects become negligible for later days, suggesting that text messages sent on days 4, 6, 8 and 10 and the social information contained in them had no relevant effect on deworming decisions. 

Comparing the effects of the SMS treatment across incentive arms (Figure \ref{fig:static-model-ate-plot}, with the control group, social info as reference), we find increasing effects from ink (-2pp) to calendar (+4pp) to bracelets (+12). Our main interpretation is that there are complementarities between incentives and private nudges, which increase with the strength of the incentive treatment. 

The static model allowed us to control for the consumption value of the bracelet incentive, separately identifying the social treatment component of bracelets. However, due to the (unanticipated) disproportionately large effects of the SMS treatment we are unable to create a valid counterfactual to control for the reminder and/or social learning effects introduced by bracelets or ink. The identify social signaling concerns we introduce dynamics and test for the presence of reminder and learning effects. 

## Dynamic Deworming Take-up

In this section we report the posterior distributions of^[Keep in mind that shown estimators are random functions of $\hat{\theta}$.]

* The finite sample average of the probability of take-up on each deworming day and the probability of take-up on any day
  \begin{align}
    \frac{1}{N}\sum_{i=1}^N &\Pr[Y_{im}(z, s, d, m') = 1|\hat{\theta}_{k[i]}] \label{eqn:daily-takeup-level} \\
    \frac{1}{N}\sum_{i=1}^N &\Pr[Y_i(z, s, d) = 1|\hat{\theta}_{k[i]}]. \label{eqn:any-day-takeup-level}
  \end{align}
  We use the notation $Pr[Y_{im}(z, s, d, m') = 1|\hat{\theta}]$ to refer to the probability of deworming on day $m$, given $m'$ days of social signaling and SMS treatment. In our results we will be looking at two cases, (i) the observed outcomes when $m' = 11$ and (ii) the unobserved outcome when $m' = 0$. 
* The finite sample average treatment effect on take-up on each deworming day and on any day
  \begin{align}
    \frac{1}{N}\sum_{i=1}^N &\Pr[Y_{im}(z', s', d', m'') = 1|\hat{\theta}_{k[i]}] - \Pr[Y_{im}(z, s, d, m') = 1|\hat{\theta}_{k[i]}] \label{eqn:daily-ate} \\
    \frac{1}{N}\sum_{i=1}^N &\Pr[Y_i(z', s', d') = 1|\hat{\theta}_{k[i]}] - \Pr[Y_i(z, s, d) = 1|\hat{\theta}_{k[i]}]. \label{eqn:any-day-ate} 
  \end{align}
* The finite sample average dynamic effect of signals and SMS treatment
  \begin{equation}
    \frac{1}{N}\sum_{i=1}^N \kappa_m^{dyn}(z,s;\hat{\theta}_{k[i]}) \label{eqn:dyn-kappa}.
  \end{equation}


```{r, ref.label="dyn-model-ate"}
```

```{r, ref.label="dyn-stan-data"}
```

```{r, ref.label="old-load-dyn-model-fit", include=FALSE}
```

```{r, ref.label="dyn-model-sim-params"}
```

```{r load-prepared-fast-sim}
load(file.path("data", "prepared_fast_sim.RData"))

```

```{r, ref.label="fast-sim-ate"}
```


In Figure \ref{fig:sim-fast-take-up}, we are reporting the posterior distribution of deworming take-up levels as defined in \eqref{eqn:any-day-takeup-level}, separately by SMS cross treatment. Figure \ref{fig:sim-fast-take-up-dist} reports the same but split by distance to treatment location.

```{r sim-fast-take-up, ref.label="sim-fast-take-up", fig.width=9, fig.height=5, fig.cap="Posterior distribution of the finite sample average probability of deworming take-up across all treatments and subgroups (dynamic model)."}
```

```{r sim-fast-take-up-dist, ref.label="sim-fast-take-up-dist", fig.width=9, fig.height=7, fig.cap="Posterior distribution of the finite sample average probability of deworming take-up across all treatments, split by distance (dynamic model)."}
```

In Figure \ref{fig:fast-sim-ate-plot}, we report the posterior distribution of treatment effects as defined in \eqref{eqn:any-day-ate}, separately by SMS cross treatment. Figure \ref{fig:fast-sim-ate-dist-plot} reports the same split by distance to treatment location. We report treatment effect in comparison with

i. The control arm, with no SMS treatment, and with the same distance from treatment location
ii. The control arm, with social information SMS treatment, and with the same distance from treatment location
iii. The same arm, with no SMS treatment, and with the same distance from treatment location

```{r fast-sim-ate-plot, ref.label="fast-sim-ate-plot", fig.width=10, fig.height=8, fig.cap="Posterior distribution of the finite sample average treatment effect across all treatments and subgroups, split by phone ownership (dynamic model)."}
```

```{r fast-sim-ate-dist-plot, ref.label="fast-sim-ate-dist-plot", fig.width=10, fig.height=10, fig.cap="Posterior distribution of the finite sample average treatment effect across all treatments and subgroups."}
```

In Figure \ref{fig:fast-sim-daily-obs-plot}, we report the posterior daily mean of the probability of deworming as defined in \eqref{eqn:daily-takeup-level}, separately by distance from treatment location. We also report the "no observation" predicted counterfactual showing how the impact of signals would differ had there been no difference in salience/learning dynamics from the baseline level in the the control arm.

```{r fast-sim-daily-obs-plot, ref.label="fast-sim-daily-obs-plot", fig.width=10, fig.height=5, fig.cap="Posterior distribution of the daily finite sample average probability of deworming take-up (with no SMS treatment)."}
```

In Figure \ref{fig:fast-sim-daily-dyn-kappa}, we show the shape of the $\kappa^{dyn}_m$ quadratic functions, as defined in \eqref{eqn:dyn-kappa}, for the ink and bracelet arms.

```{r fast-sim-daily-dyn-kappa, ref.label="fast-sim-daily-dyn-kappa", fig.width=8, fig.cap="Posterior distribution of the finite sample dynamic effect of signal observation."}
```

In Figure \ref{fig:fast-sim-daily-ate-obs-plot}, we report the daily posterior mean difference in the probability of deworming take-up compared to the control arm, as defined in \eqref{eqn:daily-ate}, and separately by distance from treatment location. We also report the "no observation" predicted counterfactual difference showing how the impact of signals would differ had there been no difference in salience/learning dynamics from the baseline level in the the control arm.

```{r fast-sim-daily-ate-obs-plot, ref.label="fast-sim-daily-ate-obs-plot", fig.width=10, fig.height=5, fig.cap="Posterior distribution of the daily finite sample average treatment effect (with no SMS treatment)."}
```

In Figure \ref{fig:fast-sim-daily-sms-plot}, we report the posterior daily mean of the probability of deworming as defined in \eqref{eqn:daily-takeup-level}, separately by signal/incentive treatment and SMS treatment. We also report the predicted counterfactual of SMS recruitment and one pre-MDA reminder SMS message.

```{r fast-sim-daily-sms-plot, ref.label="fast-sim-daily-sms-plot", fig.width=9, fig.cap="Posterior distribution of the daily finite sample average probability of deworming take-up (with SMS treatment)."}
```

<!-- TODO We are not showing the dynamics of SMS with no signal observation. -->

In Figure \ref{fig:sim-fast-daily-sms-dyn-kappa}, we show the shape of the $\kappa^{dyn}_m$ quadratic functions, as defined in \eqref{eqn:dyn-kappa}, for all arms and SMS treatment.

```{r sim-fast-daily-sms-dyn-kappa, ref.label="sim-fast-daily-sms-dyn-kappa", fig.width=8, fig.height=4, fig.cap="Posterior distribution of the finite sample dynamic effect of SMS treatment."}
```

In Figure \ref{fig:fast-sim-daily-ate-sms-plot}, we report the daily posterior mean difference in the probability of deworming take-up compared to the control arm, as defined in \eqref{eqn:daily-ate}, and separately by signal/incentive and distance from treatment location. We also report the "no salience" predicted counterfactual difference.

```{r fast-sim-daily-ate-sms-plot, ref.label="fast-sim-daily-ate-sms-plot", fig.width=9, fig.height=8, fig.cap="Posterior distribution of the daily finite sample average treatment effect (with SMS treatment)."}
```

In Figure \ref{fig:fast-sim-ate-day-one}, we focus our analysis on the first deworming day. We report posterior mean treatment effects on deworming take-up of SMS treatment, compared to take-up levels in the same signal/incentive arm with no SMS treatment. For reference, we also show the baseline take-up level.

```{r fast-sim-ate-day-one, ref.label="fast-sim-ate-day-one", fig.width=10, fig.height=7, fig.cap="Posterior distribution of the finite sample average treatment effect of SMS treatment on take-up on deworming day one, for phone owners only."}
```

In Figure \ref{fig:fast-sim-no-obs-plot}, we show how treatment effects on deworming differ with (solid line) and without (dashed line) dynamic salience/learning.

```{r fast-sim-no-obs-plot, ref.label="fast-sim-no-obs-plot", fig.width=10, fig.height=9, fig.cap="Posterior distribution of the finite sample average treatment effect across all treatments and subgroups."}
```

The dynamics model allows us to test for treatment effect changes over time that are due to social learning or salience/reminder effects as individuals can observe others’ treatment decisions. The model allows us to separate static impacts on take-up--with a fixed proportional impact on take-up over the 12 deworming days--and dynamic changes resulting in a temporal shift in the preference of deworming day which we assume must be due to learning/salience effects. Therefore, by shutting down this dynamic component of the model we eliminate learning and salience. This also results in discarding any learning effects relevant to social signaling, i.e., updating of beliefs on reputational returns to signaling. Nevertheless, this does not present a problem since we find practically negligible dynamic changes across treatments. We thus conclude that the impact of bracelets, after controlling for their private consumption utility, is entirely driven by social signaling.

# Conclusion

This paper provides field experimental evidence on the effects of making actions observable in the context of deworming. Working with the Kenyan Government, we introduced a new community deworming program where adults were offered free deworming treatment at central locations. We show that social incentives can lead to meaningful increases in deworming take-up and outperform material incentives. Our experiment also identifies social signaling concerns, overcoming a main identification challenge when introducing visibility in actions in a dynamic setting. We also provide evidence of the powerful nature of private nudges. The SMS treatment had the unintended consequence of being most effective in increasing deworming take-up. We believe that this research can be extended in several directions. First, it will be important to test whether social incentives can have similar effects on take-up in future rounds of community deworming. Once community deworming is no longer novel and the signals are repeatedly implemented, will treatment effects disappear or could they increase as signals could contribute to forming stronger norms around community deworming. Second, we believe that understanding the underlying mechanism of social signaling in deworming will be key to apply social signaling to other public good domains and health behaviors. Future research should investigate the social costs and sanctions or reputational benefits that people gain from signaling. Finally, given the large effects of private text message nudges it will be important to understand if the effects are dependent on the initial in-person sensitization or the in-person recruitment that was part of this experiment, or if we could send simple text message reminders to all households in Kenya and thereby increase deworming take-up.

# References

<div id="refs"></div>
