---
title: "The Role of Social Signaling in Community Mass Deworming"
subtitle: "Evidence from a Field Experiment in Kenya"
output: 
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
header-includes:
   - \usepackage{pxfonts}
   - \usepackage{bbm}
---

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(tibble)
library(tidyr)
library(lubridate)
library(purrr)
library(readr)
library(haven)
library(broom)
library(ggplot2)
library(ggmap)
library(stringr)

source("takeup_rct_assign_clusters.R")

# rct.schools.data <- read_rds("takeup_rct_schools.rds")

knitr::opts_chunk$set(echo = FALSE, cache = TRUE, cache.path = "takeup_pap")

```
# Abstract
registry 

# Abstract

Registry

# Introduction
UCB IRB background
Expand on social signaling 

* UC Berkeley background 
* Expand on social signaling part (B&T)

# Intervention
registry 

Registy

# Research Questions
Our main research question is: Can social signaling incentivize adults to take up deworming treatment? The experiment contains the following 9 treatments arms:

|                             | Control  | Ink | Bracelet | Calendar |
|-----------------------------|----------|-----|----------|----------|
| No SMS                      | 1        | 4   | 6        | 8        |
| Reminder SMS                | 2        | -   | -        | -        |
| Reminder  + Social Info SMS | 3        | 5   | 7        | 9        |


1) Reminder and social information text message treatment vs. no text messages for control individuals: a random subsample of phone owners within each control (no incentive) cluster is randomized into receiving no text message (1 in above table), receiving a reminder text message about the availability of deworming treatment (2) or receiving a reminder text message that also provided information about other community members deworming treatment take-up. Comparing (1) vs. (2) will allow us to identify the effect reminders have on the probability of deworming treatment take-up. Comparing (1) vs. (3) we estimate the effect that reminders plus information about other people's deworming choice has on individuals' deworming take-up. By differencing the effects of (1 vs. 3 ~ reminder + social info effect) and (1 vs. 3 ~ reminder effect only) we identify the effect social learning has on deworming take-up behavior. The text message treatment (CROSS CUT?) across control clusters allows us to identify whether reminder and/or social learning is relevant in the context of deworming take-up. 

2) Social information text message treatment vs. no text messages for Ink / Bracelet individuals: a random subsample of phone owners within each ink and bracelet cluster is randomized into receiving no text message (4 and 6 in above table) or receiving a reminder text message that also provides information about other community members deworming treatment take-up. Comparing (4) vs. (5) and (6) vs. (7) we identify the additional reminder and social learning effect of text messages given visibility of deworming take-up choices through ink and bracelets. These treatment show how "satiated" individuals are in terms being reminded and social learning through visibile signals. If we find no significant effect in take-up behavior for these treatments, reminder and social learning are either not relevant or the ink and bracelets have already reminded people or facilitated social learning. To know which is true we look at the control group comparison in 1): if we find no significant effect for text messages within the control group, ink or bracelets had no reminder or social learning effect; if we find a significant effect for text messages within the control group, ink or bracelets had a reminder or social learning effect such that the marginal reminder/social learning effect of text messages is insignificant. 

3) No incentive vs. ink for text message treatment individuals: comparing individuals that received reminder plus social information text messages across clusters where no incentive was given when coming for deworming treatment (3 in above table) vs. clusters where individuals had their thumb marked with ink when coming for deworming treatment (5), we identify the effect of social signaling on individuals' decision to deworm. A comparison only within text message recipients allows to control for the potential reminder effect (when seeing other people with ink on their thumb, people might be reminded of the availability of deworming treatment) and social learning effect (when seeing other people with ink on their thumb, people might update their beliefs of how many people in their community take up deworming and therefore its importance or value) ink has on people's deworming choice. 
If reminder and social learning effects turn out to be insignificant in 1) we can pool individuals from groups (1), (2) and (3) and compare them to individuals from (4) and (5). Question: could also compare (4) vs. (3) i.e. only applying text treatment for control?

4) Calendar incentive vs. bracelet for text message treatment individuals: comparing individuals that received reminder plus social information text messages across clusters where a calendar incentive was given for deworming (9 in above table) vs. clusters were individuals received a bracelet (7), we identify the effect of social signaling on individuals' decision to deworm. Same as for the control-ink comparison, comparing text message recipients only allows us to control for the potential reminder effect (when seeing other people with a bracelet, people might be reminded of the availability of deworming treatment) and social learning effect (when seeing other people with a bracelet, people might update their beliefs about deworming take-up in their community and therefore its importance or value) bracelets have on people's deworming choice. By comparing the bracelet treatment to the calendar treatment we control for the consumption value of the bracelet and any normative effect a material incentive could have on people's deworming choices. 

Note: we chose to test two different social signaling treatments, ink and bracelets, in this experiment. The experiment is meant to generate cost-effective solutions to increasing deworming take-up. The cost of ink is close to zero and ink has no consumption value i.e. we eliminate that confound, but ink is potentially less visible, wears off over time (after 2 weeks?)

5) Testing of auxiliary assumptions:
a) private value of bracelets is equivalent to that of calendar. 

Non-experimental test: revealed choice between bracelet and calendar. 


Explain why ink and bracelet


Justification for why we use ink AND bracelets and not just one of the two - difference in treatment effects due to different characteristics of ink and bracelets. (political), (observability) 

Our main research question is: Can social signaling incentivize adults to take up deworming treatment?

# Experiment Design

This study will adopt a cluster randomized experiment to make causal inferences addressing our research questions. We selected subcounties in three counties in western Kenya where soil transmitted helminths are endemic: Busia, Siaya and Kakamega. We then identified 158 clusters (communities) dispersed across the selected region. After various surveys identifying clusters where implementation would be infeasible, the study was reduced to 146 clusters. In each cluster, we conducted a census of all households and eligible adults (18 years or older). 

All communities in the experiment will be provided with 

* Deworming treatment at a point-of-treatment 
* An outreach campaign providing information on the location and duration of treatment, as well as framing the public good aspect of deworming.

We then randomly assigned treatment over cluster, stratified over counties and distance to the point-of-treatment.

## Clustered Design

The experiment will be carried out in 18 subcounties in western Kenya, randomized at the cluster level. A _cluster_ is composed of 

(i) a centralized _point-of-treatment (PoT)_ at an easily identifiable location (e.g. near a ~~primary school~~ church/mosque), and
(ii) a _targeted village_ where we will conduct an outreach campaign^[Other communities will not be denied treatment, but our analysis will be focused on targeted villages.].

## Experimental Manipulation

In the experiment there will be two levels of randomized treatment assignment.

1. At the cluster level, there will be four groups:
    (i) a control group
    (ii) a private incentive group: wall calendars provided as gifts to treatment compliers
    (iii) a low private value, low visibility social incentive group: indelible ink mark on treatment compliers' hands
    (iv) a high private value, high visibility social incentive group: colorful silicon bracelets will be provided as gifts to treatment compliers 
2. At the individual level, there will be three groups:
    (i) the control group, composed of a stratified sample of
        a. phone owners
        b. non-phone owners
    (ii) the text message reminder group: participants will receive regular messages on where and when treatment will be available
    (iii) the text message and peer take-up information group: participants will receive regular messages on where and when treatment will be available, as well as the proportion of treatment take-up among others in their village.

## Cluster Selection Algorithm

The selection of clusters (PoT and targeted villages) relied on geospatial data of primary schools in the targeted subcounties. While schools did not play a direct role in the study's implementation, they were used as proxies for the location of communities.

Below is the main body of the selection algorithm:

1. Let $\mathcal{C}$ be the set of all potential clusters, defined as 2.5 kilometer radius circle centered on a primary school in the study region. In this study the size of this set is $\#\mathcal{C} = 1,451$.
2. Let $\mathcal{R} := \emptyset$ be the set of clusters selected for the experiment
3. While $\mathcal{C} \neq \emptyset$:
    a) Randomly pick $i \in \mathcal{C}$
    b) Set $\mathcal{C} := \mathcal{C}\setminus\{i\}$
    c) If $(ClusterSize(i, \mathcal{R}) < ThresholdClusterSize) \lor (\exists j \in \mathcal{R}, ClusterSize(j, \mathcal{R} \cup \{i\}) < ThresholdClusterSize)$: 
        i. Repeat Loop
        
          Else:
          
        i. Set $\mathcal{R} := \mathcal{R} \bigcup \{i\}$
4. If $\#\mathcal{R} < NumRctClusters$: Goto 1

$ClusterSize(m, \mathcal{M})$ is a function that returns the size of cluster $m$, removing any overlaps with the clusters in $\mathcal{M}$. We defined the size of a cluster to be the number of primary schools available in the non-overlapped 2.5 km circle around the cluster center (as a proxy of the available communities to target). We set the cluster size threshold to be 1 primary school^[To be exact we defined the threshold to be 60% of a 1 km radius circle around a school.].  

While we use a 2.5 km circle to define the boundary of the area we will target communities within for treatment, when considering overlaps we assume points-of-treatment would have larger catchment areas, thus providing buffers between clusters. In order to fit the study's geographic area we randomly split the PoT to have 3 and 4 km catchment areas. Thus a targeted village would always be at least 0.5 km closer to its own assigned point-of-treatment than any other cluster's.

This first step of cluster selection yielded 158 clusters.

```{r, echo = FALSE}

```


## Treatment Assignment Mechanism

## Village and Point-of-Treatment Selection

## Power Calculation

# Data Collection and Sample Selection

## Pre-Intervention

### Census

A census of all households in _targeted villages_ will be conducted before the treatment intervention. It will be used to randomly select households for surveying and further individual level interventions, as well as to monitor treatment take-up. Information on all adults, 15 years of age or older:

a) Name
b) Gender
c) Age
d) Household head name
e) Last two digits of phone number
f) GPS coordinates of each house

### Baseline Household Survey

## Mid-Intervention

### Treatment Take-up Monitoring

#### Name Matching

### SMS Airtime Reward

## Post-Intervention

### Endline Household Survey

### Social Knowledge

## Data Quality

### Backchecks

### Geographic and Time Monitoring

# Analysis

Below is the primary counterfactual framework we will use:

* $i$ indexes individuals and $j$ indexes clusters
* $Z_j \in \mathcal{Z} = \{control, ink, calendar, bracelet\}$ is the cluster level treatment
* $S_{ij} \in \mathcal{S} = \{none, reminders, socialinfo\}$ is the individual level text message treatment
* $Y_{ij}(z, s) \in \{0, 1\}$ is an individual deworming outcome in response to treatment $z$ and $s$. * $Y_j(z)$ is cluster $j$'s absolute number of treatment seekers in response to treatment $z$.
* $X_{ij}$ individual and cluster level pre-treatment characteristics. All analysis below will also be done controling for covariates. 

Inference will be conducted using cluster robust variance estimators as well as using block bootstrapping.

## Cluster Level Treatment Specifications

The first specifications comparing the finite sample impact of various treatment arms and text message treatment are
 \[ \frac{\sum_{j=1}^J Y_j(z') - Y_j(z)}{J}, \]
 and
\[ \frac{\sum_{i=1}^N Y_{ij}(z', none) - Y_{ij}(z, none)}{N} \]
 at the cluster level. 
 
 We will estimate these models using Neyman's repeated sampling approach or by regression analysis
 \[ Y_j = \alpha_1 + \beta_1 \cdot Z_j + \varepsilon_{j} \]
 and
 \[ Y_{ij} = \alpha_2 + \sum_{k \in \mathcal{Z}\setminus \{control\}} \beta_{k} \cdot \mathbbm{1}\{Z_j = k\} + \nu_{ij} \]

[Include stratification] 
    
## Cross-cut with Reminders and Informational Messages

To assess the impact reminder and social information text messages we will estimate the finite sample impact
\[ \frac{\sum_{i=1}^N Y_{ij}(z', s) - Y_{ij}(z, s)}{N} \]
and
\[ \frac{\sum_{i=1}^N Y_{ij}(z, s') - Y_{ij}(z, s)}{N} \]
at the individual level. This will be done using Neyman's repeated sample approach and by regression analysis

 \[ Y_{ij} = \alpha_2 + \sum_{k \in \mathcal{Z}\setminus \{control\}} \beta_{k} \cdot \mathbbm{1}\{Z_j = k\} + \sum_{l \in \mathcal{S}\setminus \{none\}}\delta_l \cdot \mathbbm{1}\{S_{ij} = l\} + \sum_{k\in \mathcal{Z}\setminus\{control\}, l \in \mathcal{S}} \gamma_{kl}\cdot \mathbbm{1}\{Z_j = k\} \times \mathbbm{1}\{S_{ij} = l\} + \nu_{ij} \]

## Heterogeneity

* Cluster level pre-treatment characteristics
* Beliefs and attitudes
* Content of informational messages
* Distance to point-of-treatment (this should be included in the stratification section)
* Rainfall (?)

## Temporal Dynamics

## Willingness to Pay for Incentives

## Social Information

## Sample Selection

Talk about stratified sampling of phone and non-phone owners within clusters.

## Inter-cluster Spillover

# References
