---
title: |
    | The Role of Social Signaling in Community Deworming 
    | Evidence from a Field Experiment in Kenya^[This study was funded by the Children's Investment Fund Foundation and implemented by Evidence Action. We thank Guillaume Kroll, the study's project manager; Arthur Baker, our research assistant; Doris Njomo and Rosemary Musuva for their qualitative research input during the study's pilot; Carol Nekesa and her implementation and data collection team; Ned Augenblick, Edward Miguel and Stefano DellaVigna for their research advice; and Karen Levy and Grace Hollister for their advice and support. We received Internal Review Board clearance from the Kenya Medical Research Institute and the University of California Berkeley. The study pre-analysis plan was registered with the American Economic Association registry (<https://www.socialscienceregistry.org/trials/1643/history/17782>).]
subtitle: "Internal Working Paper -- Do Not Cite or Distribute"
date: "November 2018"
author:
- Anne Karing^[University of California Berkeley, `akaring@econ.berkeley.edu`.]
- Karim Naguib^[Evidence Action, `karim.naguib@evidenceaction.org`.]
output: 
  pdf_document:
    number_sections: yes
header-includes:
   - \usepackage{mathtools}
   - \usepackage{pxfonts}
   - \usepackage{bbm}
   - \usepackage{setspace}
   - \usepackage{booktabs}
   - \usepackage[table]{xcolor}
   - \usepackage{pdflscape}
   - \usepackage{threeparttable}
   - \usepackage{todonotes}
   - \usepackage{tikz}
abstract: "Can social image concerns motivate adults to internalize important health externalities? We conduct a large-scale field experiment to estimate the effect of social signaling on adults' decision to take up deworming treatment. Working with the Kenyan Government, we implement a new community deworming program that provides free treatment to over 200,000 adults and explicitly emphasizes the public good aspect of deworming. We introduce two different signals - a colorful bracelet and ink applied to the thumb - for adults to broadcast their participation, and exogenously vary the distance that adults have to travel for treatment. We find that social signals: (i) reduce information asymmetries in deworming decisions; (ii) significantly increase take-up and outperform a material incentive; and (iii) have a greater impact at larger travel distances, providing evidence that signaling returns increase as fewer people deworm. We find no evidence for signals to affect deworming decisions through social learning or increased salience." 

bibliography: /home/karim/Documents/library.bib
---

\doublespacing
\newtheorem{assumption}{Assumption}

\usetikzlibrary{arrows,positioning,shapes.geometric,fit}

\tikzset{
  >=stealth',
  county/.style={
    ellipse,
    draw=black, very thick,
    fill=white,
    text width=8.5em,
    minimum height=2em,
    text centered},
  punkt/.style={
    rectangle,
    rounded corners,
    draw=black, very thick,
    fill=white,
    text width=8.5em,
    minimum height=2em,
    text centered},
  expgroup/.style 2 args={
    rectangle,
    rounded corners, 
    draw=black!50, dashed,
    fill=black!10,
    fit=(#1) (#2)},
  pil/.style={
    <-,
    thick,
    shorten <=2pt,
    shorten >=2pt},
  greypil/.style={
    <-,
    draw=black, dotted,
    shorten <=2pt,
    shorten >=2pt},
  triangle/.style={
    regular polygon,
    draw=black, very thick,
    fill=white,
    regular polygon sides=3
  },
  popcircle/.style={
    circle,
    fill=white,
    draw=black, very thick
  }
}


```{r workingpaper-setup, include=FALSE}
library(plyr)
library(magrittr)
library(lubridate)
library(forcats)
library(broom)
library(ggrepel)
library(ggmap)
library(gridExtra)
library(rgeos)
library(sp)
library(knitr)
library(modelr)
library(car)
library(rstan)
library(tidyverse)

library(econometr)

source("takeup_rct_assign_clusters.R")
source("analysis_util.R")

knitr::read_chunk("analysis_util.R", labels = "analysis-util")

read_chunk(purl("takeup_analysis2.Rmd")) 
# read_chunk(purl("takeup_bayesian_analysis.Rmd")) 

options(dplyr.show_progress = FALSE, digits = 4)

opts_chunk$set(echo = FALSE, warning = FALSE, 
               cache = TRUE, cache.path = "takeup_workingpaper-cache/", 
               fig.path = "takeup_workingpaper-fig/", fig.align = "center")

```

```{r proj4}
wgs.84 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
kenya.proj4 <- "+proj=utm +zone=36 +south +ellps=clrk80 +units=m +no_defs"
```

```{r model-versions}
static_fit_version <- "param_static_2962857" # Name matched and SMS
dyn_fit_version <- "param_dynamic_2330870" # Strata level only with cluster RE
```

```{r ggplot-theme, cache=FALSE}
theme_set(theme_minimal() +
            theme(legend.position = "bottom"))
```

```{r load-experiment-design-data}
rct.schools.data <- read_rds(file.path("data", "takeup_rct_schools.rds"))
rct.cluster.selection <- read_rds(file.path("data", "rct_cluster_selection_2.0.rds"))
cluster.strat.data <- read_rds(file.path("data", "takeup_processed_cluster_strat.rds"))

load(file.path("data", "takeup_village_pot_dist.RData"))
```

```{r load-analysis-data}
load(file.path("data", "analysis.RData"))
```

# Introduction

Externalities play an important role in many health behaviors. Prominent examples are deworming, smoking, open defecation and vaccination. Individuals frequently undervalue the social costs and benefits of their actions and underinvest in public goods like deworming. There is an extensive theoretical literature on the role of social signaling and image concerns. Recent field experiments have found that social image concerns affect important behaviors, such as consumption, the decision to vote, and student effort (DellaVigna et al. 2017; Bursztyn et al. 2017; Bursztyn and Jensen 2015). However, empirical evidence from field settings in developing countries is limited. Developing countries are a particularly important context, since formal enforcement mechanisms^[E.g. the US and Germany have laws that require children to be immunized to attend daycare.] are often missing to produce efficient contributions to public goods and signaling incentives could be an inexpensive substitute^[There is an extensive literature showing the effectiveness of material/financial incentives in encouraging positive health behaviors in developing countries. However, governments often raise concerns about the scaleability and financial sustainability of these incentives.]. We choose community deworming, as an important empirical setting, to manipulate social signaling concerns. Deworming is a public good for which most of its benefits accrue through reduced disease transmission. Worm infections in adults present a large disease burden as they lead to continuous reinfections among children. In this paper, we ask two questions: Can social signals increase adults' willingness to take up deworming treatment? How is the value of signaling affected by the cost of the action? 

Working with the Kenyan Government, we implement a large-scale field experiment in Western Kenya covering three different counties. We introduce a new community deworming program where community health volunteers provide free deworming treatment to over 100,000 adults (instead of children) at central locations (instead of through a door-to-door campaign) over a period of twelve days. Adults are informed about the private and community-wide health benefits of deworming prior to the start of deworming. Our main experimental manipulations are to alter the observability of take-up decisions and to vary the cost of deworming. We introduce two social signals in the form of colorful bracelets and ink applied to people's thumb. To control for the consumption value of bracelets, we introduce a private material incentive in the form of a one-page calendar. In a separate willingness-to-pay experiment we show that adults strictly prefer the calendar over the bracelets. 144 treatment locations and their surrounding communities are randomized into the ink, bracelet and calendar treatment or a control group where no incentive is offered. The cluster randomization identifies the combined effect of social signaling, salience and social learning. To separately identify the extent to which deworming decisions are driven by a desire to signal, we offer free text messages to a small random subset of adults in each of the study communities. The text messages remind individuals of the availability of deworming and provide information about the share of adults that have come for deworming treatment in their community. To exogenously vary the cost of deworming, we randomly assign communities to close (less than 1.25 kilometers) or far (between 1.25-2.5 kilometers) walking distance to treatment locations. The distance randomization allows us to exogenously shift the level of take-up in communities. 

We monitor the deworming decision of 38,000 adults, avoiding to rely on data from self-reported take-up. We estimate a static and dynamic (hierarchical Bayesian) model to create the necessary counterfactuals to identify the partial effect of social signaling on deworming take-up decisions. In the static model, we show that bracelets as signals meaningfully increase individuals' probability to deworm, and that these effects persist when also providing text message reminders and information about others' take-up decision. Bracelets increase deworming take-up by 8.4 percentage points, a 24 percent increase in take-up to the control group. We find no detectable effect for the ink incentive, which we attribute to the lower visibility of ink and its strong association with voting in Kenya. Our experiment took place shortly before the presidential elections, which might have created suspicion among adults. The calendar incentive increased take-up only marginally by 2.7 percentage points. Its effect on take-up is one-third of that of bracelets, despite adults preferring the calendar as consumption item. The dynamic model allows us to explicitly model potential salience and social learning effects that were introduced as individuals could observe other people's deworming decision. Same as in the static model with the text message treatment, we find no evidence that visibility in actions, through ink or bracelets, affects take-up decisions through reminders or social learning. Our distance treatment shows that adults are highly sensitive to increases in cost. An increase in the mean walking distance by 1 kilometer leads to a large drop in take-up from 44$\%$ to 28$\%$ in the control group. We find that both signals have a larger impact on take-up at far distances, which is consistent with the theoretical prediction that signaling returns increase as signals become more informative. The signaling effect of bracelets almost fully compensates for the increase in deworming cost. This result suggests that optimal incentive design should take into account the increase in reputational returns at larger distances, when deciding on optimal treatment locations. A zero walking distance may not be socially optimal. 

In addition to the administrative data on take-up, we collect detailed survey data on adults' knowledge, first and second-order beliefs and social norm concerns to shed led on the mechanism underlying social signaling. At baseline we find that adults know about the private health benefits of deworming and consider deworming as ``the right thing to do'' (similar to vaccinating one's child), despite having a limited understanding of externalities. We further find evidence for signals to reduce perceived information asymmetries, as adults are more likely to think that others have information about their take-up decision.  

The remainder of this paper is organized as follows. In Section \ref{the-intervention}, we describe the setting of the intervention. In Section \ref{experiment-design}, we describe the experimental design to identify social signaling concerns. Section \ref{descriptive-statistics}, provides descriptive statistics from the experiment. In Section \ref{empirical-models}, we present the empirical Bayesian model. In Section \ref{results} we show the results. Section \ref{conclusion} concludes.

# The Intervention

Working with the Government of Kenya we offered free deworming treatment to adults at central locations in 3 counties in Western Kenya: Busia, Kakamega and Siaya County. Central locations were selected to be easily locatable by targeted community members by being in close proximity of a primary school and either located in their own villages or in neighboring villages.^[We initially selected treatment locations to be adjacent to primary schools because of their prominence and ubiquity. However, the Ministry of Education did not permit us to operate in such close proximity to schools to prevent cheating in exams. We therefore used alternative locations (such as churches) that were not too far from the originally selected schools.] Community Health Volunteers (CHVs) led the implementation of the community deworming program and provided the treatment at central locations and informed households about the upcoming deworming treatment.^[CHVs were trained in drug administration by their supervising Community Health Extension Workers (CHEWs), who also handled the distribution and recovery of deworming drugs. The research team worked closely with national and local health officials but was not involved in the medical aspects of deworming.] One week prior to the start of the deworming treatment CHVs conducted a door-to-door sensitization, informing households about the community-wide benefits of deworming and risk of infection through others, when and where free treatment will be available and if applicable what type of incentive will be given to adults coming for treatment. CHVs further worked with community stakeholders to spread the information through established channels (e.g. community meetings/barazas) and placed posters in prominent locations. 

<!-- TODO Add CHV script in Appendix -->
<!-- TODO Add Poster Example in Appendix -->

Deworming treatment was subsequently offered at central locations, from 8am to 5pm, for a period of 12 days. For logistical reasons, we split the intervention into two waves: from October 3 to 14 we offered deworming treatment to communities in Busia and Siaya County, and from October 24 to November 4 we offered treatment in Kakamega County. Depending on the treatment location a community was assigned to, adults who came for deworming were dewormed or were dewormed and also the first deworming wave was from October 3 to 14 in Busia and Siaya County, and the second wave was from October 24 to November 4 in Kakamega County. Depending on the a cluster's assigned treatment, individuals who came for deworming were either only dewormed or were dewormed and either 

(i) received a mark on their thumb using indelible ink as is normally done during voting, 
(ii) given a simple one page wall calendar, with a design unrelated to deworming, as a gift, or
(iii) given a silicon green bracelet as a gift.

All adults who came to a given treatment location were provided with deworming treatment (and if applicable were given an incentive) irrespective of where they lived.^[We did not provide treatment only to adults that came from communities that were targeted by the informational campaign or require individuals to receive treatment in their home cluster.] After treatment, individuals were asked to provide their name, gender, age and community location.^[This data is commonly collected during health campaigns for administrative purposes. For the purpose of this evaluation, recording deworming treatment take-up directly at the point of treatment instead of relying on self-reported measures greatly helped us improve the accuracy of our data.]   

Prior to the start of deworming treatment, we also recruited a random sample of individuals to receive informational text messages about the community deworming program (see the [Experiment Design](#experiment-design) section). The text messages reminded adults of the availability of deworming treatment and their treatment location, and provided information about deworming treatment take-up in their communities. Messages were sent the day before the deworming program started and after that every other day (on the second, fourth, sixth, eight and tenth deworming day). 


# Experiment Design

We randomly selected 158 clusters in the three study counties, of which 144 were used in the study.^[We only intended to use 150 clusters, and only included eight extra clusters as fallback clusters. For various practical reasons, implementation was only possible in 144 clusters.] We relied on the high geographic density of primary schools in the study counties to select both treatment locations and targeted communities.^[Geographic coordinates for primary schools were retrieved from the Kenya Open Data Portal (<http://www.opendata.go.ke/>).] Each cluster is defined as a treatment location and targeted community pair. We used the location of primary schools as proxies to (i) identify acceptable locations to set up our treatment locations and (ii) to find villages to target with our informational campaign and data collection.

To select our clusters from the pool of a total of 1,451 primary schools in our study area, we used an acceptance-rejection method whereby we randomly picked schools, checked their acceptability based on their overlap with already selected clusters, and if accepted added them to our selected sample. This process was repeated until we had selected the requisite number of clusters. If no acceptable schools remained before completion, the whole process was restarted. Each cluster, centered on its treatment location, had a 2.5 kilometer radius _catchment circle_ and 3-4 kilometer radius _buffer circle_. A cluster was considered acceptable if its _buffer circle_ did not leave any of the already selected clusters' non-overlapping _catchment circles_ smaller than an a pre-specified size.

<!-- TODO ^[Buffer sizes were randomly assigned -  EXPLAIN MORE?]  -->
<!-- TODO ^[EXPLAIN OR DELETE: with about one primary school nonoverlapped. ALSO ADD pre-specified size = X] -->

```{r all-clusters-map, message=FALSE, fig.width=6, fig.height=6, fig.cap="Map of Initial Cluster Selection. Black crosses (+) indicate the selected treatment locations, while the grey regions indicate the nonoverlapped catchment circles from which we selected village(s) to target."}
ggplot.clusters(rct.cluster.selection, include.cluster.ids = FALSE, source = "stamen", maptype = "toner") 
```

After all clusters were selected, we randomly assigned^[Randomization was stratified within counties to increase statistical power.] each cluster to be either a "close" or "far" cluster: whether its targeted community would be less or more than 1.25 kilometers away from the treatment location, respectively. We then selected for each cluster, from its non-overlapping _catchment circle_ and according to its assigned distance treatment, a primary school as an anchor for us to locate its targeted community.^[For further details on the cluster selection algorithm refer to the study's pre-analysis plan [@Karing2016].] Figure \ref{fig:dist-to-pot} shows the distribution of targeted communities' distances (in meters) to their own treatment locations and to the closest other treatment locations.

<!-- TODO I struggle to interpret: first graph shows almost zero overlap, second graph shows that for 25% of communities closest other treatment loc was 2.5km or less away. DELETED 2nd graph (for now). -->
<!-- TODO Add further detail about what learn from graph e.g. (?) cluster selection algorithm was successful in that for almost all clusters own treatment location was closer than closest other treatment location -->

```{r dist-to-pot, echo=FALSE, fig.width=6, fig.height=3, fig.cap="Distance to Treatment Locations"}
verify.vill.pot.dist %>% 
  select(dist.to.own.pot, closest.other) %>% 
  gather(dist.type, dist) %>% {
  ggplot(.) +
    geom_histogram(aes(dist, fill = dist.type), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = alpha("black", 0.5), position = "dodge") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 5)) +
    scale_fill_discrete("Distance", labels = c("To Closest Other Treatment Location", "To Assigned Treatment Location")) 
}
```

```{r dist-to-other-pot, fig.width=6, fig.height=2, fig.cap="Distance to Closest Other Point-of-Treatment", eval=FALSE}
verify.vill.pot.dist %>% { 
  ggplot(.) +
    geom_histogram(aes(closest.other), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = "black") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 2)) 
} 
```

```{r marginal-dist-to-other-pot, fig.height=2.5, fig.width=6, fig.cap="Marginal Distance to Closest Other Treatment Location. Dashed vertical lines indicate the 10th, 25th, 50th, 75th, and 90th percentiles of the distribution.", eval=FALSE}
verify.vill.pot.dist %>% 
  mutate(marginal.dist = closest.other - dist.to.own.pot,
         dist.to.own.pot.cat = cut(dist.to.own.pot, 
                                   breaks = c(0,  2500/2, 10000),
                                   labels = c("Close", "Far"))) %>% {
                                     ggplot(.) +
                        geom_histogram(aes(marginal.dist), alpha = 0.5, color = alpha("black", 0.5), binwidth = 500, boundary = 0, position = "dodge") +
                        scale_y_continuous("Number of Clusters", breaks = seq(0, 50, 2)) +
                        scale_x_continuous("", breaks = seq(-1000, 10000, 1000)) +
                        geom_vline(xintercept = quantile(.$marginal.dist, probs = c(0.1, 0.25, .5, 0.75, 0.9)), linetype = "dashed", alpha = 0.5)
                                   }
```

Clusters were then randomly assigned, stratified over counties and distance treatment, to the different incentive treatments: 

(i) Control: no incentive
(ii) Indelible ink: a public signal of treatment
(iii) Calendar: a private low-value gift 
(iv) Bracelet: a low-value gift and public signal of treatment 

To finalize the cluster selection process, we surveyed the treatment location and target community anchor schools. For the treatment locations we confirmed that treatment would be feasible there and identified alternative treatment locations, close to the selected schools, as potential backups. For the anchor schools, we identified all the communities near them and randomly selected one community to target.^[In some cases because the initial village was too small, we added a second village] We then conducted a census of all adults (18 years or older of age) residing in the selected communities: surveyors visited each household, captured their geographic coordinates, and collected basic information of each household member that would allow us to follow-up with individuals if they were sampled in later stages and to stratify over relevant characteristics (e.g., phone ownership).

Using the census lists we randomly sampled individuals to be surveyed at base- and/or endline and to be part of the text messaging intervention. The sampling of individuals who did not receive any text messages was stratified over phone ownership. For all sampled individuals, we monitored the decision to take-up deworming treatment and obtained their consent to having observed their take-up status and using their data.^[Except for individuals who were surveyed at baseline, the majority were not informed about their participation in the study and therefore needed to be re-consented.] 

\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\begin{figure}
  \centering
  \begin{tikzpicture}[node distance=1cm, auto,]
    
    \node[county] (kakamega) at (-5, -2) {Kakamega County};
    \node[county] (siaya) at (0, -2) {Siaya County};
    \node[county] (busia) at (5, -2) {Busia County};
    
    \node[punkt] (close) at (-2, -4) {Close}
      edge[greypil] (kakamega)
      edge[greypil] (busia)
      edge[pil] (siaya);
    \node[punkt] (far) at (2, -4) {Far}
      edge[greypil] (kakamega)
      edge[greypil] (busia)
      edge[pil] (siaya);
      
    \node[punkt] (control) at (-6, -6) {Control}
      edge[pil] (close)
      edge[pil] (far);
    \node[punkt] (ink) at (-2, -6) {Ink}
      edge[pil] (close)
      edge[pil] (far);
    \node[punkt] (calendar) at (2, -6) {Calendar}
      edge[pil] (close)
      edge[pil] (far);
    \node[punkt] (bracelet) at (6, -6) {Bracelet}
      edge[pil] (close)
      edge[pil] (far);
      
    \node[triangle, below=of ink] (village1) {}
      edge[pil] (ink);
    \node[triangle, left=0.25cm of village1] (village2) {}
      edge[pil] (ink);
    \node[triangle, right=0.75cm of village1] (village3) {}
      edge[pil] (ink);
      
    \node[triangle, below=of control] (village1-control) {}
      edge[pil] (control);
    \node[triangle, left=0.25cm of village1-control] (village2-control) {}
      edge[pil] (control);
    \node[triangle, right=0.75cm of village1-control] (village3-control) {}
      edge[pil] (control);
      
    \node[triangle, below=of calendar] (village1-calendar) {}
      edge[pil] (calendar);
    \node[triangle, left=0.25cm of village1-calendar] (village2-calendar) {}
      edge[pil] (calendar);
    \node[triangle, right=0.75cm of village1-calendar] (village3-calendar) {}
      edge[pil] (calendar);
      
    \node[triangle, below=of bracelet] (village1-bracelet) {}
      edge[pil] (bracelet);
    \node[triangle, left=0.25cm of village1-bracelet] (village2-bracelet) {}
      edge[pil] (bracelet);
    \node[triangle, right=0.75cm of village1-bracelet] (village3-bracelet) {}
      edge[pil] (bracelet);
      
     \path (village1) -- node[auto=false,font=\bf]{\ldots} (village3); 
     \path (village1-control) -- node[auto=false,font=\bf]{\ldots} (village3-control); 
     \path (village1-calendar) -- node[auto=false,font=\bf]{\ldots} (village3-calendar); 
     \path (village1-bracelet) -- node[auto=false,font=\bf]{\ldots} (village3-bracelet); 
     
    \node[popcircle, below=1.5cm of village2-control, label={below:{\footnotesize\bf{SMS Control}}}] (non-phone-sms-control-control) {}
      edge[pil] (village1-control);
    \node[popcircle, below=3.5cm of village3-control, label={[text depth=-2ex,text width=4cm,rotate=-35]right:{\footnotesize\bf{SMS Control}}}] (phone-sms-control-control-1) {}
      edge[pil] (village1-control);
    \node[popcircle, right=0.25cm of phone-sms-control-control-1, label={[text depth=-2ex,text width=4cm,rotate=-35]right:{\footnotesize\bf{Reminders Only}}}] (phone-sms-control-control-2) {}
      edge[pil] (village1-control);
    \node[popcircle, right=0.25cm of phone-sms-control-control-2, label={[text depth=-2ex,text width=4cm,rotate=-35]right:{\footnotesize\bf{Social Info}}}] (phone-sms-control-control-3) {}
      edge[pil] (village1-control);
     
    \node[popcircle, below=1.5cm of village2, label={below:{\footnotesize\bf{SMS Control}}}] (non-phone-sms-control) {}
      edge[pil] (village1);
    \node[popcircle, below=3.5cm of village3, label={[text depth=-2ex,text width=4cm,rotate=-35]right:{\footnotesize\bf{SMS Control}}}] (phone-sms-control-1) {}
      edge[pil] (village1);
    \node[popcircle, right=0.25cm of phone-sms-control-1, label={[text depth=-2ex,text width=4cm,rotate=-35]right:{\footnotesize\bf{Social Info}}}] (phone-sms-control-2) {}
      edge[pil] (village1);
     
    \begin{pgfonlayer}{background}
      \coordinate (strata top right) at (8, -1.1);
      \coordinate (strata bottom left) at (-8, -2.9);
      
      \node[expgroup={strata bottom left}{strata top right}, label={[yshift=0.5cm,xshift=6cm]below:{\bf Strata} (Counties)}] (stratabox) {};
      %% \node[rotate=-30, anchor=south] at (stratabox.east) {};
      
      \coordinate (villages top right) at (8, -7.1);
      \coordinate (villages bottom left) at (-8, -8.5);
      
      \node[expgroup={villages bottom left}{villages top right}, label={[yshift=0.5cm, xshift=6cm]below:{\bf Clusters} (Villages)}] (villagesbox) {};
      
      %%\node[rotate=-30, anchor=south] at (villagesbox.east) {{\bf Clusters}}; 
      
      \coordinate (non-phone top right) at (8, -9);
      \coordinate (non-phone bottom left) at (-8, -10.52);
      
      \node[expgroup={non-phone bottom left}{non-phone top right}, label={[yshift=0.5cm, xshift=6cm]below:{\bf Non Phone Owners}}] (non-phonebox) {};
      
      %%\node[rotate=-30, anchor=south] at (non-phonebox.east) {{\bf Non Phone Owners}}; 
      
      \coordinate (phone top right) at (8, -11);
      \coordinate (phone bottom left) at (-8, -13.3);
      
      \node[expgroup={phone bottom left}{phone top right}, label={[yshift=0.5cm, xshift=6cm]below:{\bf Phone Owners}}] {};
    \end{pgfonlayer}
  \end{tikzpicture}
  \caption{Experiment Design: grey boxes identity the types of population units over which treatment was assigned. The study was stratified over counties (ellipses) and clustered over villages (triangles). Boxes identify cluster (village) level treatments while circles identify individual level treatments.}
\end{figure}

<!-- TODO Strange bit since we state above that all individuals who came for treatment, were asked about their name, age, gender and community. So saying "All individuals who were in these samples were collectively put the _monitored_ group. At the treatment location, individuals who were treated were asked some quick identifying questions (name, age, etc.), and if they were found to match someone in the _monitored_ group we made a record of their treatment." does not quite make sense and makes it sound like as if we did not monitor other people's treatment status which we did though.-->

<!-- TODO Add experiment design and survey timeline diagram -->

### Baseline survey {-}

<!-- TODO should later replace intended number of people surveyed with actual avrg. number of adults surveyed-->

Before implementing the information campaign, we aimed to conduct baseline surveys with 15 individuals from unique households in each cluster.^[The actual number of individuals that were located varied for all the samples.] 
<!-- TODO ADD WHY WE DID THIS?-->
The baseline survey included questions on:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of.
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others.
c) Beliefs about one's own and others' deworming decisions in response to an MDA, and how that decision is affected by others' choices.
d) Beliefs about one's own and others' reputation if infected and treated.
e) Past experience with deworming treatment.

### Text message intervention {-}

We aimed to recruit 30 individuals per cluster in the control arm and 25 individuals per cluster in the treated arms to receive informational text messages. In the control arm, we divided the sample into two groups of 15: one group that received reminder messages only,^[The reminder messages stated "Free deworming now at [Central Location]."] and a second group that received reminders and social information about other individuals' deworming take-up.^[Peer take-up was described both as "few", "almost half", "almost everyone", etc. of your village came, and as a "$n$ in 10" proportion.] In the incentive arms, all individuals received the reminder and the social information.

The text message treatment sample was drawn from the population of phone owners, from which we also drew a comparison "control" sample, that did not receive any text messages. 

### Endline survey {-}

After deworming treatment was completed, we aimed to conduct endline surveys with the 25 individuals per cluster, who were selected from the following groups:

* From the sample of those not receiving text messages:
    - 15 individuals per cluster in the control arm
    - 20 individuals per cluster in the treated arms
* From the sample of those receiving reminder messages only:
    - 5 individuals per cluster 
* From the sample of those receiving reminder and social information messages:
    - 5 individuals per cluster 
   
Since the majority of endline survey respondents were not part of the baseline survey, some questions overlapped between the two questionnaires. The endline survey included questions on:

a) Demographics, such as ethnicity, religion, language, age, phone ownership, education, and what material the floors in their homes are made of.
b) Knowledge of STH infection, how it is spread and treated, and how individuals' infection status affects others.
c) Knowledge of the MDA intervention: location, start date, and duration of treatment; where respondent got dewormed; how did respondent learn about the MDA; and if they were contacted by a CHV or received text messages.
d) Questions testing knowledge of others' deworming choices: 
    i. Respondents were incentivized to estimate how many of their community members got dewormed.
    ii. Respondents were explicitly asked about their relationship with and their knowledge of deworming status of ten other individuals or pairs of individuals in their community.^[We randomly asked respondents about individuals or pairs of individuals, with the objective to reduce potential aversion to disclosing negative information about peers.]
    
<!-- TODO Note according to IRB WTP was part of endline survey, just a different survey part. I think we should treat it that way. -->

As part of the endline survey, we implemented a discrete choice experiment to elicit individuals' private valuation for the calendar and bracelet incentives. We conducted a willingness-to-pay survey with a sample of subjects in the control arm who were neither part of the endline survey nor were they part of the text messaging treatment. We randomly selected 24 control communities and sampled 25 individuals from each. Respondents were given the choice to receive either the calendar or the bracelet for free, revealing their preferred choice. We then offered a random cash amount for respondents to switch to the incentive that they had not chosen, which allows us to estimate the utility difference in monetary terms. 

# Descriptive Statistics 

In this section we will present descriptive statistics pertinent to implementation of the community deworming program and its outcomes. 

### Study sample {-}
Table \ref{tab:cluster-stats} shows the total number of clusters by treatment arm and county as well as the number of adults that were surveyed during the census. Across 144 cluster, we surveyed 39,301 individuals who formed the sampling frame for different surveys and text messaging intervention. 
<!-- useless sentence and should definitely move table to appendix later. useful only if we describe different sample, where this is super sample and then there is monitored, monitored consent and endline sample -->

```{r cluster-stats}
cluster.stats <- census.data %>%
  filter(!is.na(cluster.id)) %>%
  left_join(select(cluster.strat.data, cluster.id, dist.pot.group), "cluster.id") %>% 
  arrange(county) 

calc.cluster.stats <- . %>% 
  count(county, assigned.treatment) %>% 
  ungroup %>% 
  spread(assigned.treatment, n) %>% { 
    total <- select(., -county) %>% mutate_all(as.integer) %>% rowSums 
    mutate(., all = total) 
  }

clusters.stats <- cluster.stats %>% 
  distinct(cluster.id, .keep_all = TRUE) %>% 
  calc.cluster.stats %>%
  set_names(str_to_title(names(.))) 

individ.stats <- cluster.stats %>% 
  calc.cluster.stats %>% 
  set_names(str_to_title(names(.))) 
```

\begin{table}
\centering
\caption{Number of clusters and individuals in targeted communities, by county and treatment arm.}\label{tab:cluster-stats}
\begin{tabular}{l*{10}{c}}
\toprule
       & \multicolumn{5}{c}{Clusters} & \multicolumn{5}{c}{Individuals} \\ \\
County & Control & Ink & Calendar & Bracelet & All & Control & Ink & Calendar & Bracelet & All \\
\cmidrule(r){2-6} \cmidrule(r){7-11}

```{r cluster-stats-tab, results="asis"}
clusters.stats %>%
  left_join(individ.stats, "County", suffix = c(".clusters", ".individuals")) %>% 
  plyr::a_ply(1, function(row) sprintf("%s %s \\\\\n", 
                                 row$County,
                                 paste(sprintf(" & %s", prettyNum(as.integer(row[, -1]), big.mark = ",")), collapse = "")) %>% 
          cat)
  
```
\bottomrule
\end{tabular}
\end{table}

Figure \ref{fig:general-desc-stats} shows socio-economic characteristics of individuals in the census, base- and endline survey. The mean age is 35 and 40 years respectively. Over half of respondents have not completed primary education and a large share (80$\%$) live in houses with floors made of earth. Both is indicative of low-income status, yet 65$\%$ to 80$\%$ of respondents report to have a mobile phone across the different surveys. 

```{r general-desc-stats, fig.width=8, fig.height=6, warning=FALSE, fig.cap="Study population summary statistics"}
gen.stats.plot <- tribble(~ col.name,       ~ label,
        "gender",         "Gender",
        "ethnicity2",      "Ethnicity",
        "school",         "Schooling",
        "floor",          "Home floor construction",
        "have_phone",     "Own mobile phone?") %>%
  multi.know.bel.cat.plot(.census.data = census.data %>% mutate(gender = factor(gender, levels = 1:2, labels = c("Male", "Female"))),
                          preprocess.fun = . %>% mutate(response = fct_relevel(response, rev(levels(baseline.data$school)))),
                          na.rm = TRUE)

age.density.plot <- list(Census = mutate(census.data, age = age.census), 
                         Baseline = baseline.data, 
                         Endline = endline.data) %>% 
  map_df(~ select(., age), .id = "survey.type") %>% 
  mutate(survey.type = factor(survey.type, levels = c("Census", "Baseline", "Endline"))) %>% 
  ggplot(aes(survey.type, age, color = survey.type)) +
  geom_boxplot() +
  coord_flip() +
  scale_y_continuous("Age Box Plot", breaks = seq(15, 100, 5)) +
  labs(x = "") +
  theme(legend.position = "none")

grid.arrange(gen.stats.plot, age.density.plot, layout_matrix = as.matrix(c(1, 1, 1, 1, 2)))
```

<!--Gender decomposition -->

### Knowledge, beliefs and perceptions of deworming {-}

Figure \ref{fig:know-believe-categorical-responses} presents individuals' responses to base- and endline questions about worms and deworming treatment. The majority of respondents knew about deworming treatment (78$\%$). However, less than one third of adults had knowledge of the negative externalities of worm infection. Comparing reported knowledge and beliefs of baseline and endline surveyed individuals, the most significant change is in people's understanding of who is at risk of worm infections. More people are reporting after the intervention the belief that everyone is at risk of worm infection. 
<!-- TOOK OUT since people are both less likely to answer yes and no to this question, as if they were less open to answering the question after deworming took place "Surprisingly, there seems to be a decrease in the understanding that individuals can infection one another. -->

```{r know-believe-categorical-responses, warning=FALSE, fig.width=8, fig.height=10, fig.cap="Knowledge and beliefs baseline and endline survey responses."}
tribble(~ col.name,      ~ label,
        "who_worms",     "Who is at risk of worms?",
        "effect_worms",  "What are the effects of worms?",
        "spread_worms",  "Can an infected person spread worms to other?",
        "how_spread",    "How are worms spread?",
        "stop_worms",    "How to stop worms?",
        "when_treat",    "When should people get dewormed?",
        "worms_affect",  "If infected, can you affect others' health?",
        "neighbours_worms_affect", "Can neighbors or relatives worm infection affect your health?") %>% 
  multi.know.bel.cat.plot() +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

Since our study's main research questions focus on social influence in deworming decisions, we tried to elicit individuals' perceptions and beliefs of others' deworming choices. Figure \ref{fig:response-other-deworm} shows individuals reporting that their own deworming decisions would not be influenced by others' decisions, as well as having a strong _intention_ to getting dewormed.

```{r response-other-deworm, warning=FALSE, fig.width=8, fig.height=2.5, fig.cap="Reported response to others' deworming choices."}
tribble(~ col.name,      ~ label,
        "few_deworm",     "Deworm if less than half of others deworm?",
        "many_deworm",    "Deworm if more than half of others deworm?",
        "more_less",      "Would you be more likely to deworm if few/many others get dewormed?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 
```

In addition, as shown in Figure \ref{fig:baseline-deworming-beliefs}, people predicted similar deworming among peers. As we will see below, most people overestimated their own and others' deworming take-up. Finally, when individuals were asked about how others would respond to the use of indelible ink as a signal of deworming treatment, they predicted a positive effect, contrary to what we actually observed.

```{r survey-of-10-beliefs, ref.label="survey-of-10-beliefs", warning=FALSE}
```

```{r survey-of-10-beliefs-boxplot, ref.label="survey-of-10-beliefs-boxplot", warning=FALSE}
```

```{r baseline-deworming-beliefs, warning=FALSE, fig.width=8, fig.height=5, fig.cap="Baseline beliefs/predictions about others' deworming choices."}
other.predict.deworm.plot <- tribble(~ col.name,              ~ label,
                                     "dworm_proportion",      "How many people will come to get dewormed?",
                                     "ink_more_less",         "Will the ink signal increase/decrease deworming take-up?") %>% 
  multi.know.bel.cat.plot(.endline.data = NULL,
                          preprocess.fun = . %>% 
                            mutate(response = fct_relevel(response,
                                                          "Few", "Nearly Half", "Half", "More Than Half", "Many", "All", "Less", "Same", "More", "Prefer Not Say", "Don't Know"))) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  labs(title = "Peer deworming predictions")

survey.takeup.beliefs.10.boxplot <- survey.takeup.beliefs.10.boxplot + theme(legend.position = "none")
survey.takeup.beliefs.10 <- survey.takeup.beliefs.10 + theme(legend.position = "right")

grid.arrange(other.predict.deworm.plot, survey.takeup.beliefs.10, survey.takeup.beliefs.10.boxplot, 
             layout_matrix = rbind(c(1, 1, 1, 1), c(2, 2, 3, 3)))

```

To measure existing social norms surrounding deworming, we elicited individuals' attitudes towards deworming and other well-known behaviors such as wearing nice clothes to church, using latrines, and immunizing children. We presented individuals with different scenarios and asked whether these would inspire praise or stigma.

We also inquired about respondents' social perception/judgement of some of others' behaviors (some more observable than others). We wanted to compare attitudes towards deworming and other behaviors such as wearing nice clothes to church, using latrines, and immunizing children. Individuals were presented with difference scenarios and were asked whether they would inspire praise or stigma. Figure \ref{fig:praise-stigma-plot} shows that deworming is considered to be as highly praiseworthy as the use of latrines and immunization of children, and more praiseworthy than wearing nice clothes to church. In terms of stigma, failing to get dewormed is reported to be slightly less stigmatized than open defecation and not immunizing ones children, but is more negatively viewed than not wearing nice clothes to church.


```{r praise-stigma, ref.label="praise-stigma"}
```

```{r praise-stigma-plot, fig.width=8, fig.height=3, fig.cap="Reported social perception of some observable activities."}
plot(praise.stigma.plot) 
```

```{r mda-dates-dist, ref.label="mda-dates-dist"}
```

### Prior experience with deworming {-}

Figure \ref{fig:dewormed-history} presents individuals' reported experience with deworming, prior to the intervention. The majority of respondents said that children in their families had been previously dewormed, and the most common location for treatment for family members had been during the annual school-based deworming program. We also see that almost two third of adults had been previously dewormed. However, more than half of those reporting prior treatment, were treated over two years ago. Furthermore, most adults reported getting dewormed at a hospital/clinic or to have purchased medication.

```{r dewormed-history, fig.width=8, fig.height=9, fig.cap="Deworming history."}
ever.dewormed.plot <- baseline.data %>% 
  select(treated, family_treated) %>% 
  gather(key = who.treated) %>% 
  mutate(who.treated = if_else(who.treated == "treated", "Self", "Family")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>%
  ungroup %>%
  mutate(value = fct_recode(factor(value), "Don't Know" = "DK") %>% 
             fct_relabel(str_to_title) %>% 
             fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Ever been dewormed before?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

who.was.dewormed.plot <- baseline.data %>% 
  select(family_treated, who_treated) %>% 
  filter(family_treated == "yes") %>% 
  mutate(who_treated = fct_relabel(factor(who_treated), str_to_title)) %>% 
  ggplot(aes(who_treated)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "Who in family got dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

when.dewormed.plot <- baseline.data %>% 
  transmute(treated, 
            treated_when = fct_relabel(factor(treated_when), str_to_title)) %>% 
  filter(treated == "yes") %>%
  ggplot(aes(treated_when)) +
  geom_bar(aes(y = ..count../sum(..count..)), alpha = 0.5) +
  coord_flip() +
  labs(title = "When did you last get dewormed?", x = "", y = "Proportion")

where.treated.plot <- baseline.data %>% 
  select(treated, family_treated, treated_where, where_family_treated) %>% 
  gather(key = who.treated, value = value, -c(treated, family_treated)) %>% 
  mutate(who.treated = if_else(who.treated == "treated_where", "Self", "Family")) %>% 
  filter((who.treated == "Self" & treated == "yes") | (who.treated == "Family" & family_treated == "yes")) %>% 
  count(who.treated, value) %>% 
  group_by(who.treated) %>% 
  mutate(n = n/sum(n)) %>% 
  ungroup %>% 
  mutate(value = fct_recode(value, "Don't Know" = "DK") %>% 
           fct_relabel(str_to_title) %>% 
           fct_relabel(function(.label) str_replace_all(.label, "Mda", "MDA")) %>% 
           fct_reorder(n)) %>%
  ggplot(aes(value)) +
  geom_col(aes(y = n), alpha = 0.5) +
  coord_flip() +
  facet_grid(who.treated ~ .) +
  labs(title = "Where did you last get dewormed?", x = "", y = "Proportion") +
  theme(strip.text.y = element_text(angle = 0)) 

grid.arrange(ever.dewormed.plot, who.was.dewormed.plot, when.dewormed.plot, where.treated.plot, 
             layout_matrix = as.matrix(c(1, 1, 2, 3, 3, 4, 4)))
```

### Information campaign and knowledge about the community deworming program {-}

To verify that individuals were informed about the new community deworming program we asked endline survey respondents questions to test their knowledge, presented in Figure \ref{fig:know-about-mda}. Responses indicate a good knowledge of the program and its start and end dates. The majority reported learning about the deworming program from CHVs, and few said they were informed by other social contacts such as barazas, churches, family and friends. Posters did not appear to be very successful. Overall, the community deworming program's informational campaign, led by CHVs, was successful at reaching most community members.

```{r know-about-mda, warning=FALSE, fig.width=8, fig.height=6.5, fig.cap="Knowledge of RCT intervention."}
know.mda.cat.plot <- tribble(~ col.name,      ~ label,
        "know_deworm",    "Know about community-based MDA?",
        "treat_begin",    "Know when MDA starts?",
        "treat_end",      "Know when MDA ends?",
        "days_available", "Know length of MDA?",
        "find_out",       "From whom or how did you learn about the MDA?",
        "chv_visit",      "Did a CHV visit you to tell you about MDA?") %>% 
  multi.know.bel.cat.plot(.baseline.data = NULL, .census.data = NULL) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) 

mda.dates.dist.plot <- mda.dates.dist.plot + theme(legend.position = "right")

grid.arrange(know.mda.cat.plot, mda.dates.dist.plot, layout_matrix = as.matrix(c(1, 1, 1, 2, 2)))
```


### Preferences for incentives {-}

<!-- Revealed Preferences for Incentives AND STATED --> 

In order to distinguish between the private and social motivation of incentives, we asked endline respondents for their preferences for the calendar and bracelet incentives, and separately conducted a [willingness-to-pay survey](#willingness-to-pay-survey-sample) in the control arm. The identification challenge for us is to separate

a) _private valuation_, individuals like the bracelets for their consumption value, and 
<!--I think in B&T intrinsic value is used to refer to the value assigned to deworming, a calendar or bracelet item would have extrinsic value because calendar can be used for dates etc. and bracelet can be worn on wrist -- both are goods to use-->
b) _social valuation_, individuals are influenced by bracelets in their deworming decision because they want to broadcast that their deworming or because they are reminded or learn about deworming by observing others' decisions.

Figure \ref{fig:gift-plots} reports which incentive (bracelet or calendar) individuals preferred as a gift during the endline survey. Calendars are typically preferred by all except for those already dewormed. Similarly, in the willingness-to-pay survey, we find that the majority (72 $\%$) of individuals preferred calendars to bracelets. This provides evidence that individuals assign a higher private value to calendars and that by comparing deworming treatment take-up across calendar and bracelet arms we are able to isolate the social component. 
<!-- weak, needs to be rewritten but hopefully okay for CIFF, really would need model at beginning -->

```{r reported-gift-pref-deworm, ref.label="reported-gift-pref-deworm"}
```

```{r other-incentive-plot, ref.label="other-incentive-plot"}
```

```{r gift-plots, fig.height=4, fig.width=8, fig.cap="Reported calendar/bracelet preferences, split by experiment arm and respondents' deworming take-up."}
plot(reported.gift.pref.dewormed.plot)
# grid.arrange(reported.gift.pref.dewormed.plot, other.have.incentive.plot, 
#              layout_matrix = as.matrix(c(1, 1, 2, 2, 2)))
```

```{r reported-gift-pref-deworm, ref.label="reported-gift-pref-deworm"}
```


### Distance to treatment location {-} 

As described in the [Experiment Design](#experiment-design) section, communities were randomly assigned to be either located _close_ or _far_ from the treatment locations. The distance assignment is key for us to estimate individuals' response to changes in treatment (travel) cost and quantify the utility from social signaling. Due to small changes in the actual location of treatment and the dispersion of households within targeted areas, actual distances to points of treatments were distributed as shown in Figure 11. While there does appear to be some slight overlap between _close_ and _far_ clusters (i.e. non-compliance with assigned treatment), this does not affect the intention-to-treat analysis carried out in this report.

```{r act-dist, fig.width=8, fig.cap="Distribution of actual distance from targeted villages and their assigned treatment location."}
analysis.data %>%  
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% 
  ggplot(aes(dist.to.pot)) +
  geom_density(aes(color = dist.pot.group, linetype = "Household")) +
  geom_density(aes(color = dist.pot.group, linetype = "Cluster Center"),
               data = mutate(village.centers, assigned.treatment = fct_relabel(assigned.treatment, str_to_title))) +
  geom_vline(xintercept = c(1250), linetype = "dashed") +
  labs(y = "Density", 
       caption = "Cluster centers were calculated as the centroid location of all households in cluster.") +
  scale_x_continuous("Distance to Treatment Location (meters)", breaks = seq(0, 10000, 2500/4)) +
  scale_color_discrete("Cluster Distance Assignment", labels = c("Close", "Far")) +
  scale_linetype_discrete("Distance From") +
  facet_wrap(~ assigned.treatment)
```


We can see in Table \ref{tab:mean-assigned-dist} that individuals from _far_ communities had to travel more than twice the distance to treatment locations compared to individuals from _close_ communities. 
<!-- TODO Elaborate on point that "treatment cost" assignment was successful. Sadly, though least difference for bracelets... -->

```{r mean-assigned-dist, warning=FALSE}
analysis.data %>%  
  # anti_join(outlier.clusters, c("sms.treatment", "cluster.id")) %>% 
  mutate(assigned.treatment = fct_relabel(assigned.treatment, str_to_title)) %>% {
    bind_rows(group_by(., assigned.treatment, dist.pot.group) %>%
                summarize(mean.dist = mean(dist.to.pot)) %>%
                ungroup,
              group_by(., dist.pot.group) %>% 
                summarize(mean.dist = mean(dist.to.pot), assigned.treatment = "(All)") %>% 
                ungroup)
  } %>% 
  spread(dist.pot.group, mean.dist) %>% 
  mutate(mean.dist.diff = far - close) %>% 
  kable(col.names = c("Arm", "Close", "Far", "Mean Difference"), 
        caption = "Mean Distance to Treatment Location (meters)",
        format = "latex", align = "lccc", booktabs = TRUE, longtable = FALSE, format.args = list(big.mark = ",")) 
```


### Absolute deworming treatment take-up {-}

By the end of the intervention, we had recorded the deworming treatment of approximately 97,000 individuals. Figure \ref{fig:absolute-takeup} shows how much absolute take-up there was, split by assigned incentive treatment, assigned distance to treatment location, and county. While the pattern of take-up is similar to what we will find in our formal analysis, we are not making any causal interpretations based on these findings. The aim of this study is to learn about impact on the _proportion_ of take-up in targeted communities, and therefore an analysis based on absolute figures would be misleading as we do not have information of what communities all treated individuals are from.


```{r absolute-takeup, fig.height=6, fig.cap="Absolute Deworming Take-up"}
plot.aggreg.takeup <- function(.data) {
  ggplot(.data, aes(assigned.treatment)) +
    geom_bar(alpha = 0.5, color = alpha("black", 0.5)) +
    labs(x = "Treatment", y = "Number of Individuals Dewormed (x 100)", caption = "Note: range on Y axis varies between counties.") +
    facet_grid(county.randomization ~ dist.pot.group, scales = "free_y", margins = TRUE) +
    scale_y_continuous(labels = . %>% divide_by(100)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

takeup.data %>% 
  mutate_at(vars(dist.pot.group, assigned.treatment), funs(factor(.) %>% fct_relabel(str_to_title))) %>% 
  plot.aggreg.takeup 
```

# Empirical Models

## Model subscripts 

* $i$: individuals
* $j$: clusters (villages)
* $k$: strata (counties)
* $m \in \{1,\ldots,12\}$, deworming day index.

## Variables

* $Y_i \in \{0, 1\}$, is observed take-up over the whole intervention duration. $Y_{im} \in \{0, 1\}$, is observed take-up on day $m$.
* $\mathbf{Z}_i$, assigned treatment: incentive treatments, SMS treatment, distance treatment 
* $\mathbf{X}_i$, covariates: phone-ownership, and name-matching indicators. 

## Static Model

### Likelihood Model

This is the model's likelihood, the data generating process for observed outcomes:

$$
\begin{aligned}
\Pr[Y_i = 1 | \mathbf{Z}_i, \mathbf{X}_i, \theta_{j[i]}] &= g^{-1}(\eta_i | \theta_{j[i]}) \\
\eta_i &=  f(\mathbf{Z}_i, \mathbf{X}_i | \theta_{j[i]})   
\end{aligned}
$$

where 

* $g$ is a binary link function (e.g., logit or probit link functions).
* $f$ is a linear function of $\mathbf{Z}$ and $\mathbf{X}$^[I'm writing it this way so I don't have to write the whole linear model with treatment indicators, covariates and, their interactions. I can specify it separately, it would just distract from the overall model here.]. 
* $\theta_j = (\alpha_j, \beta_j)'$, where $\alpha_j$ and $\beta_j$ are the model parameters for the village-level intercept and the village-level vector of slope coefficients, respectively.

### Parameters Model

This section describe the hierarchical model for parameters. Distribution that have $\mathtt{Multi}$ prefix are multivariate distributions and distributions with $\mathtt{Half}$ prefix are restricted to have non-negative values. 

The vector of village-level parameters has the following multivariate distribution:

$$
\forall j: \theta_j \sim \mathtt{MultiStudentT}(\nu^\text{village}, \theta_{k[j]}, \Sigma_{k[j]}^\text{village})
$$
while the county-level parameters have the following distribution
$$
\forall k: \theta_k \sim \mathtt{MultiStudentT}(\nu^\text{county}, \theta^o, \Sigma^\text{county})
$$
where $\theta^o = (\alpha^o, \beta^o)$ are the hyperparameters of the linear model:
$$
\begin{aligned}
\alpha^o &\sim \mathtt{Normal}(0, 5) \\
\beta^o &\sim \mathtt{MultiNormal}(0, \mathsf{diag}(1))
\end{aligned}
$$
($\mathsf{diag}(x)$ is a matrix with the diagonal vector $x$.)

The covariance matrices for $\theta_j$ and $\theta_k$ are defined as
$$
\begin{aligned}
\forall k: \Sigma_k^\text{village} &= \mathsf{diag}(\sigma^\text{village}) \Omega_k^\text{village} \mathsf{diag}(\sigma^\text{village}) \\
\Sigma^\text{county} &= \mathsf{diag}(\sigma^\text{county}) \Omega^\text{county} \mathsf{diag}(\sigma^\text{county})
\end{aligned}
$$
where $\Omega_k^\text{village}$ and $\Omega^\text{county}$ are correlation matrices with their own prior distributions.

Other hyper parameters have the following prior distributions
$$
\begin{aligned}
\nu^\text{village} &\sim \Gamma(2, 0.1) \\
\nu^\text{county} &\sim \Gamma(2, 0.1) \\
\sigma^\text{village} &\sim \mathtt{HalfMultiNormal}(0, \mathsf{diag}(1)) \\
\sigma^\text{county} &\sim \mathtt{HalfMultiNormal}(0, \mathsf{diag}(1)) \\
\end{aligned}
$$

### Posterior Distribution of Model Parameters

Let $\theta$ be a vector of all linear model parameters at all levels and $\phi$ is a vector of all hyperparameters, and $\mathbf{Y}$ is a matrix of all observed outcomes. To conduct our inference we need to calculate the distribution
$$
p(\theta,\phi|\mathbf{Y}^\text{observed}, \mathbf{Z}^\text{observed}, \mathbf{X}) = p(\mathbf{Y}^\text{observed} | \mathbf{Z}^\text{observed}, \mathbf{X}, \theta, \phi) p(\theta | \phi) p(\phi)
$$

### Inference

After calculating the posterior distribtution of the model's parameters we want to be able to calculate, for any two treatments $z$ and $z'$, the distribution of the average treatment effect
$$
\frac{1}{N} \Sigma_i Y_i(z) - Y_i(z')
$$

Since we only observe at most one outcome of $Y_i(\cdot)$, we need to quantify the distribution of _missing_ counterfactuals:
$$
p(\mathbf{Y}^\text{missing} | \mathbf{Y}^\text{observed}, \mathbf{Z}^\text{observed}, \mathbf{Z}^\text{missing}, \mathbf{X}) = \int p(\mathbf{Y}^\text{missing} | \mathbf{Z}^\text{missing}, \mathbf{X}, \theta, \phi) \cdot p(\theta,\phi|\mathbf{Y}^\text{observed}, \mathbf{Z}^\text{observed}, \mathbf{X})\, d\theta d\phi
$$

## Dynamic Model

### Likelihood Model

The dynamic model is extends the static model to the 12 deworming days.

$$
\begin{aligned}
\Pr[Y_{im} = 1 | Y_{i,m-1} = 0, \mathbf{Z}_i, \mathbf{X}_i, \theta_{j[i]}] &= g^{-1}(\eta_{im} | \theta_{j[i]}) \\
\eta_{im} &= \log(\lambda_{k[i],m}) + f(\mathbf{Z}_i, \mathbf{X}_i | \theta^\text{static}_{j[i]}) + f_m(\mathbf{Z}_i, \mathbf{X}_i | \theta^\text{dynamic}_{k[i]}) \\
\\
\Pr[Y_{im} = 1 | Y_{i,m-1} = 1, \mathbf{Z}_i, \mathbf{X}_i, \theta_{j[i]}] &= 1 \\
\Pr[Y_{im} = 0 | Y_{i,m-1} = 1, \mathbf{Z}_i, \mathbf{X}_i, \theta_{j[i]}] &= 0
\end{aligned}
$$

The link function $g$ here is a complementary log-log^[Logit and probit work just as well.]. $\lambda_{km}$ the is the piecewise-constant proportional hazard (Just taking a log of it to add it to the other linear model terms instead of leaving outside the $\exp(\cdot)$ term in the complementary log-log). The linear function $f$ is the same as in the static model, while $f_m$ is a quadratic linear model of days $m$ interacted with $\mathbf{Z}_i$ and $\mathbf{X}_i$. In the above notation I split the static and dynamic parameters such that $\theta = (\theta^\text{static}, \theta^\text{dynamic})$.

## Willingness-to-Pay Model

Let

* $V^c_i$ and $V^b_i$ be an individual's monetary valuation of calendars and bracelets, respectively.
* $G_i \in \{0, 1\}$ indicates initial gift choice of calendar (vs bracelet). Also, let $\widetilde{G}_i \equiv 2\cdot G_i - 1 \in \{-1, 1\}$.
* $M_i \in \{0, 10, 20,\ldots, 100\}$ be the randomly assigned offer (in Ksh) to switch gifts choice (calendar instead of bracelet and v.v.)
* $W_i(m) \in \{0, 1\}$ indicates accepting $m$ Ksh to switch gift choice.

\begin{align*}
  V_i \equiv V^c_i - V^b_i &\sim \mathtt{StudentT}(\nu_v, \mu_{k[i]}, \sigma) \\
  \mu_k &\sim \mathtt{StudentT}(\nu_\mu, \mu, \tau_\mu) \\
  \mu &\sim \mathtt{StudentT}(\nu_\mu, 0, \tau_\mu) \\
  \sigma &\sim \mathtt{HalfStudentT}(\nu_\sigma, 0, \tau_\sigma)
\end{align*}

with fixed hyper parameters: $\nu_v, \nu_\mu, \nu_\sigma, \tau_\mu, \tau_\sigma$.

<!-- TODO Specify fixed hyperparameter values -->

We estimate these model parameters using the likelihood probability:

\begin{equation*}
\mathcal{L}_i = \left\{\widetilde{G}_i\cdot [F_V(\widetilde{G}_i \cdot M_i|\mu, \mu_{k[i]}, \sigma) - F_V(0|\mu, \mu_{k[i]}, \sigma)]\right\}^{W_i}\cdot\left\{ F_V(\widetilde{G}_i\cdot M_i|\mu, \mu_{k[i]}, \sigma)\right\}^{(1 - W_i)} 
\end{equation*}

# Results

## Willingness-to-Pay

The WTP experiment was implemented with a random subsample of adults in the no incentive i.e. control group after the end of the community deworming program. The adults had therefore no prior exposure to the bracelet or calendar incentive.

```{r, ref.label="wtp-stan-data"}
```

```{r, ref.label="load-wtp-fit", include=FALSE}
```

```{r, ref.label="prepare-wtp-sim-data"}
```

Table \ref{tab:wtp} shows the summary of the posterior distribution of the willingness-to-pay model. As shown, the posterior probability of preferring calendar to bracelets is high with an average of 42-53 Ksh difference in valuation. 

```{r wtp-table, results="asis"}
wtp_model_0_fit %>% 
  summary(par = c("hyper_mu_wtp_diff", "sigma_wtp_diff", "mu_wtp_diff", "hyper_prob_prefer_calendar", "prob_prefer_calendar"), 
          probs = c(0.025, 0.05, 0.5, 0.95, 0.975)) %$% 
  summary %>% 
  xtable::xtable(caption = "Posterior Estimates for Willing-to-Pay Parameters\\label{tab:wtp}",
                 align = "lrrrrrrrrrr") %>% 
  print(sanitize.colnames.function = . %>% 
          str_replace_all(c("se\\_mean" = "$SE_{Mean}$",
                            "mean" = "Mean",
                            "sd" = "SD",
                            "%" = "\\\\%",
                            "n_eff" = "$N_{eff}$",
                            "Rhat" = "$\\\\hat{R}$")),
        sanitize.rownames.function = . %>% 
          str_replace_all(c("hyper_mu_wtp_diff" = "$\\\\mu$",
                            "sigma_wtp_diff" = "$\\\\sigma$",
                            "mu_wtp_diff\\[(\\d)\\]" = "$\\\\mu_\\1$",
                            "hyper_prob_prefer_calendar" = "$\\\\Pr[V^c_i > V^b_i]$",
                            "prob_prefer_calendar\\[(\\d)\\]" = "$\\\\Pr[V^c_i > V^b_i|k = \\1]$")),
        booktabs = TRUE,
        comment = FALSE)
```

## Static Deworming Take-up Model 

```{r load-static-fit}
load(file.path("stan_analysis_data", "static_processed.RData"))
load(file.path("stan_analysis_data", str_interp("model_${static_fit_version}.RData")))
```

```{r static_level_smsctrl, fig.height=3, fig.width=8, fig.cap="Posterior distribution of deworming take-up levels (with no SMS treatment)"}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_all,
  data_preparer = . %>%
    filter(
      !name_matched,
      sms.treatment.2 == "control",
      incentive_treatment != "Bracelet Social"
      ),
  incentive_treatment_col = "incentive_treatment",
  show_observed = FALSE,
  num_obs = param_stan_data$num_obs
    ) +
  labs(y = "") 
```

```{r static_level_all, fig.height=4, fig.width=8, fig.cap="Posterior distribution of deworming take-up levels (phone owners only)"}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_phone,
  data_preparer = . %>%
    filter(
      phone_owner,
      !name_matched,
      incentive_treatment != "Bracelet Social"
      ),
  incentive_treatment_col = "incentive_treatment",
  sms_treatment_col = "sms.treatment.2",
  include_sms_treatment = TRUE,
  show_observed = FALSE,
  num_obs = param_stan_data$num_obs
    ) +
  labs(y = "", subtitle = "Phone Owners Only") +
  theme(legend.position = "top")
```


```{r static_ate_smsctrl, fig.width=8, fig.height=2.5, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (with no SMS treatment)."}
# est_deworming_takeup_ate_all_name_matched %>% # Used this check the different ATE for name_matched and monitored
est_deworming_takeup_ate_all %>%
  filter(incentive_treatment_left != "bracelet social",
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>%
  plot_ate(
    ate_summ_data = .,
      data_preparer = . %>% 
      filter(incentive_treatment_right %in% c("Control", "Calendar"),
             incentive_treatment_left != incentive_treatment_right,
             sms.treatment.2_left == "control",
             sms.treatment.2_left == sms.treatment.2_right),
    incentive_treatment_left_col = "incentive_treatment_left" 
  ) + 
  labs(y = "Treatment Effect on Take-up Probability") +
       # subtitle = "ATE(z)",
       # x = "Incentive/signal (z)") #+ facet_wrap(~ name_matched_left)
  NULL
```

```{r static_ate_all, fig.width=8, fig.height=4, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (conditional on SMS treatment)."}
# est_deworming_takeup_ate_phone_name_matched %>%
est_deworming_takeup_ate_phone %>%
  mutate(same_incentive = incentive_treatment_left == incentive_treatment_right,
         same_sms = sms.treatment.2_left == sms.treatment.2_right) %>% 
  filter(phone_owner_left, 
         incentive_treatment_left != "bracelet social",
         !same_incentive & same_sms,
         sms.treatment.2_right != "reminder.only",
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>% 
  plot_ate(
    ate_summ_data = .,
    incentive_treatment_left_col = "incentive_treatment_left",
    sms_treatment_col = "sms.treatment.2_left",
    include_sms_treatment = TRUE,
    num_obs = param_stan_data$num_obs
  ) + 
  labs(y = "", subtitle = "For phone owners only, compared to control incentive treatment,\nand conditional on SMS treatment.") + #+ facet_wrap(~ name_matched_left)
  theme(legend.position = "top")
```

```{r static_ate_combined_sms, fig.width=8, fig.cap="Posterior distribution of signal/incentive treatment + SMS treatment effects on take-up compared with the control arm take-up (with no SMS treatment)."}
est_deworming_takeup_ate_phone %>%
  mutate(same_incentive = incentive_treatment_left == incentive_treatment_right,
         same_sms = sms.treatment.2_left == sms.treatment.2_right) %>% 
  filter(phone_owner_left, 
         incentive_treatment_left != "bracelet social",
         !same_incentive | incentive_treatment_left == "control",
         sms.treatment.2_right == "control",
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>% 
  plot_ate(
    ate_summ_data = .,
    incentive_treatment_left_col = "incentive_treatment_left",
    sms_treatment_col = "sms.treatment.2_left",
    include_sms_treatment = TRUE,
    num_obs = param_stan_data$num_obs
  ) + 
  labs(y = "Treatment Effect on Take-up Probability", 
       subtitle = "For phone owners only,\ncomparing incentive treatment + SMS treatment vs incentive control + No SMS.") + #+ facet_wrap(~ name_matched_left)
  theme(legend.position = "top") +
  # scale_color_brewer("SMS Treatment", type = "qual", palette = "Set2") +
  NULL
```

### Conditional on Distance

```{r static_level_smsctrl_dist, fig.width=8, fig.height=5, fig.cap="Posterior distribution of deworming take-up levels (with no SMS treatment), split by distance."}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_dist,
  data_preparer = . %>%
    filter(
      !name_matched,
      sms.treatment.2 == "control",
      incentive_treatment != "Bracelet Social"
      ) %>% 
    mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(., str_to_title))), 
    incentive_treatment_col = "incentive_treatment", 
    show_observed = FALSE,
    num_obs = param_stan_data$num_obs
    ) +
  labs(y = "", subtitle = "Split by distance") +
  facet_wrap(~ dist.pot.group, ncol = 1) +
  theme(strip.text = element_text(size = 15, face = "bold"))
```


```{r static_level_all_dist, fig.width=8, fig.height=7, fig.cap="Posterior distribution of deworming take-up levels (phone owners only), split by distance."}
plot_takeup(
  takeup_summ_data = est_deworming_takeup_phone_dist,
  data_preparer = . %>%
    filter(
      phone_owner,
      !name_matched,
      incentive_treatment != "Bracelet Social"
      ) %>% 
    mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(., str_to_title))), 
    incentive_treatment_col = "incentive_treatment",
    sms_treatment_col = "sms.treatment.2",
    include_sms_treatment = TRUE,
    num_obs = param_stan_data$num_obs
  ) +
  labs(y = "", subtitle = "For phone owners only, split by distance.") +
  facet_wrap(~ dist.pot.group, ncol = 1) +
  theme(strip.text = element_text(size = 15, face = "bold"), legend.position = "top") 
```


```{r static_ate_smsctrl_dist, fig.width=8, fig.cap="Posterior distribution of deworming take-up levels (with no SMS treatment), split by distance."}
est_deworming_takeup_ate_dist %>% 
# est_deworming_takeup_ate_dist_name_matched %>% 
  filter(incentive_treatment_left != "bracelet social",
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>% 
  plot_ate(
    ate_summ_data = .,
    data_preparer = . %>% 
    filter(incentive_treatment_right %in% c("Control", "Calendar"),
           incentive_treatment_left != incentive_treatment_right,
           dist.pot.group_left == dist.pot.group_right,
           sms.treatment.2_left == "control",
           sms.treatment.2_left == sms.treatment.2_right) %>% 
      mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(factor(.), str_to_title))), 
    incentive_treatment_left_col = "incentive_treatment_left",
    num_obs = param_stan_data$num_obs
  ) + 
  labs(subtitle = "Split by distance to point of treatment.") +
  # facet_grid(name_matched_left ~ dist.pot.group_left)
  facet_wrap(~ dist.pot.group_left, ncol = 1) +
  theme(strip.text = element_text(size = 15, face = "bold"))
```

```{r static_ate_all_dist, fig.width=8, fig.height=7, fig.cap="Posterior distribution of signal/incentive treatment effects on take-up compared with the control arm take-up (conditional on SMS treatment), split by distance."}
est_deworming_takeup_ate_phone_dist %>% 
  mutate(same_incentive = incentive_treatment_left == incentive_treatment_right,
         same_sms = sms.treatment.2_left == sms.treatment.2_right) %>% 
  filter(phone_owner_left,
         incentive_treatment_left != "bracelet social",
         !same_incentive & same_sms,
         dist.pot.group_left == dist.pot.group_right,
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>% 
  # mutate(incentive_treatment_left = if_else(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar", 
                                            # "bracelet social",
                                            # as.character(incentive_treatment_left)) %>% 
           # incentive_treatment_factor()) %>% 
  plot_ate(
    ate_summ_data = .,
    incentive_treatment_left_col = "incentive_treatment_left",
    sms_treatment_col = "sms.treatment.2_left",
    data_preparer = . %>% 
      mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(factor(.), str_to_title))), 
    include_sms_treatment = TRUE,
    sms_treatment_right = FALSE,
    num_obs = param_stan_data$num_obs
  ) + 
  facet_wrap(~ dist.pot.group_left, ncol = 1) +
  theme(strip.text = element_text(size = 15, face = "bold"), legend.position = "top")
```

```{r static_ate_combined_sms_dist, fig.width=8, fig.height=7, fig.cap="Posterior distribution of signal/incentive treatment + SMS treatment effects on take-up compared with the control arm take-up (with no SMS treatment), split by distance."}
est_deworming_takeup_ate_phone_dist %>%
  mutate(same_incentive = incentive_treatment_left == incentive_treatment_right,
         same_sms = sms.treatment.2_left == sms.treatment.2_right) %>% 
  filter(phone_owner_left, 
         incentive_treatment_left != "bracelet social",
         !same_incentive | incentive_treatment_left == "control",
         dist.pot.group_left == dist.pot.group_right,
         sms.treatment.2_right == "control",
         !(incentive_treatment_left == "bracelet" & incentive_treatment_right == "calendar")) %>% 
  plot_ate(
    ate_summ_data = .,
    incentive_treatment_left_col = "incentive_treatment_left",
    sms_treatment_col = "sms.treatment.2_left",
    data_preparer = . %>% 
      mutate_at(vars(starts_with("dist.pot.group")), funs(fct_relabel(factor(.), str_to_title))), 
    include_sms_treatment = TRUE,
    num_obs = param_stan_data$num_obs
  ) + 
  labs(y = "Treatment Effect on Take-up Probability", 
       subtitle = "Split by distance to point of treatment.\nFor phone owners only, comparing incentive treatment + SMS treatment to the control.") + #+ facet_wrap(~ name_matched_left)
  facet_wrap(~ dist.pot.group_left, ncol = 1) +
  # scale_color_brewer("SMS Treatment", type = "qual", palette = "Set2") +
  theme(strip.text = element_text(size = 15, face = "bold"), legend.position = "top") +
  NULL
```

In Figure \ref{fig:static-model-ate-plot} we report the posterior distribution of deworming take-up levels as defined in \eqref{eqn:static-ate}. Looking at treatment effects for individuals that did not receive the SMS treatment (Figure \ref{fig:static-model-ate-plot}, indicated in red), we find the biggest treatment effects for the bracelet incentives. Controlling for their consumption value, bracelets as signals (Bracelet Social) increased deworming take-up by 4 percentage points from 21 percent in the control to 25 percent, which is equivalent to a 19% increase in take-up.

The combined consumption and signaling treatment effect of bracelets (Bracelet) is three times that of calendars, despite the higher private valuation individuals expressed for calendars in the WTP experiment. 

We find a close to zero average treatment effect for the ink incentive, with substantial heterogeneity in the impact across close (-4pp) and far communities (+1pp) as shown in Figure \ref{fig:static-model-dist-ate-plot}. The results suggest that mandatory signaling as in the case of inking peoples thumb, can dissuade marginal individuals if the private valuation of the signal is negative. 

Looking at treatment effects for individuals that also received the SMS reminder and social information treatment (Figure \ref{fig:static-model-ate-plot}, indicated in blue), we find a large increases in take-up across all incentive arms and the control group. We achieve deworming take-up levels of 48 percent in the control group up to 60 percent in the bracelet arm (Figure \ref{fig:static-model-takeup-plot}). By combining the SMS treatment with the calendar incentive, we intended to control for the consumption value of the bracelets and mimic the reminder/nudge effects as well as potential learning that could take place in the presence of observability in the bracelet treatment. The combined treatment effect of calendar plus SMS is 16 percentage points, which is almost triple the effect of the bracelet incentive (Bracelets). The SMS reminder and/or social learning treatment effects are much stronger than any potential reminder or social learning effects that are introduced in the ink or bracelet treatment. 

We find similar results for the ink versus control group comparison. Providing individuals in the control group with SMS reminders (Figure \ref{fig:static-model-ate-plot}, indicated in green), increases the probability of deworming take-up by 15 percentage points. The very similar treatment effects of SMS reminder only (15pp) and SMS reminder plus social information (13pp) for the control group suggest that the SMS treatment mainly works as a reminder. The results from the dynamic model further support this. The posterior distribution of the daily finite sample average probability of deworming take-up (Figure \ref{fig:fast-sim-daily-sms-plot}) shows that the SMS treatment leads to the largest increases in take-up on day one and two, as a result of the text message reminder that was sent the day before treatment started. The treatment effects become negligible for later days, suggesting that text messages sent on days 4, 6, 8 and 10 and the social information contained in them had no relevant effect on deworming decisions. 

Comparing the effects of the SMS treatment across incentive arms (Figure \ref{fig:static-model-ate-plot}, with the control group, social info as reference), we find increasing effects from ink (-2pp) to calendar (+4pp) to bracelets (+12). Our main interpretation is that there are complementarities between incentives and private nudges, which increase with the strength of the incentive treatment. 

The static model allowed us to control for the consumption value of the bracelet incentive, separately identifying the social treatment component of bracelets. However, due to the (unanticipated) disproportionately large effects of the SMS treatment we are unable to create a valid counterfactual to control for the reminder and/or social learning effects introduced by bracelets or ink. The identify social signaling concerns we introduce dynamics and test for the presence of reminder and learning effects. 

## Dynamic Deworming Take-up

```{r load-param-dyn-est-data, cache=FALSE}
load(file.path("stan_analysis_data", "dynamic_processed.RData"))
load(file.path("stan_analysis_data", str_interp("model_${dyn_fit_version}.RData")))
```


```{r param-dyn-daily-takeup-levels-all, fig.width=8, fig.height=4}
est_deworming_day_all %>% 
  mutate(full_observation = incentive_treatment_static == incentive_treatment_dynamic) %>% 
  filter(full_observation,
         incentive_treatment_static != "bracelet social",
         sms.treatment.2_static == sms.treatment.2_dynamic,
         sms.treatment.2_static == "control") %>% 
  plot_dyn_takeup_daily(control_observation = FALSE) +
  coord_cartesian(ylim = c(0, 0.12)) +
  theme(legend.position = "bottom")
```

```{r param-dyn-daily-takeup-levels-with-sms, fig.width=7, fig.height=4}
est_deworming_day_all %>% 
  mutate(full_observation = incentive_treatment_static == incentive_treatment_dynamic) %>% 
  filter(full_observation,
         incentive_treatment_static != "bracelet social",
         sms.treatment.2_static == sms.treatment.2_dynamic) %>% 
  # filter(full_observation | incentive_treatment_dynamic == "control") %>% 
  plot_dyn_takeup_daily(control_observation = FALSE, include_sms_treatment = TRUE) +
  coord_cartesian(ylim = c(0, 0.21)) +
  facet_wrap(~ incentive_treatment_static, nrow = 1) +
  theme(legend.position = "bottom", axis.text.x = element_text(size = 5))
```


```{r param-dyn-daily-takeup-levels-dist, fig.width=7, fig.height=4}
est_deworming_day_dist %>% 
  mutate(full_observation = incentive_treatment_static == incentive_treatment_dynamic) %>% 
  filter(full_observation,
         incentive_treatment_static != "bracelet social",
         incentive_treatment_static == incentive_treatment_dynamic,
         sms.treatment.2_static == sms.treatment.2_dynamic,
         sms.treatment.2_static == "control",
         dist.pot.group_static == dist.pot.group_dynamic) %>% 
  mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
  plot_dyn_takeup_daily() +
  facet_wrap(~ dist.pot.group_static, nrow = 1, scales = "free_y") +
  # scale_color_brewer("Incentive/Signal Treatment", type = "div", palette = "Spectral") +
  coord_cartesian(ylim = c(0, 0.13)) +
  theme(legend.position = "bottom")
```

```{r param-dyn-daily-takeup-levels-dist-with-sms, fig.width=8, fig.height=5}
est_deworming_day_dist %>% 
  mutate(full_observation = incentive_treatment_static == incentive_treatment_dynamic) %>% 
  filter(full_observation,
         incentive_treatment_static != "bracelet social",
         incentive_treatment_static == incentive_treatment_dynamic,
         sms.treatment.2_static == sms.treatment.2_dynamic,
         dist.pot.group_static == dist.pot.group_dynamic) %>% 
  mutate_at(vars(starts_with("dist.pot.group_static")), funs(fct_relabel(., str_to_title))) %>% 
  plot_dyn_takeup_daily(control_observation = FALSE, include_sms_treatment = TRUE) +
  # scale_color_brewer("SMS Treatment", type = "qual", palette = "Set2") +
  labs(subtitle = "Split by distance to point of treatment. For phone owners only.") + #+ facet_wrap(~ name_matched_left)
  # scale_color_brewer("SMS Treatment", type = "div", palette = "RdBu") +
  coord_cartesian(ylim = c(0, 0.24)) +
  facet_grid(dist.pot.group_static ~ incentive_treatment_static) +
  theme(legend.position = "bottom")
```

# Conclusion

This paper provides field experimental evidence on the effects of making actions observable in the context of deworming. Working with the Kenyan Government, we introduced a new community deworming program where adults were offered free deworming treatment at central locations. We show that social incentives can lead to meaningful increases in deworming take-up and outperform material incentives. Our experiment also identifies social signaling concerns, overcoming a main identification challenge when introducing visibility in actions in a dynamic setting. We also provide evidence of the powerful nature of private nudges. The SMS treatment had the unintended consequence of being most effective in increasing deworming take-up. We believe that this research can be extended in several directions. First, it will be important to test whether social incentives can have similar effects on take-up in future rounds of community deworming. Once community deworming is no longer novel and the signals are repeatedly implemented, will treatment effects disappear or could they increase as signals could contribute to forming stronger norms around community deworming. Second, we believe that understanding the underlying mechanism of social signaling in deworming will be key to apply social signaling to other public good domains and health behaviors. Future research should investigate the social costs and sanctions or reputational benefits that people gain from signaling. Finally, given the large effects of private text message nudges it will be important to understand if the effects are dependent on the initial in-person sensitization or the in-person recruitment that was part of this experiment, or if we could send simple text message reminders to all households in Kenya and thereby increase deworming take-up.

# References

<div id="refs"></div>
