---
title: "The Role of Social Signaling in Community Mass Deworming"
subtitle: "Evidence from a Field Experiment in Kenya"
date: "November 2016"
author:
- Anne Karing^[University of California Berkeley]
- Karim Naguib^[Evidence Action]
output: 
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
header-includes:
   - \usepackage{pxfonts}
   - \usepackage{bbm}
abstract: "This document describes the analysis plan for a randomized control trial (RCT) assessing the effectiveness of social incentives on adult deworming. Working with the Kenyan Government, we implemented a new Community Deworming Program that offered free deworming treatment to adults and explicitly emphasized the public good aspect of deworming. We distributed two types of social incentives in the form of colorful bracelets and ink that adults received upon coming for deworming. The bracelets and ink made the decision to deworm or abstain from treatment observable and allowed adults to signal to others that they contributed to protecting their community from worms. We further introduced a calendar as private incentive that is comparable in its consumption value to the bracelet but cannot easily be observed by others. Communities were randomized into being eligible for the ink, calendar or bracelet or receive no incentive when coming for deworming. In a second stage, we offered free text messages to a random subset of adults living in these communities, reminding them of the availability of free deworming treatment and providing information about deworming treatment take-up in their community. This pre-analysis plan outlines the regression specifications, outcome variables, and covariates that will be considered in this analysis." 
---

```{r setup, include=FALSE}
library(magrittr)
library(plyr)
library(dplyr)
library(tibble)
library(tidyr)
library(lubridate)
library(purrr)
library(readr)
library(haven)
library(broom)
library(ggplot2)
library(ggmap)
library(stringr)
library(rgeos)

source("../util.R")
source("takeup_rct_assign_clusters.R")

knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, cache.path = "takeup_pap-cache/", fig.path = "takeup_pap-fig/", fig.align = "center")

wgs.84 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
kenya.proj4 <- "+proj=utm +zone=36 +south +ellps=clrk80 +units=m +no_defs"
```

```{r load-data, include=FALSE}
rct.schools.data <- read_rds("data/takeup_rct_schools.rds")
rct.cluster.selection <- read_rds("data/rct_cluster_selection_2.0.rds")

load("data/takeup_village_pot_dist.RData")
```


# Introduction

Over the last decade there has been important progress in the treatment of neglected tropical diseases (NTDs), as a result of unprecedented attention by governments, funders, and the private sector. The enduring prevalence of Soil Transmitted Helminths (STHs), however, still constitutes a massive development burden for both children and adults in many developing countries, including Kenya. Recent efforts to reduce contamination rates in the country have focused on deworming school-aged children, but the remaining reservoir of worms among the adult population fosters reinfection. Epidemiologists have recently postulated that it may be scientifically feasible to reach a transmission breakpoint for STHs^[Anderson, Roy, T Deirdre Hollingsworth, James Truscott, and Simon Brooker. 2012. Optimisation of Mass Chemotherapy to Control Soil-Transmitted Helminth Infection. Lancet 379 (9813). Elsevier Ltd: 289-90.].Preventing transmission and eliminating STHs using mass drug administration (MDA) covering the entire population, including children and adults, might be a viable strategy to eliminate worms moving forward. 

This study explores cost-effective ways to achieve high deworming take-up among adults by offering free deworming treatment at central locations and social incentives. The evaluation of the incentivized community deworming program relates three separate strands of the literature: compliance with mass drug administration (MDA), incentives and volunatry good contributions. 

Different to previous MDA, this study is focused on deworming treatment at a central location, not through door-to-door visits. Kremer and Glennerster^[Glennerster, R., & Kremer, M. (2011). Small changes, big results: behavioral economics at work in poor countries. Boston Review: A Political and Literary Forum.] observe that for preventive and non-acute care such as deworming, insecticide-treated bednet use and water chlorination there is a dramatic drop in demand at non-zero prices. Since a large number of people have such an abrupt cutoff at the same point, they conclude that they are not likely motivated by a simple cost-benefit analysis, but instead have a strong present bias; future benefits are heavily discounted compared to immediate benefits. One approach that has been widely tested and shown to be successful, is to provide a small reward when coming for treatment to offset any inconvenience costs individuals might face, as well as to address present bias. Kremer and Glennerster^[ibid.] review a wide number of studies on the use for incentives to increase education and health service take-up. They find strong evidence in favor of incentives compared to education only interventions.

One possibility is to incentivize compliance with MDA by focusing the program's message on social returns, emphasizing the benefit of taking treatment to reduce reinfection of community members, especially school-aged children. The Community Deworming Program could therefore be viewed as a voluntary collective action game, where an individual's treatment compliance decision can be modeled as the decision to contribute to a pool shared by all community members. One approach to increase contribution in such a setting is to allow for signaling, thus introducing social approval/disapproval as a reward/punishment^[Bénabou, Roland, and Jean Tirole. 2006. "Incentives and Prosocial Behavior." American Economic Review 96 (5): 1652-78.] ^[Bénabou, Roland, and Jean Tirole. 2011. "Laws and norms." No. w17579. National Bureau of Economic Research.].We are testing how social signaling can be leveraged to increase demand for deworming treatment among adults, by introducing two signals in the form of colourful ink and bracelets. Both allow individuals to show to others that they have taken deworming treatment. 

This pre-analysis plan outlines our strategy to test the theory of social signaling through a randomized field experiment in the context of deworming decisions. The remainder of this document is organized as follows. Section II provides .... Section III..... Finally, Sections IV and V outline the main empirical specifications that will be used in our analysis......

# Intervention

Working with the Government of Kenya we offered free deworming treatment to adults in 3 counties (Busia, Kakamega, Siaya) in Western Kenya. Community Health Volunteers (CHVs) provided the treatment at central locations and sensitized households about the upcoming deworming treatment. CHVs were identified as ideal agents to sensitize communities and give out deworming drugs, both because of their experience in providing health services to communities and because of their familiarity and trusted relationship with community members, allowing them to credibly convey new information (e.g. about the externality aspect of deworming) and address concerns (e.g. that deworming drugs might sterilize women). CHVs informed all study communities one week prior to the start of the deworming treatment about the social benefits of deworming, when and where free deworming treatment will be available and if applicable what type of incentive will be given to adults when coming for treatment. Deworming treatment was subsequently offered at central locations for a period of 12 days. 

We identified 150 central locations in the 3 selected counties. Central locations and their catchment areas were randomly assigned, in equal numbers, into one of four intervention arms: 
1) CHVs mark adults' fingers with ink; 
2) CHVs give adults a green wrist bracelet; 
3) CHVs give adults a one-page calendar for 2017; 
4) Only deworming treatment is provided and no incentive. 

We mapped communities that fall within a 2.5km catchment radius of the central location and randomly selected one community per catchment area. We conducted a census of all adults in those 150 communities and randomly selected 15 individuals in each control arm community to receive reminder text messages, and 15 (for control arm) or 25 (for ink/bracelet/calendar arms) individuals to receive reminder text messages that also contain information about deworming take-up in their community. Adults that signed up for the free text message service received a text message on the day before deworming starts, on the 2nd, 4th, 6th, 8th and 10th day of deworming treatment. The text message service is free and individuals could unsubscribe at any time at no cost. The reminder messages contained the following content: 

> Free deworming now at [Central Location]. Reply ___ to _____ stop texts. All texts are free.

The reminder and social information about deworming take-up messages contained the following content:

> Free deworming now at [Central Location]. [No/few/almost half/half/more than half/almost all/all] of your village came, that is _X_ in 10 adults. Reply ___ to _____ stop texts. All texts are free. 

To verify that adults were reading the text messages, we offered an airtime reward of 50 Kenyan Shillings (50 US Cents) to a random subset of subscribers conditional on texting back and confirming the receipt of the text message.^[We only implemented the reward scheme during the second wave of deworming treatment. The reason being, we only decided to add the treatment shortly before we started deworming in wave one communities and had to wait for ethical approval for this added component before we could implement it.] The following reward text was sent to adults on day 2 and 6 of deworming treatment: 

> Thank you for signing up for this text message from Evidence Action. To receive your 50Ksh airtime reward, message ___ to _____. The text is free. 

We sent a reminder text messsage to adults that had not taken up the reward two days after the original reward text was sent: 

> Thank you for signing up for text messages from Evidence Action. Don't forget to reclaim your 50Ksh airtime. Message ___ to _____ to receive the reward. The text is free.

The reminder messages were sent on day 4 (for reward messages sent on day 2) and on day 8 (for reward messages sent on day 6). 

We split deworming treatment into two waves: wave one of deworming was implemented from October 3rd to 14th in Busia and Siaya counties and wave two was implemented from October 24th to November 4th in Kakamega county. 

Sample reward text: wave two (78 clusters), among people that were successfully reached on day 0 when sent out reminder message - eligible sample. randomization: for each of the 76 retained clusters and for each SMS treatment type we randomly picked 2 people (i.e. for bracelet/ink/calendar chose total of 2 people from social info SMS group to receive reward messsage; for control chose 2 people from reminder SMS and 2 people from social info SMS groups) and then randomly assigned half of sample to day 2 and half to day 6.

Note: confirm cluster no across waves. 

# Research Questions

Our main research question is: Can social signaling incentivize adults to take up deworming treatment? The experiment contains the following 9 treatments arms:

|                             | Control  | Ink | Bracelet | Calendar |
|-----------------------------|:--------:|:---:|:--------:|:--------:|
| No SMS                      | 1        | 4   | 6        | 8        |
| Reminder SMS                | 2        | --- | ---      | ---      |
| Reminder  + Social Info SMS | 3        | 5   | 7        | 9        |


Add:

0) Incentive vs. no incentive treatment: the effect of social or private incentives on deworming take-up behavior. 

Note: as you are diving sample into text message treatment and no text message treatment we need to check (a) for balance i.e. are the two samples similar on observables? and (b) for differences in take-up behavior, comparing none phone owners and phone owners (those that were part of the SMS control)

1) Reminder and social information text message treatment vs. no text messages for control individuals: a random subsample of phone owners within each control (no incentive) cluster is randomized into receiving no text message (1 in above table), receiving a reminder text message about the availability of deworming treatment (2) or receiving a reminder text message that also provided information about other community members deworming treatment take-up. Comparing (1) vs. (2) will allow us to identify the effect reminders have on the probability of deworming treatment take-up. Comparing (1) vs. (3) we estimate the effect that reminders plus information about other people's deworming choice has on individuals' deworming take-up. By differencing the effects of (1 vs. 3 ~ reminder + social info effect) and (1 vs. 3 ~ reminder effect only) we identify the effect social learning has on deworming take-up behavior. The text message treatment (CROSS CUT?) across control clusters allows us to identify whether reminder and/or social learning is relevant in the context of deworming take-up. CHANGE TO (3) - (2).

2) Social information text message treatment vs. no text messages for Ink / Bracelet individuals: a random subsample of phone owners within each ink and bracelet cluster is randomized into receiving no text message (4 and 6 in above table) or receiving a reminder text message that also provides information about other community members deworming treatment take-up. Comparing (4) vs. (5) and (6) vs. (7) we identify the additional reminder and social learning effect of text messages given visibility of deworming take-up choices through ink and bracelets. These treatment show how "satiated" individuals are in terms being reminded and social learning through visibile signals. If we find no significant effect in take-up behavior for these treatments, reminder and social learning are either not relevant or the ink and bracelets have already reminded people or facilitated social learning. To know which is true we look at the control group comparison in 1): if we find no significant effect for text messages within the control group, ink or bracelets had no reminder or social learning effect; if we find a significant effect for text messages within the control group, ink or bracelets had a reminder or social learning effect such that the marginal reminder/social learning effect of text messages is insignificant. 

3) No incentive vs. ink for text message treatment individuals: comparing individuals that received reminder plus social information text messages across clusters where no incentive was given when coming for deworming treatment (3 in above table) vs. clusters where individuals had their thumb marked with ink when coming for deworming treatment (5), we identify the effect of social signaling on individuals' decision to deworm. A comparison only within text message recipients allows to control for the potential reminder effect (when seeing other people with ink on their thumb, people might be reminded of the availability of deworming treatment) and social learning effect (when seeing other people with ink on their thumb, people might update their beliefs of how many people in their community take up deworming and therefore its importance or value) ink has on people's deworming choice. 
If reminder and social learning effects turn out to be insignificant in 1) we can pool individuals from groups (8) and (9) and compare them to individuals from (6) and (7). Question: could also compare (6) vs. (9) i.e. only applying text treatment for control?

4) Calendar incentive vs. bracelet for text message treatment individuals: comparing individuals that received reminder plus social information text messages across clusters where a calendar incentive was given for deworming (9 in above table) vs. clusters were individuals received a bracelet (7), we identify the effect of social signaling on individuals' decision to deworm. Same as for the control-ink comparison, comparing text message recipients only allows us to control for the potential reminder effect (when seeing other people with a bracelet, people might be reminded of the availability of deworming treatment) and social learning effect (when seeing other people with a bracelet, people might update their beliefs about deworming take-up in their community and therefore its importance or value) bracelets have on people's deworming choice. By comparing the bracelet treatment to the calendar treatment we control for the consumption value of the bracelet and any normative effect a material incentive could have on people's deworming choices. 
If reminder and social learning effects turn out to be insignificant in 1) we can pool individuals from groups (1), (2) and (3) and compare them to individuals from (4) and (5). Question: could also compare (4) vs. (3) i.e. only applying text treatment for control?

Note: we chose to test two different social signaling treatments, ink and bracelets, in this experiment. The experiment is meant to generate cost-effective solutions to increasing deworming take-up. The cost of ink is close to zero and ink has no consumption value i.e. we eliminate that confound, but ink is potentially less visible, is not as lasting as signal and might cause mistrust as it is traditionally used for voting. Bracelets on the other hand have the advantage of being very visible when worn on people's wrist and is not used as signal in other contexts, but is more expensive and might privately be valued as incentive. 

5) Estimate value of social signaling: parameters to estimate, structural modeling. WHAT PARAMETERS? Benabou & Tirole. Mean of utility distribution. Distance to price out social signaling. 

6) Testing of auxiliary assumptions:
    a) private value of bracelets vs. calendar: equivalence between two incentives. 
    b) social knowledge: individuals should have more accurate knowledge about other individuals' deworming take-up in ink and bracelet arms, given the visibility in actions that both signals create. 
    c) retention of bracelets and ink:
    d) beliefs: aggregate take-up at community level: 
    e) take up of SMS treatment: i) capture through responses to SMS reward treatment and ii) variables text_content, text_content_other, receive_text, number_text to verify through self-reported data. 
    
        did people read SMS? lower bound is SMS reward (subtreatment) We believe that the reward treatment is imperfect in the sense that some people might read the tezt 
    f) knowledge about externalities (potentially base- and endline)




Missing experimental variation --> assumptions --> which one? can you test it?



Specification (in order Karim):
i) comparison of control vs. ink, control vs. bracelet, control vs. calendar ~ effect of incentives. 
ii) conditional on same information treatment (SMS) varying incentive
iii) conditional on same incentive vary SMS treatment 


heterogeneity

Our main research question is: Can social signaling incentivize adults to take up deworming treatment?

# Experiment Design

## Sampling and Identification Strategy

This study will adopt a cluster randomized experiment to make causal inferences addressing our research questions. We selected subcounties in three counties in western Kenya where soil transmitted helminths are endemic: Busia, Siaya and Kakamega. We then identified 158 clusters (communities) dispersed across the selected region. After various surveys identifying clusters where implementation would be infeasible, the study was reduced to 144 clusters. In each cluster, we conducted a census of all households and eligible adults (18 years or older). 

All communities in the experiment will be provided with 

* Deworming treatment at a point-of-treatment 
* An outreach campaign providing information on the location and duration of treatment, as well as framing the public good aspect of deworming.

We then randomly assigned treatment over cluster, stratified over counties and distance to the point-of-treatment.

From each cluster the following samples were selected:

* A baseline sample randomly selected from the entire cluster population
* A sample of individuals to monitor the treatment of during the intervention
    - Text messaged individuals picked from the subpopulation of phone owners
        + Deworming reminders
        + Information on peer deworming
    - A stratified sample of phone and non-phone owners:
        + Phone owners are used as controls for the text messaging treatment
        + Non-phone owners selected to allow us to estimate impact of incentive treatment over the whole population 

    We split this sample into two groups 
      * Endline survey respondents (stratified between text message recipients and non-recipients)
      * Data use reconsent only individuals


## Clustered Design

The experiment will be carried out in 18 subcounties in western Kenya, randomized at the cluster level. A _cluster_ is composed of 

(i) a centralized _point-of-treatment (PoT)_ at an easily identifiable location (e.g. near a ~~primary school~~ church/mosque), and
(ii) a _targeted village_ where we will conduct an outreach campaign^[Other communities will not be denied treatment, but our analysis will be focused on targeted villages.].

## Experimental Manipulation

In the experiment there will be two levels of randomized treatment assignment.

1. At the cluster level, there will be four groups:
    (i) a control group
    (ii) a private incentive group: wall calendars provided as gifts to treatment compliers
    (iii) a low private value, low visibility social incentive group: indelible ink mark on treatment compliers' hands
    (iv) a high private value, high visibility social incentive group: colorful silicon bracelets will be provided as gifts to treatment compliers 
2. At the individual level, there will be three groups:
    (i) the control group, composed of a stratified sample of
        a. phone owners
        b. non-phone owners
    (ii) the text message reminder group: participants will receive regular messages on where and when treatment will be available
    (iii) the text message and peer take-up information group: participants will receive regular messages on where and when treatment will be available, as well as the proportion of treatment take-up among others in their village.

## Cluster Selection Algorithm

The selection of clusters (PoT and targeted villages) relied on geospatial data of primary schools in the targeted subcounties. While schools did not play a direct role in the study's implementation, they were used as proxies for the location of communities.

Below is the main body of the selection algorithm:

1. Let $\mathcal{C}$ be the set of all potential clusters, defined as 2.5 kilometer radius circle centered on a primary school in the study region. In this study the size of this set is $\#\mathcal{C} = 1,451$.
2. Let $\mathcal{R} := \emptyset$ be the set of clusters selected for the experiment
3. While $\mathcal{C} \neq \emptyset$:
    a) Randomly pick $i \in \mathcal{C}$
    b) Set $\mathcal{C} := \mathcal{C}\setminus\{i\}$
    c) If $(ClusterSize(i, \mathcal{R}) < ThresholdClusterSize) \lor (\exists j \in \mathcal{R}, ClusterSize(j, \mathcal{R} \cup \{i\}) < ThresholdClusterSize)$: 
        i. Repeat Loop
        
          Else:
          
        i. Set $\mathcal{R} := \mathcal{R} \bigcup \{i\}$
4. If $\#\mathcal{R} < NumRctClusters$: Goto 1

$ClusterSize(m, \mathcal{M})$ is a function that returns the size of cluster $m$, removing any overlaps with the clusters in $\mathcal{M}$. We defined the size of a cluster to be the number of primary schools available in the non-overlapped 2.5 km circle around the cluster center (as a proxy of the available communities to target). We set the cluster size threshold to be 1 primary school^[To be exact we defined the threshold to be 60% of a 1 km radius circle around a school.].  

While we use a 2.5 km circle to define the boundary of the area we will target communities within for treatment, when considering overlaps we assume points-of-treatment would have larger catchment areas, thus providing buffers between clusters. In order to fit the study's geographic area we randomly split the PoT to have 3 and 4 km catchment areas. Thus a targeted village would always be at least 0.5 km closer to its own assigned point-of-treatment than any other cluster's.

This first step of cluster selection yielded 158 clusters. Figure \ref{fig:all-clusters-map} shows the geographic location of all clusters. The center of each cluster (the point-of-treatment) is represented by a cross, and the grey regions are the catchment areas of each cluster not within the buffers we placed between clusters. Targeted villages were chosen within these catchment areas.

```{r all-clusters-map, fig.width=8, fig.height=8, fig.cap="Map of Initial Cluster Selection"}
ggplot.clusters(rct.cluster.selection, include.cluster.ids = FALSE, source = "stamen", maptype = "toner")
```

While the cluster point-of-treatments and targeted villages were initially selected as describd above, their exact locations varied slightly before the intervention started. Figures \ref{fig:dist-to-pot}, and \ref{fig:marginal-dist-to-other-pot} show the actual distribution of (i) the distance between targeted villages and their home points-of-treatment, (ii) the distance between targeted villages and their the closest other point-of-treatment, and (iii) the difference between (i) and (ii).

```{r dist-to-pot, fig.width=6, fig.height=4, fig.cap="Distance to Points-of-Treatment"}
verify.vill.pot.dist %>% 
  select(dist.to.own.pot, closest.other) %>% 
  gather(dist.type, dist) %>% {
  ggplot(.) +
    geom_histogram(aes(dist, fill = dist.type), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = "black", position = "dodge") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 2)) +
    scale_fill_discrete("Distance", labels = c("To Closest Other Point-of-Treatment", "To Home Point-of-Treatment")) +
    theme(legend.position = "top")
}
```

```{r dist-to-other-pot, fig.width=6, fig.height=4, fig.cap="Distance to Closest Other Point-of-Treatment", eval=FALSE}
verify.vill.pot.dist %>% { 
  ggplot(.) +
    geom_histogram(aes(closest.other), binwidth = 2500/4, boundary = 0, alpha = 0.5, color = "black") + 
    scale_x_continuous("", breaks = seq(0, 10000, 2500/4)) + 
    scale_y_continuous("Number of Clusters", breaks = seq(0, 100, 2)) 
} 
```

```{r marginal-dist-to-other-pot, fig.cap="Marginal Distance to Closest Other Point-of-Treatment"}
verify.vill.pot.dist %>% 
  mutate(marginal.dist = closest.other - dist.to.own.pot,
         dist.to.own.pot.cat = cut(dist.to.own.pot, 
                                   breaks = c(0,  2500/2, 10000),
                                   labels = c("Close", "Far"))) %>% {
  ggplot(.) +
    geom_histogram(aes(marginal.dist), alpha = 0.5, color = "black", binwidth = 500, boundary = 0, position = "dodge") +
    scale_y_continuous("Number of Clusters", breaks = seq(0, 50, 2)) +
    scale_x_continuous("", breaks = seq(-1000, 10000, 1000)) +
     geom_vline(xintercept = quantile(.$marginal.dist, probs = c(0.25, .5, 0.75)), 
                color = "red", linetype = "dashed")
}
```

## Village and Point-of-Treatment Selection

Villages were randomly selected across clusters to give us an equal proportion of _close_ and _far_ village to point-of-treatment distances. Distances were categorized as _close_ if less than 1250 meters and _far_ otherwise. This split is half the upper range of the distance we observed people were generally willing to travel for deworming treatment. As explained above, these distances varied in response to implementation contraints, so after some clusters had to be dropped from the study, we ended up with approximately 46% of targeted villages being _far_ from their point-of-treatment.

This random assignment of each cluster to the _close_ or _far_ group is considered orthogonal to any targeted village characteristics, since each village could have been assigned to either group with equal probability. In other words, we are exogenously varying the distance individuals in a targeted village would have to travel for treatment.

## Treatment Assignment Mechanism

We used a stratified treatment assignment mechanism, whereby we stratified by (i) county and (ii) targeted village to point-of-treatment distance. Thus we had six strata within which we randomly assigned with equal probability one of four incentive treatments (control, indelible voting ink, calendars, and bracelets). For strata not divisible by four, we randomly assign, without replacement, one of the four treatments to the $(\text{stratum size} \mathbin{\%} 4)$ remaining clusters (randomly picked)^[http://blogs.worldbank.org/impactevaluations/tools-of-the-trade-doing-stratified-randomization-with-uneven-numbers-in-some-strata].

## Power Calculation

Registry

# Data Collection and Sample Selection

## Pre-Intervention

### Census

A census of all households in _targeted villages_ will be conducted before the treatment intervention. It will be used to randomly select households for surveying and further individual level interventions, as well as to monitor treatment take-up. Information on all adults, 15 years of age or older:

a) Name
b) Gender
c) Age
d) Household head name
e) Last two digits of phone number
f) GPS coordinates of each house

### Baseline Household Survey

## Mid-Intervention

### Treatment Take-up Monitoring

### SMS Airtime Reward

## Post-Intervention

### Endline Household Survey

### Social Knowledge

## Data Quality

### Backchecks

### Geographic and Time Monitoring

# Analysis

## Framework

Below is the primary counterfactual framework we will use:

* $i$ indexes individuals and $j$ indexes clusters
* $Z_j \in \mathcal{Z} = \{control, ink, calendar, bracelet\}$ is the cluster level treatment
* $M_{ij} \in \mathcal{M} = \{none, reminders, socialinfo\}$ is the individual level text message treatment
* $Y_{ij}(z, m) \in \{0, 1\}$ is an individual deworming outcome in response to treatment $z$ and $m$.
* $Y_j(z)$ is cluster $j$'s absolute number of treatment seekers in response to treatment $z$.
* $X_{ij}$ individual and cluster level pre-treatment characteristics. All analysis below will also be done controling for covariates. 

Inference will be conducted using cluster robust variance estimators as well as using block bootstrapping.

## Cluster Level Treatment Specifications

The first specifications comparing the finite sample impact of various treatment arms and text message treatment are
 \[ \frac{\sum_{j=1}^J Y_j(z') - Y_j(z)}{J}, \]
 and
\[ \frac{\sum_{i=1}^N Y_{ij}(z', none) - Y_{ij}(z, none)}{N} \]
 at the cluster level. 
 
 We will estimate these models using Neyman's repeated sampling approach or by regression analysis
 \[ Y_j = \alpha_1 + \beta_1 \cdot Z_j + \varepsilon_{j} \]
 and
 \[ Y_{ij} = \alpha_2 + \sum_{k \in \mathcal{Z}\setminus \{control\}} \beta_{k} \cdot \mathbbm{1}\{Z_j = k\} + \nu_{ij} \]

[Include stratification] 
    
## Cross-cut with Reminders and Informational Messages

To assess the impact reminder and social information text messages we will estimate the finite sample impact
\[ \frac{\sum_{i=1}^N Y_{ij}(z', m) - Y_{ij}(z, m)}{N} \]
and
\[ \frac{\sum_{i=1}^N Y_{ij}(z, m') - Y_{ij}(z, m)}{N} \]
at the individual level. This will be done using Neyman's repeated sample approach and by regression analysis

$$
Y_{ij} = \alpha_2 + \sum_{k \in \mathcal{Z}\setminus \{control\}} \beta_{k} \cdot \mathbbm{1}\{Z_j = k\} + \sum_{m \in \mathcal{M}\setminus \{none\}}\delta_m \cdot \mathbbm{1}\{M_{ij} = m\} + \sum_{k\in \mathcal{Z}\setminus\{control\}, m \in \mathcal{M}} \gamma_{km}\cdot \mathbbm{1}\{Z_j = k\} \times \mathbbm{1}\{M_{ij} = m\} + \nu_{ij} 
$$

## Heterogeneity

* Cluster level pre-treatment characteristics
* Beliefs and attitudes
* Content of informational messages
* Distance to point-of-treatment (this should be included in the stratification section)
* Rainfall (?)

## Temporal Dynamics

## Willingness to Pay for Incentives

## Social Information

## Sample Selection

## Inter-cluster Spillover

## Structural Model

We modify our causal framework by introducing the following latent variables:

* $V^*_{ij}(z)$, represents the private utility of deworming when $Z_j = z$
* $S^*_{ij}(z)$, represents the social influence (in utility terms) of treatment $z$ on deworming. This influence could be social learning, reputational returns from social signaling or simply due to a reminder effect. At this point we do not distinguish between these various mechanisms.
    
We further modify the deworming counterfactual function to be $Y_{ij}(V^*_{ij}(z), S^*_{ij}(z))$. This is equivalent to the previous counterfactual function such that $Y_{ij}(V^*_{ij}(z), S^*_{ij}(z)) \equiv Y_{ij}(z, m = none) \equiv Y_{ij}(z)$. We will consider the impact of the text messaging treatment, $M_{ij}$, later.

The decision to deworm is determined by 
$$ 
Y_{ij}(V^*_{ij}(z), S^*_{ij}(z)) = \mathbbm{1}\{V^*_{ij}(z) + S^*_{ij}(z) > 0\}. 
$$

We further parameterize the distribution of these latent variables to be

$$ 
\begin{pmatrix} V^*_{ij}(control) \\ V^*_{ij}(calendar) \\ V^*_{ij}(bracelet) \\ V^*_{ij}(ink) \end{pmatrix} \sim \mathcal{N} \left( \begin{matrix} \mu_0 \\ \mu_c \\ \mu_b \\ \mu_k \end{matrix},
\begin{matrix} 
  \sigma^2_0 & 0 & 0 & 0 \\
  0          & \sigma^2_c & 0 & 0 \\
  0          & 0 & \sigma^2_b & 0 \\
  0          & 0 & 0 & \sigma^2_k
\end{matrix} \right) 
$$

### Calendar/Bracelet Preference Survey
   
During the endline survey, respondents were asked to choose between a calendar or bracelet as a gift for their participation. We will use this to identify the distribution of preference over these two incentives.

First, we define their choice to be 
$$
H_{ij} = \mathbbm{1}\{D^*_{ij} > 0\},
$$ 

where
$$
D^*_{ij} = V^*_{ij}(calendar) - V^*_{ij}(bracelet).
$$

We parameterize the distribution of $D^*_{ij}$ to be
$$ 
D^*_{ij} \sim \mathcal{N}(\mu_d, \sigma^2_d), 
$$
such that $\mu_d = \mu_c - \mu_b$ and $\sigma^2 = \sigma^2_c + \sigma^2_b$. Without lost of generality we define $\sigma^2_d = 1$. This allows us to estimate the posterior distribution of $\mu_d$

\begin{equation} f(\mu_d|\mathbf{H}) \label{eqn:choice_posterior} \end{equation}

### Estimating the Social Impact of Bracelets

We want to estimate two causal effects of the bracelets treatment (as a social incentive) by comparing  it to the calendar (private incentive) treatment.

1. The social impact in the bracelet treatment arm, $Z_j = bracelet$
\begin{equation}
\frac{\sum_i^N Y_{ij}(V^*_{ij}(bracelet), S^*_{ij}(bracelet)) - Y_{ij}(V^*_{ij}(bracelet), S^*_{ij}(calendar)) }{N} \label{eqn:social_in_b}
\end{equation}

2. The social impact in the calendar treatment arm, $Z_j = calendar$
\begin{equation}
\frac{\sum_i^N Y_{ij}(V^*_{ij}(calendar), S^*_{ij}(bracelet)) - Y_{ij}(V^*_{ij}(calendar), S^*_{ij}(calendar)) }{N} \label{eqn:social_in_c}
\end{equation}

The challenge in estimating these effects is the need to impute unobservable deworming outcomes, where the treatment assignments to $V^*_{ij}(z)$ and $S^*_{ij}(z')$ are different. Thus, aside from having to impute the missing values
$$ 
Y^{mis}_{ij} = \begin{cases} 
  Y_{ij}(calendar) & \text{if } Z_{j} \ne calendar \\ 
  Y_{ij}(bracelet) & \text{if } Z_{j} \ne bracelet
\end{cases} 
$$
which we can do using the posterior distribution of $Y_{ij}(calendar)$ and $Y_{ij}(bracelet)$, but also outcomes that are not in any of the experiment's potential outcomes. However, we can use the posterior distribution of $D^*_{ij}$ to impute these outcomes.
$$ 
\begin{aligned}
Y_{ij}^{mis,bc} = Y_{ij}(V^*_{ij}(bracelet), S^*_{ij}(calendar)) &= \mathbbm{1}\{V^*_{ij}(bracelet) + S^*_{ij}(calendar) > 0\} \\ 
&= \mathbbm{1}\{V^*_{ij}(calendar) + S^*_{ij}(calendar) + D^*_{ij}> 0\}
\end{aligned}
$$
and
$$ 
\begin{aligned}
Y_{ij}^{mis,cb} = Y_{ij}(V^*_{ij}(calendar), S^*_{ij}(bracelet)) &= \mathbbm{1}\{V^*_{ij}(calendar) + S^*_{ij}(bracelet) > 0\} \\
&= \mathbbm{1}\{V^*_{ij}(bracelet) + S^*_{ij}(bracelet) - D^*_{ij} > 0\}
\end{aligned}
$$

Therefore, the posterior distribution we need in order to estimate \eqref{eqn:social_in_b} and \eqref{eqn:social_in_c} are
$$
f(\mathbf{Y}^{mis}, \mathbf{Y}^{mis,bc}|\mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z}) = \int_{\theta, \mu_d} f(\mathbf{Y}^{mis}, \mathbf{Y}^{mis,bc}, \theta, \mu_d|\mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z})\cdot f(\theta, \mu_d| \mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z})\, \mathrm{d}\theta\mathrm{d}\mu_d
$$
and 
$$
f(\mathbf{Y}^{mis}, \mathbf{Y}^{mis,cb}|\mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z}) = \int_{\theta, \mu_d} f(\mathbf{Y}^{mis}, \mathbf{Y}^{mis,cb}, \theta, \mu_d|\mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z})\cdot f(\theta, \mu_d| \mathbf{Y}^{obs}, \mathbf{H}, \mathbf{Z})\, \mathrm{d}\theta\mathrm{d}\mu_d
$$
respectively. Where $\theta = (\mu_{c,total}, \mu_{b,total}, \sigma^2_{c,total}, \sigma^2_{b,total})$ and 
$$
\begin{aligned}
V^*_{ij}(calendar) + S^*_{ij}(calendar) \sim \mathcal{N}(\mu_{c,total}, \sigma^2_{c,total}) \\
V^*_{ij}(bracelet) + S^*_{ij}(bracelet) \sim \mathcal{N}(\mu_{b,total}, \sigma^2_{b,total})
\end{aligned}
$$

# References
