---
title: "TakeUp Bayesian Analysis Notebook"
author:
- Anne Karing^[University of California Berkeley]
- Karim Naguib^[Evidence Action]
output:
  html_notebook:
    fig_align: "center"
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 5
header-includes:
   - \usepackage{bbm}
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup, include=FALSE}
library(magrittr)
library(purrr)
library(plyr)
library(dplyr)
library(multidplyr)
library(tibble)
library(tidyr)
library(lubridate)
library(forcats)
library(readr)
library(haven)
library(broom)
library(ggplot2)
library(ggrepel)
library(ggmap)
library(stringr)
library(knitr)
library(modelr)
library(rstan)

library(econometr)

source("takeup_rct_assign_clusters.R")
source("analysis_util.R")

knitr::read_chunk("analysis_util.R", labels = "analysis-util")

options(dplyr.show_progress = FALSE, digits = 4, mc.cores = max(1, parallel::detectCores()))
rstan_options(auto_write = TRUE)
```

```{r load-data, include=FALSE}
load(file.path("data", "analysis.RData"))
```

# Priors

Just some plots to visualize what some prior distributions look like. Not very exciting.

```{r name-match-priors}
name_match_false_pos_alpha <- 1
name_match_false_pos_beta <- 15

ggplot(tibble(x = c(0, 1)), aes(x)) + 
  stat_function(fun = . %>% dbeta(shape1 = name_match_false_pos_alpha, shape2 = name_match_false_pos_beta)) + 
  labs(x = "Probability of False Positive", y = "Density", title = "Prior Distribution for the Name Matching Model") +
  scale_x_continuous(breaks = seq(0, 1, 0.1))
```

```{r scale-prior-plots}
ggplot(tibble(x = c(0, 20)), aes(x)) + 
  stat_function(aes(color = "Cauchy"), fun = . %>% dcauchy(0, 2.5)) + 
  stat_function(aes(color = "Student t(2)"), fun = . %>% dt(2)) + 
  stat_function(aes(color = "Student t(4)"), fun = . %>% dt(4)) + 
  stat_function(aes(color = "Student t(7)"), fun = . %>% dt(7)) + 
  stat_function(aes(color = "N(0, 5)"), fun = . %>% dnorm(0, 5)) + 
  scale_x_continuous(breaks = seq(0, 50, 1))
```

# Willingness-to-Pay

Skip for now.

```{r wtp-sim-run, eval=FALSE}
wtp_model_0 <- stan_model(file = "wtp_model.stan", model_name = "wtp_model_0")
wtp_model_0_fit <- sampling(wtp_model_0, data = stan_data, chains = 4, iter = 2000, sample_file = file.path("stanfit", "wtp_model.csv")) 
```

```{r, eval=FALSE}
print(wtp_model_0_fit, pars = c("sim_gift_choice", "sim_wtp_response"), include = FALSE)
```

## Model Checking

```{r, eval=FALSE}
wtp_model_0_fit %>% 
  extract(pars = "sim_gift_choice") %$% 
  adply(sim_gift_choice, 1, function(iter) tibble(prop_calendar = mean(iter))) %>% 
  ggplot() +
  geom_density(aes(x = prop_calendar)) +
  geom_vline(xintercept = mean(stan_data$gift_choice)) +
  coord_cartesian(xlim = c(-1, 1))

wtp_model_0_fit %>% 
  extract(pars = "sim_wtp_response") %$% 
  adply(sim_wtp_response, 1, function(iter) tibble(prop_switch = mean(iter))) %>% 
  ggplot() +
  geom_density(aes(x = prop_switch)) +
  geom_vline(xintercept = mean(stan_data$wtp_response)) +
  coord_cartesian(xlim = c(-1, 1))
```

# Private/Social Value Parameterized Model

* Incentives/signals are split into
    - Private incentives: $Z^p_j \in \{\text{control, calendar, bracelet}\}$
    - Social incentives: $Z^s_j \in \{\text{control, ink, bracelet}\}$
* Assigned distance to treatment location: $D_j \in \{\text{close, far}\}$
* SMS treatment: $S_i \in \{\text{control, reminders-only, social-info}\}$ 
* Baseline survey indicator: $B_i = \{0, 1\}$.
* Phone ownership subgroup: $H_i = \{\0, 1\}$.
* Deworming outcome: $Y_i(z^p, z^s, d, s, b)$, in response to randomly assigned incentives, distance, SMS treatment and baseline surveying.

```{r param-ate}
param_sms_control_ate <- tribble(
  ~ private_value_left, ~ social_value_left, ~ private_value_right, ~ social_value_right,
  "control",            "ink",               "control",             "control",
  "calendar",           "control",           "control",             "control",
  "bracelet",           "bracelet",          "control",             "control",
  "bracelet",           "bracelet",          "calendar",            "control",
  
  "control",           "bracelet",           "control",            "control" 
) %>%
  bind_rows("close" = ., "far" = ., .id = "dist.pot.group") %>% 
  bind_rows(`TRUE` = ., `FALSE` = ., .id = "phone_owner") %>%
  mutate(sms.treatment.2_left = "sms.control", sms.treatment.2_right = "sms.control",
         phone_owner = as.logical(phone_owner),
         hh.baseline.sample = FALSE) 

param_phone_owners_ate <- tribble(
  ~ private_value_left, ~ social_value_left, ~ sms.treatment.2_left, ~ private_value_right, ~ social_value_right, ~ sms.treatment.2_right,
  "control",            "control",           "reminder.only",        "control",             "control",            "sms.control",
  "control",            "control",           "social.info",          "control",             "control",            "sms.control",
  "control",            "control",           "social.info",          "control",             "control",            "reminder.only",

  "control",            "ink",               "social.info",          "control",             "control",            "sms.control",
  "control",            "ink",               "social.info",          "control",             "control",            "social.info",
  "control",            "ink",               "social.info",          "control",             "ink",                "sms.control",

  "calendar",           "control",           "social.info",          "control",             "control",            "sms.control",
  "calendar",           "control",           "social.info",          "control",             "control",            "social.info",
  "calendar",           "control",           "social.info",          "calendar",            "control",            "sms.control",

  "bracelet",           "bracelet",          "social.info",          "control",             "control",            "sms.control",
  "bracelet",           "bracelet",          "social.info",          "control",             "control",            "social.info",
  "bracelet",           "bracelet",          "social.info",          "calendar",            "control",            "social.info",
  "bracelet",           "bracelet",          "social.info",          "bracelet",            "bracelet",           "sms.control",
  
  "control",           "bracelet",           "social.info",          "control",             "control",            "sms.control",
  "control",           "bracelet",           "social.info",          "control",             "control",            "social.info",
  "control",           "bracelet",           "social.info",          "calendar",            "control",            "social.info",
  "control",           "bracelet",           "social.info",          "bracelet",            "control",            "sms.control"
) %>%
  bind_rows("close" = ., "far" = ., .id = "dist.pot.group") %>%
  mutate(phone_owner = TRUE,
         hh.baseline.sample = FALSE) 

param_all_ate <- bind_rows(param_sms_control_ate, param_phone_owners_ate) 
```

```{r}
param_all_ate %>% 
  # select(-hh.baseline.sample) %>% 
  select(phone_owner, dist.pot.group, private_value_left, social_value_left, sms.treatment.2_left, private_value_right, social_value_right, sms.treatment.2_right) %>% 
  mutate_at(vars(starts_with("sms")), funs(fct_recode(., control = "sms.control"))) %>% 
  kable(col.names = c("Phone Owner", "Distance", sprintf(c("Private Value (%s)", "Social Value (%s)", "SMS (%s)"), rep(c("L", "R"), each = 3))))
```


```{r param-model-data}
param_stan_data <- analysis.data %>%
  mutate(private_value = fct_collapse(assigned.treatment, control = c("control", "ink")),
         social_value = fct_collapse(assigned.treatment, control = c("control", "calendar"))) %>% 
  prepare_bayesian_analysis_data(
    wtp.data, 
    
    treatment_map = data_grid(., private_value, social_value, dist.pot.group, sms.treatment.2, hh.baseline.sample, phone_owner) %>%
      filter(phone_owner | sms.treatment.2 == "sms.control",
            (private_value == "control" & social_value == "control") | sms.treatment.2 != "reminder.only",
            private_value != "calendar" | social_value == "control",
            private_value != "bracelet" | social_value == "bracelet"),
    
    treatment_formula = ~ (private_value + social_value * sms.treatment.2 * (dist.pot.group + hh.baseline.sample)) * phone_owner,
    
    subgroup_col = NULL,
    
    all_ate = param_all_ate,
    
    # name_match_false_pos_alpha, 
    # name_match_false_pos_beta,
    
    scale_df = 3,
    scale_sigma = 1,
    # real scale_sigma_ksh_util_gamma = 0.05;
  
    coef_df = 7,
    coef_sigma = 5,
    
    wtp_utility_df = 3,
    tau_mu_wtp_diff = 100,
    mu_wtp_df_student_t = 7,
    tau_sigma_wtp_diff = 50,
    sigma_wtp_df_student_t = 2.5,
    sigma_ksh_util_gamma = 5,
  )
```

```{r basic-model-1, eval=FALSE}
basic_model_1 <- stan_model(file = "takeup_model_1.stan", model_name = "model_1")
basic_model_1_fit <- sampling(basic_model_1, data = param_stan_data, chains = 8, iter = 200, sample_file = file.path("stanfit", "basic_model_1_10.csv"), control = lst(max_treedepth = 15)) # adapt_delta = 0.99, 
```

```{r}
basic_model_1_fit <- dir("stanfit", pattern = "basic_model_1_10_[1-8].csv", full.names = TRUE) %>% 
  read_stan_csv()
```

```{r, eval=FALSE}
print(basic_model_1_fit, pars = c("non_phone_takeup", "phone_takeup", "non_phone_takeup_ate", "phone_takeup_ate"))
```

```{r, eval=FALSE}
print(basic_model_1_fit, pars = "hyper_ksh_util_gamma_raw", digits_summary = 10)
```

```{r basic-model-1-prep-data}
est_deworming_takeup_ate <- basic_model_1_fit %>% 
  as.data.frame(pars = c("non_phone_takeup_ate", "phone_takeup_ate")) %>% 
  imap_dfr(~ tibble(outcome_id = .y, sim_outcome = .x)) %>% 
  separate(outcome_id, c("phone_owner", "ate_pair_rank"), "(_takeup_ate\\[)|,|\\]", extra = "drop") %>% 
  mutate_at(vars(ate_pair_rank), as.integer) %>% 
  group_by(phone_owner) %>% 
  do(bind_cols(., param_stan_data[[str_interp("${first(.$phone_owner)}_owner_ate_pairs")]][.$ate_pair_rank, ])) %>%
  mutate(all_treatment_id_left = param_stan_data[[str_interp("${first(phone_owner)}_owner_treatments")]][rank_id_left],
         all_treatment_id_right = param_stan_data[[str_interp("${first(phone_owner)}_owner_treatments")]][rank_id_right]) %>%
  ungroup() 

num_raw_takeup_ate <- nrow(est_deworming_takeup_ate)

est_deworming_takeup_ate %<>% 
  mutate(phone_owner = phone_owner == "phone") %>% 
  left_join(param_stan_data$treatment_map, c("all_treatment_id_left" = "all_treatment_id")) %>% 
  left_join(param_stan_data$treatment_map, c("all_treatment_id_right" = "all_treatment_id"), suffix = c("_left", "_right"))

assertthat::assert_that(num_raw_takeup_ate == nrow(est_deworming_takeup_ate) & all(phone_owner.x == phone_owner.y) & all(phone_owner.y == phone_owner), 
                        env = est_deworming_takeup_ate)

est_deworming_takeup_ate %<>% 
  select(-matches("phone_owner\\.[xy]"))

sms_ctrl_est_deworming_takeup_ate <- est_deworming_takeup_ate %>% 
  filter(sms.treatment.2_left == "sms.control", 
         sms.treatment.2_right == "sms.control",
         private_value_right == "control",
         social_value_right == "control",
         private_value_left != "control" | social_value_left != "control") %>% 
  group_by_at(vars(matches("((private|social)_value|sms.treatment.2|dist.pot.group)_(left|right)"), phone_owner)) %>% 
  summarize(mean_takeup_prop = mean(sim_outcome),
            ub_90 = quantile(sim_outcome, 0.95),
            ub_95 = quantile(sim_outcome, 0.975),
            lb_90 = quantile(sim_outcome, 0.05),
            lb_95 = quantile(sim_outcome, 0.025)) %>% 
  ungroup() %>% 
  unite(incentive_treatment_left, str_c(c("private", "social"), "_value_left"), sep = "-", remove = FALSE) %>% 
  unite(incentive_treatment_right, str_c(c("private", "social"), "_value_right"), sep = "-", remove = FALSE) %>% 
  mutate_at(vars(matches("incentive_treatment_left")), 
            funs(fct_relevel(factor(.), "control-ink", "calendar-control", "control-bracelet", "bracelet-bracelet")))
```

```{r, fig.height=6}
sms_ctrl_est_deworming_takeup_ate %>% 
  filter(incentive_treatment_left != "control-bracelet") %>% 
  ggplot(aes(incentive_treatment_left, mean_takeup_prop)) +
  geom_pointrange(aes(ymin = lb_95, ymax = ub_95), size = 0.75) +
  geom_linerange(aes(ymin = lb_90, ymax = ub_90), size = 1.75) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_text(aes(label = sprintf("%.2f", mean_takeup_prop)), nudge_x = 0.16) +
  scale_x_discrete("Comparator Incentive Treatment") +
  scale_y_continuous("Average Difference in Deworming Proportion") +
  labs(title = "Incentive Average Treatment Effect", subtitle = "Compared with the control arm", caption = "Points on plot are the mean point estimates.\nThe thick and thin vertical lines show the 90% and 95% posterior probability ranges, respectively.") +
  facet_grid(phone_owner ~ dist.pot.group_left, labeller = label_both) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```

```{r}
est_deworming_takeup <- basic_model_1_fit %>% 
  as.data.frame(pars = c("non_phone_takeup", "phone_takeup")) %>% 
  imap_dfr(~ tibble(outcome_id = .y, sim_outcome = .x)) %>% 
  separate(outcome_id, c("phone_owner", "all_treatment_rank", "monitored"), "(_takeup\\[)|,|\\]", extra = "drop") %>% 
  mutate_at(vars(all_treatment_rank, monitored), as.integer) %>% 
  mutate(monitored = monitored == 2) %>% 
  group_by(phone_owner) %>% 
  mutate(all_treatment_id = param_stan_data[[str_interp("${first(phone_owner)}_owner_treatments")]][all_treatment_rank]) %>% 
  ungroup() 

num_raw_takeup <- nrow(est_deworming_takeup)

est_deworming_takeup %<>% 
  mutate(phone_owner = phone_owner == "phone") %>% 
  left_join(param_stan_data$treatment_map, c("all_treatment_id" = "all_treatment_id")) 

assertthat::assert_that(num_raw_takeup == nrow(est_deworming_takeup) & all(phone_owner.x == phone_owner.y), 
                        env = est_deworming_takeup)

est_deworming_takeup %<>% 
  mutate(phone_owner = phone_owner.x) %>% 
  select(-matches("phone_owner\\.[xy]"))

sms_ctrl_est_deworming_takeup <- est_deworming_takeup %>% 
  filter(sms.treatment.2 == "sms.control") %>% 
  group_by_at(vars(matches("((private|social)_value|sms.treatment.2|dist.pot.group)"), phone_owner, monitored)) %>% 
  summarize(mean_takeup_prop = mean(sim_outcome),
            ub_90 = quantile(sim_outcome, 0.95),
            ub_95 = quantile(sim_outcome, 0.975),
            lb_90 = quantile(sim_outcome, 0.05),
            lb_95 = quantile(sim_outcome, 0.025)) %>% 
  ungroup() %>% 
  unite(incentive_treatment, str_c(c("private", "social"), "_value"), sep = "-", remove = FALSE) %>% 
  mutate(incentive_treatment = fct_relevel(incentive_treatment, "control-control", "control-ink", "calendar-control", "control-bracelet", "bracelet-bracelet"))
```

```{r, fig.width=10}
sms_ctrl_est_deworming_takeup %>%
  filter(incentive_treatment != "control-bracelet") %>% 
  ggplot(aes(incentive_treatment, mean_takeup_prop, color = monitored)) + 
  geom_pointrange(aes(ymin = lb_95, ymax = ub_95), position = position_dodge(), size = 0.75) +
  geom_linerange(aes(ymin = lb_90, ymax = ub_90), position = position_dodge(), size = 1.75) +
  scale_x_discrete("Incentive Treatment Arm") +
  scale_y_continuous("Deworming Proportion", breaks = seq(0, 1, 0.1)) +
  labs(title = "Deworming Take-up by Treatment Arm", caption = "Points on plot are the mean point estimates.\nThe thick and thin vertical lines show the 90% and 95% posterior probability ranges, respectively.") +
  scale_color_discrete("", labels = c("Name Matched", "Monitored")) +
  facet_grid(phone_owner ~ dist.pot.group, labeller = label_both) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```

# Dynamic Model

## Qualitative Plots

```{r, fig.width=10, fig.height=10}
prop_deworm_day_data <- analysis.data %>% 
  filter(!name_matched) %>% 
  group_by(wave, assigned.treatment, dist.pot.group, sms.treatment.2) %>% 
  mutate(cell_size = n()) %>% 
  group_by(dewormed.date.any, add = TRUE) %>% 
  summarize(prop_dewormed = n() / first(cell_size)) %>% 
  group_by(wave, assigned.treatment, dist.pot.group, sms.treatment.2) %>% 
  mutate(cumul_prop_dewormed = cumsum(prop_dewormed)) %>% 
  ungroup() %>% 
  mutate(dewormed.weekday = factor(weekdays(dewormed.date.any), 
                                   levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))

base_plot <- function(.data, col, lt = NULL) {
  .data %>% 
    filter(!is.na(dewormed.date.any)) %>% 
    ggplot(aes_string(x = "dewormed.date.any", y = "cumul_prop_dewormed", color = col)) +
    geom_line(aes_string(color = col, linetype = lt)) +
    geom_point() +
    scale_x_date("", labels = scales::date_format("%a")) +
    scale_y_continuous("Cumulative Deworming Proportion") +
    theme(legend.position = "bottom")
}

dist_incentive_plot <- prop_deworm_day_data %>% 
  base_plot("sms.treatment.2") + 
  facet_grid(assigned.treatment ~ dist.pot.group + wave, scales = "free_x")
  # facet_grid(assigned.treatment ~ dist.pot.group, scales = "free_x")

dist_sms_plot <- prop_deworm_day_data %>% 
  base_plot("assigned.treatment", lt = "sms.treatment.2") + 
  facet_grid(~ dist.pot.group + wave, scales = "free_x")
  # facet_grid(~ dist.pot.group, scales = "free_x")

dist_sms_plot_split <- prop_deworm_day_data %>% 
  base_plot("assigned.treatment", lt = "sms.treatment.2") + 
  facet_grid(sms.treatment.2 ~ dist.pot.group + wave, scales = "free_x")

plot(dist_incentive_plot)
```

```{r, fig.width=14, fig.height=6}
plot(dist_sms_plot)
```

```{r, fig.width=14, fig.height=10}
plot(dist_sms_plot_split)
```

```{r, fig.width=10}
analysis.data %>% 
  filter(!is.na(endline_deworm_rate)) %>% 
  ggplot() +
  geom_violin(aes(assigned.treatment, endline_deworm_rate, color = dist.pot.group, linetype = sms.treatment.2), draw_quantiles = c(0.25, 0.5, 0.75)) +
  scale_y_continuous(breaks = 0:10)
```

## Inference

```{r dyn-param-ate}
dyn_sms_control_ate <- tribble(
  ~ private_value_left, ~ social_value_left, ~ private_value_right, ~ social_value_right,
  "control",            "ink",               "control",             "control",
  "calendar",           "control",           "control",             "control",
  "bracelet",           "bracelet",          "control",             "control",
  "bracelet",           "bracelet",          "calendar",            "control",
  
  "control",           "bracelet",           "control",            "control" 
) %>%
  bind_rows("close" = ., "far" = ., .id = "dist.pot.group") %>% 
  bind_rows(`TRUE` = ., `FALSE` = ., .id = "phone_owner") %>%
  mutate(sms.treatment.2_left = "sms.control", sms.treatment.2_right = "sms.control",
         phone_owner = as.logical(phone_owner),
         signal_observed_left = social_value_left,
         signal_observed_right = social_value_right,
         reminder_info_stock_left = "control",
         reminder_info_stock_right = "control",
         hh.baseline.sample = FALSE) %>% 
  bind_rows(tribble(~ private_value_left, ~ social_value_left, ~ signal_observed_left, ~ private_value_right, ~ social_value_right, ~ signal_observed_right,
                    "control",            "bracelet",         "control",               "control",             "control",            "control",
                    "control",            "ink",              "control",               "control",             "control",            "control"))

dyn_phone_owners_ate <- tribble(
  ~ private_value_left, ~ social_value_left, ~ sms.treatment.2_left, ~ private_value_right, ~ social_value_right, ~ sms.treatment.2_right,
  "control",            "control",           "reminder.only",        "control",             "control",            "sms.control",
  "control",            "control",           "social.info",          "control",             "control",            "sms.control",
  "control",            "control",           "social.info",          "control",             "control",            "reminder.only",

  "control",            "ink",               "social.info",          "control",             "control",            "sms.control",
  "control",            "ink",               "social.info",          "control",             "control",            "social.info",
  "control",            "ink",               "social.info",          "control",             "ink",                "sms.control",

  "calendar",           "control",           "social.info",          "control",             "control",            "sms.control",
  "calendar",           "control",           "social.info",          "control",             "control",            "social.info",
  "calendar",           "control",           "social.info",          "calendar",            "control",            "sms.control",

  "bracelet",           "bracelet",          "social.info",          "control",             "control",            "sms.control",
  "bracelet",           "bracelet",          "social.info",          "control",             "control",            "social.info",
  "bracelet",           "bracelet",          "social.info",          "calendar",            "control",            "social.info",
  "bracelet",           "bracelet",          "social.info",          "bracelet",            "bracelet",           "sms.control",
  
  "control",           "bracelet",           "social.info",          "control",             "control",            "sms.control",
  "control",           "bracelet",           "social.info",          "control",             "control",            "social.info",
  "control",           "bracelet",           "social.info",          "calendar",            "control",            "social.info",
  "control",           "bracelet",           "social.info",          "bracelet",            "control",            "sms.control"
) %>%
  bind_rows("close" = ., "far" = ., .id = "dist.pot.group") %>%
  mutate(phone_owner = TRUE,
         hh.baseline.sample = FALSE, 
         signal_observed_left = social_value_left,
         signal_observed_right = social_value_right,
         reminder_info_stock_left = fct_recode(sms.treatment.2_left, control = "sms.control"),
         reminder_info_stock_right = fct_recode(sms.treatment.2_right, control = "sms.control")) %>% 
  bind_rows(
    tribble(~ private_value_left, ~ social_value_left, ~ signal_observed_left, ~ sms.treatment.2_left, ~ reminder_info_stock_left, ~ private_value_right, ~ social_value_right, ~ signal_observed_right, ~ sms.treatment.2_right, ~ reminder_info_stock_right,
            "control",            "bracelet",         "control",               "social_info",          "control",                  "control",             "bracelet",            "control",             "sms.control",           "control",
            
            
            "control",            "bracelet",         "control",               "social_info",          "control",                  "control",             "control",            "control",             "sms.social_info",           "control"))
            

dyn_all_ate <- bind_rows(dyn_sms_control_ate, dyn_phone_owners_ate) 
```

```{r dyn-model-data, dependson="param-ate"}
dyn_stan_data <- analysis.data %>%
  mutate(private_value = fct_collapse(assigned.treatment, control = c("control", "ink")),
         social_value = fct_collapse(assigned.treatment, control = c("control", "calendar")),
         signal_observed = social_value,
         reminder_info_stock = fct_recode(sms.treatment.2, control = "sms.control")) %>% 
  # filter(!name_matched, sms.treatment.2 == "sms.control") %>%
  filter(!name_matched) %>%
  prepare_bayesian_analysis_data(
    wtp.data, 
    
    treatment_map = data_grid(., private_value, social_value, signal_observed, reminder_info_stock, dist.pot.group, sms.treatment.2, hh.baseline.sample, phone_owner) %>%
      filter(phone_owner | sms.treatment.2 == "sms.control",
            (private_value == "control" & social_value == "control") | sms.treatment.2 != "reminder.only",
             private_value != "calendar" | social_value == "control",
             private_value != "bracelet" | social_value == "bracelet",
             signal_observed == social_value | signal_observed == "control",
             reminder_info_stock == fct_recode(sms.treatment.2, control = "sms.control")),
    
    # treatment_map = data_grid(., private_value, social_value, signal_observed, dist.pot.group, hh.baseline.sample, phone_owner) %>%
    #   filter(private_value != "calendar" | social_value == "control",
    #          private_value != "bracelet" | social_value == "bracelet",
    #          signal_observed == social_value | signal_observed == "control"),
    
    dynamic_treatment_map = lst(formula = ~ (signal_observed + reminder_info_stock)*phone_owner, 
                                trends = tibble(signal_observed = 0:11,
                                                reminder_info_stock = rep(0:5, each = 2))),
    
    # treatment_formula = ~ (private_value + social_value * (dist.pot.group + hh.baseline.sample)) * phone_owner,
    treatment_formula = ~ (private_value + social_value * sms.treatment.2 * (dist.pot.group + hh.baseline.sample)) * phone_owner,
    subgroup_col = NULL,
    
    all_ate = dyn_all_ate,
    # all_ate = dyn_sms_control_ate %>% select(-contains("sms.treatment")),
    
    # name_match_false_pos_alpha, 
    # name_match_false_pos_beta,
    
    scale_df = 7,
    scale_sigma = 1,
    scale_sigma_dynamic = 1,
   
    coef_df = 7,
    coef_sigma = 1,
    coef_sigma_dynamic = 5,
    
    wtp_utility_df = 3,
    tau_mu_wtp_diff = 100,
    mu_wtp_df_student_t = 7,
    tau_sigma_wtp_diff = 50,
    sigma_wtp_df_student_t = 2.5,
    sigma_ksh_util_gamma = 5,
  )
```

```{r basic-model-2-simple, eval=FALSE}
basic_model_2_simple <- stan_model(file = "takeup_model_2_simple.stan", model_name = "model_2_simple")
basic_model_2_simple_fit <- dyn_stan_data %>% 
  sampling(basic_model_2_simple, data = ., #init = .$dynamic_initializer,
                                     chains = 8, iter = 400, control = lst(max_treedepth = 15), # adapt_delta = 0.99, 
                                     sample_file = file.path("stanfit", "basic_model_2_simple_7.csv")) 
```

```{r basic-model-2-simple-debug, eval=FALSE}
basic_model_2_simple <- stan_model(file = "takeup_model_2_simple.stan", model_name = "model_2_simple")
basic_model_2_simple_fit <- dyn_stan_data %>% 
  sampling(basic_model_2_simple, data = ., #init = .$dynamic_initializer,
           chains = 1, iter = 20, control = lst(max_treedepth = 15), # adapt_delta = 0.99, 
           sample_file = file.path("stanfit", "basic_model_2_simple_debug.csv")) 
```

```{r}
basic_model_2_simple_fit <- dir("stanfit", pattern = "basic_model_2_simple_6_[1-8].csv", full.names = TRUE) %>% 
  read_stan_csv()
```

```{r basic-model-2-prep-data}
est_deworming_days <- basic_model_2_simple_fit %>% 
  as.data.frame( pars = c("non_phone_deworming_days", "phone_deworming_days")) %>% 
  imap_dfr(~ tibble(outcome_id = .y, sim_outcome = .x)) %>% 
  separate(outcome_id, c("phone_owner", "all_treatment_rank", "day"), "(_deworming_days\\[)|,|\\]", extra = "drop") %>% 
  mutate_at(vars(day, all_treatment_rank), as.integer) %>% 
  group_by(phone_owner) %>% 
  mutate(all_treatment_id = dyn_stan_data[[str_interp("${first(phone_owner)}_owner_treatments")]][all_treatment_rank]) %>%
  ungroup() %>% 
  mutate(phone_owner = phone_owner == "phone") %>% 
  left_join(dyn_stan_data$treatment_map, "all_treatment_id")

assertthat::assert_that(all(phone_owner.x == phone_owner.y), env = est_deworming_days)

est_deworming_days %<>% 
  mutate(phone_owner = phone_owner.x) %>% 
  select(-matches("phone_owner\\.[xy]"))
```

```{r, fig.width=12}
sms_control_dyn_takeup <- est_deworming_days %>% 
  filter(sms.treatment.2 == "sms.control",
         social_value != "bracelet" | private_value == "control") %>% 
  unite(incentive_treatment, private_value, social_value, sep = "-", remove = FALSE) %>% 
  group_by(day, phone_owner, dist.pot.group, private_value, social_value, incentive_treatment, day) %>% 
  summarize(mean_takeup_prop = mean(sim_outcome),
            ub_90 = quantile(sim_outcome, 0.95),
            lb_90 = quantile(sim_outcome, 0.05)) %>% 
  ungroup() %>% {
    treated <- filter(., incentive_treatment != "control-control") %>% 
      mutate(comparator = incentive_treatment)
    baseline <- filter(., incentive_treatment == "control-control") %>% 
      left_join(select(treated, day, phone_owner, dist.pot.group, comparator), c("day", "phone_owner", "dist.pot.group"))
    
    bind_rows(treated, baseline)
  } 

sms_control_dyn_takeup %>% 
  filter(day < 13) %>% 
  ggplot(aes(x = day, y = mean_takeup_prop)) +
  geom_line(data = . %>% filter(incentive_treatment == "control-control")) +
  geom_point(data = . %>% filter(incentive_treatment == "control-control")) +
  geom_line(aes(color = incentive_treatment), data = . %>% filter(incentive_treatment != "control-control")) +
  geom_point(aes(color = incentive_treatment), data = . %>% filter(incentive_treatment != "control-control")) +
  geom_ribbon(aes(group = incentive_treatment, ymin = lb_90, ymax = ub_90), alpha = 0.2) +
  facet_grid(phone_owner + dist.pot.group ~ comparator, labeller = label_both, scales = "free_y")
```

```{r}
sms_control_dyn_takeup %>% 
  filter(day == 13, incentive_treatment == comparator | (comparator == "control-ink" & incentive_treatment == "control-control")) %>% 
  mutate(incentive_treatment = fct_relevel(incentive_treatment, "control-control", "control-ink", "calendar-control", "control-bracelet")) %>% 
  mutate(mean_takeup_prop = 1 - mean_takeup_prop) %>% 
  ggplot(aes(x = incentive_treatment, y = mean_takeup_prop)) +
  geom_pointrange(aes(ymin = 1 - lb_90, ymax = 1 - ub_90)) +
  # scale_y_continuous(limits = c(0, 0.5)) +
  facet_grid(phone_owner ~ dist.pot.group, labeller = label_both)
```

```{r, fig.width=10, fig.height=10}
est_deworming_days %>% 
  filter(phone_owner,
         social_value != "bracelet" | private_value == "bracelet",
         day < 13) %>% 
  unite(incentive_treatment, private_value, social_value, sep = "-", remove = FALSE) %>% 
  group_by(day, phone_owner, dist.pot.group, private_value, social_value, incentive_treatment, sms.treatment.2) %>% 
  summarize(mean_takeup_prop = mean(sim_outcome),
            ub_90 = quantile(sim_outcome, 0.95),
            lb_90 = quantile(sim_outcome, 0.05)) %>% 
  ungroup() %>% 
  ggplot(aes(x = day, y = mean_takeup_prop)) +
  geom_point(aes(group = sms.treatment.2, color = incentive_treatment)) +
  geom_line(aes(linetype = sms.treatment.2, color = incentive_treatment)) +
  geom_ribbon(aes(group = sms.treatment.2, ymin = lb_90, ymax = ub_90), alpha = 0.25) +
  facet_grid(incentive_treatment ~ dist.pot.group )
```



