---
title: Optim
output: 
  pdf_document:
    keep_tex: yes
    extra_dependencies: ["amsmath", "threeparttable", "placeins"]
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage[utf8]{inputenc}
    - \usepackage{makecell}
    - \usepackage{xcolor}
params: 
  plot_input_path: "~/projects/takeup/optim/plots/agg-log-full-many-pots"
  misc_input_path: "~/projects/takeup/optim/plots/agg-log-full-many-pots"
  data_input_path: "~/projects/takeup/optim/data/agg-log-full-many-pots"
  many_pots: TRUE
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  warning = TRUE, 
  message = FALSE, 
  echo = FALSE, 
  cache = TRUE
  ) 
if (interactive()) {
  params = list(
    plot_input_path = "~/projects/takeup/optim/plots/agg-log-full-many-pots",
    data_input_path = "~/projects/takeup/optim/data/agg-log-full-many-pots",
    misc_input_path = "~/projects/takeup/optim/plots/agg-log-full-many-pots"
  )
}
library(knitr)
library(tidyverse)
library(ggplot2)
library(ompr)
library(ompr.roi)
library(kableExtra)
library(ROI.plugin.glpk)
```

# Problem Setup 

Suppose there are $n$ villages, indexed by $i$, and $m$ points of treatment (PoT) which we index 
by $j$. The social planner's goal is to minimise the number of PoTs required subject to hitting 
$\overline{W}^C = E\left[\sum^n_{i = 1}U(\textit{takeup}^C_{i})\right]$ - the expected social welfare the planner would have achieved by assigning 
every village in the experiment to the control condition\^[This expectation is taken over both posterior parameter uncertainty and 
different realisations of village-PoT pairs under random assignment.]. We can reformulate this 
as an integer programme:

$$
\begin{aligned}
\min \sum_{j = 1}^m  &y_j \\
s.t. \ \ 
\sum_{i = 1}^n U\left(\widehat{\textit{takeup}}_{ij}x_{ij}\right) &\geq \underbrace{E\left[\sum_{i = 1}^n U\left(\textit{takeup}^C_{i}\right)\right]}_{\overline{W}^C} \\
    \sum_{j=1}^{m} x_{ij} &= 1, \forall i \\
    x_{ij} &\leq y_j, \forall i, j  \\
 x_{ij} &\in \{0,1\}, y_j \in\{0,1\}
\end{aligned}
$$


$x_{ij}$ is an indicator corresponding to village $i$ using point of 
treatment $j$. $y_{j}$ is an indicator corresponding to if PoT $j$ is funded (i.e. 
available for use by villages) by the social planner.  The remaining constraints 
ensure every village is assigned to a funded PoT. 

We set $U(\cdot) = log(\cdot)$ for two reasons: Firstly, to introduce a dislike for 
inequality to the social planner's problem - there's decreasing marginal 
utility to increasing takeup within a village. Secondly, log-utility completely
 dissuades the 
social planner from implementing a ruthless utilitarian allocation that sets takeup to 
0 in sparsely populated locations. $\widehat{\textit{takeup}}_{ij}$ corresponds to 
the social planner's posterior median estimate of demand for deworming when village 
$i$ is assigned to point of treatment $j$.



The results presented below introduce a cutoff at 3.5km beyond which we set 
takeup to 0 - i.e. no villager is prepared to walk more than 3.5km to a point of 
treatment. Results 
in the appendix relax this assumption, although in reality past 5km 
the model places virtually no posterior density on positive takeup. We chose 3.5km 
as a compromise between limiting extrapolation and constraints imposed by our 
experimental design - by construction there are no treatment points within 2.5km of 
multiple villages in our data.



### Counterfactual Simulations 

Our structural model decomposes $takeup_{ij}$, the demand for deworming from pairing 
village $i$ with PoT $j$, into a private utility component and reputational return 
from signalling deworming status. Therefore, we fix private utility at the control 
level and explore the effect of counterfactually varying visibility, $\mu_{z}$ ,
on the number of required PoTs.
$$
takeup_{ij} = \underbrace{B(z, d_{ij})}_{\text{private benefit}} + \underbrace{\mu_{z} \Delta\left[ w^*(z, d_{i,j})\right]}_{\text{reputational return}}
$$


### Holding Private Benefit at Control

```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $\\mu_{z=\\text{control}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-control-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```


```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $\\mu_{z=\\text{bracelet}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
  "agg-log-cutoff-b-control-mu-bracelet-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```




```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $\\mu_{z=\\text{ink}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
  "agg-log-cutoff-b-control-mu-ink-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```



```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $\\mu_{z=\\text{calendar}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
  "agg-log-cutoff-b-control-mu-calendar-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```
\FloatBarrier
### Holding Visibility at Control 

```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $B_{z=\\text{control}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-control-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```


```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $B_{z=\\text{bracelet}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-bracelet-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```




```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $B_{z=\\text{ink}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-ink-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```




```{r, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, $B_{z=\\text{calendar}}$. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-calendar-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```


\FloatBarrier




### Summary Table and Histogram


```{r, echo=FALSE, fig.align="center", fig.cap="Distribution of walking distance, holding private benefit at control."}
include_graphics(
  file.path(
    params$plot_input_path,
    "optim-walk-density-b-control.png"
  ),
  rel_path = FALSE
)  
```

```{r, echo=FALSE, fig.align="center", fig.cap="Demand - Private Benefit Fixed at Control"}
include_graphics(
  file.path(
    params$plot_input_path,
    "optim-demand-df.png"
  ),
  rel_path = FALSE
)  
```


```{r, echo=FALSE}

summ_df_rep = read_csv(
  file.path(
    params$data_input_path,
    "posterior-rep-summ-optim.csv"
  )
  ) 


wide_summ_df_rep = summ_df_rep %>%
  gather(variable, value, -B_z, -mu_z)  %>%
  mutate(CI = if_else(str_detect(variable, "CI"), "ci", "estim")) %>%
  mutate(variable = str_remove(variable, "_CI")) %>%
  mutate(variable = str_remove(variable, "_estimate")) %>%
  pivot_wider(
    id_cols = c(B_z, mu_z, variable), 
    names_from = CI, 
    values_from = value
  )   %>%
  mutate(estim = as.numeric(estim) %>% round(3))  %>%
  mutate(
    estim_value = 
    linebreak(
      paste0(
        estim, "\n", 
        ci
      ), 
      align = "c"
    )
  ) %>%
  select(
    -estim, -ci
  )  %>%
  mutate(across(where(is.character), str_replace_all, "_", " ")) %>%
  spread(variable, estim_value)
  
colnames(wide_summ_df_rep) = str_replace_all(colnames(wide_summ_df_rep), "_", " ")

wide_summ_df_rep %>% 
  knitr::kable(
    caption = "PM Aware of Signalling",
    booktabs = TRUE,
    format = "latex",
    escape = FALSE
    ) %>%
  kableExtra::kable_styling(
    latex_options =  c("scale_down")
  )

summ_df_sup_rep = read_csv(
  file.path(
    params$data_input_path,
    "posterior-suppress-rep-summ-optim.csv"
  )
  ) 

colnames(summ_df_sup_rep) = str_remove(colnames(summ_df_sup_rep), "_estimate")
 summ_df_sup_rep %>% 
  filter(B_z == mu_z) %>%
  knitr::kable(
    digits = 3, 
    caption = "PM Unaware of Signalling",
    booktabs = TRUE
    ) %>%
  kableExtra::kable_styling(
    font_size = 7,
    latex_options =  "scale_down"
  )

```



```{r, echo=FALSE, fig.align="center", fig.cap="Perceived Demand Curves, by PM Type"}
include_graphics(
  file.path(
    params$data_input_path,
    "struct-naive-optim-demand-df.png"
  ),
  rel_path = FALSE
)  
```


\FloatBarrier
## Naive vs Sophisticated


## Control - Experiment Set-Up

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using control treatment. Policymaker aware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-control-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using control treatment. Policymaker unaware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path, 
    "agg-log-suppress-rep-cutoff-b-control-mu-control-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```



\FloatBarrier

## Bracelet - Experiment Set-Up

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using bracelet treatment. Policymaker aware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-bracelet-mu-bracelet-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using bracelet treatment. Policymaker unaware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
      params$plot_input_path,
    "agg-log-suppress-rep-cutoff-b-bracelet-mu-bracelet-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```


\FloatBarrier
## Calendar - Experiment Set-Up

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using calendar treatment. Policymaker aware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-cutoff-b-calendar-mu-calendar-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using calendar treatment. Policymaker unaware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
    "agg-log-suppress-rep-cutoff-b-calendar-mu-calendar-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```

\FloatBarrier
## Ink - Experiment Set-Up

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using ink treatment. Policymaker aware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
  "agg-log-cutoff-b-ink-mu-ink-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```

```{r, eval = TRUE, echo=FALSE, fig.align="center", fig.cap="Optimal allocation of points of treatment, using ink treatment. Policymaker unaware of signalling. Blue triangles indicate funded PoTs; red triangles unused PoTs; black dots denote villages; and line segments a PoT-village pairing"}
include_graphics(
  file.path(
    params$plot_input_path,
  "agg-log-suppress-rep-cutoff-b-ink-mu-ink-STRUCTURAL_LINEAR_U_SHOCKS-median-optimal-allocation-plot.png"
  ),
  rel_path = FALSE
)  
```
