---
output: pdf_document
header-includes:
  - \usepackage{pxfonts} 
---

```{r setup, echo=FALSE, include=FALSE}
library(magrittr)
library(tidyverse)

ggplot2::theme_set(theme_minimal())

knitr::opts_chunk$set(echo = FALSE)
```

Number of counties: `r stan_data$num_counties`

Number of villages: `r stan_data$num_clusters`

Number of take-up observations: `r stan_data$num_obs`

Number of WTP observations: `r stan_data$num_wtp_obs`

Number of beliefs observations: `r stan_data$num_beliefs_obs`

## Reduced-form Treatment Effects

```{r}
rf_te %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment_left, assigned_dist_group_left, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```

## Reduced-form Levels

```{r}
rf_levels %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment, assigned_dist_group, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```

\pagebreak

## Structural Incentive Treatment Effects

```{r}
incentive_te %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment_left, assigned_dist_group_left, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```

## Structural Incentive Levels

```{r}
incentive_levels %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment, assigned_dist_group, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```

## Structural Signaling Treatment Effects

```{r}
signaling_te %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment_left, assigned_dist_group_left, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```

## Structural Private Incentive Treatment Effects

```{r}
private_incentive_te %>%
  filter(fct_match(fit_type, "fit")) %>% 
  select(assigned_treatment_left, assigned_dist_group_left, mean_est, per_0.01, per_0.1, per_0.5, per_0.9, per_0.99) %>% 
  kable(booktabs = TRUE, latex_options = c("striped", "scale_down"))
```
